### 2022-05-20 examples/benchmark/full-report.qmd
update

---
title: Inventor Disambiguation Report
format:
    html:
        theme: cosmo
        code-fold: true
        code-tools: true
        code-block-border-left: true
        code-copy: true
        code-block-border-left: "#31BAE9"
jupyter: python3
---

## Data Preparation

First, we prepare the disambiguation result data to evaluate. We consider the current PatentsView disambiguation, obtained from the `rawinventor.tsv` data file, as well as one trivial disambiguation where all inventor mentions are clustered together.

The code below reads the disambiguation result from `rawinventor.tsv`. A disambiguation result is defined as a pandas Series with an index representing mention IDs and values representing cluster assignement.

Mention IDs are standardized to be of the form `<OFFICE><PATENT_NUMBER>-<INVENTOR_SEQUENCE>`, where OFFICE is the patent issuer office abbreviation (e.g. "US" or "EPO"), PATENT_NUMBER is the standard patent number form, and INVENTOR_SEQUENCE is the inventor's position on the given patent, starting from 0. For example, the mention ID
> US5811073-0
represents the first listed inventor on US patent number 5811073.

```{python}
#| label: data-prep
#| code-fold: true
import pandas as pd

import wget
import zipfile
import os

import plotly.io as pio
pio.templates.default = "plotly_white" # Set plotly theme

if not os.path.isfile("rawinventor.tsv"):
    wget.download("https://s3.amazonaws.com/data.patentsview.org/download/rawinventor.tsv.zip")
    with zipfile.ZipFile("rawinventor.tsv.zip", 'r') as zip_ref:
        zip_ref.extractall(".")
    os.remove("rawinventor.tsv.zip")

if not os.path.isfile("disambiguation.tsv"):
    rawinventor = pd.read_csv("rawinventor.tsv", sep="\t")
    rawinventor["mention-id"] = "US" + rawinventor.patent_id.astype(str) + "-" + rawinventor.sequence.astype(str)
    rawinventor[["mention-id", "inventor_id"]].to_csv("disambiguation.tsv", sep="\t", index=False)
    del(rawinventor)

data = pd.read_csv("disambiguation.tsv", sep="\t")
data.set_index("mention-id", inplace=True)
current_disambiguation = data["inventor_id"]
```

Next, we define a dictionary describing the two disambiguations to compare, i.e. the "current" disambiguation and the "one cluster" trivial disambiguation.

```{python}
#| label: disambiguations
#| code-fold: false

disambiguations = {
    "current": current_disambiguation,
    "one cluster": 0*current_disambiguation
}
```

We can now generate the disambiguation report using `disambiguations` and `rawinventor.tsv` as the input.

## Summary Statistics

```{python}
#| label: imports

import wget
import zipfile
import os

import plotly.io as pio
pio.templates.default = "plotly_white" # Set plotly theme

from pv_evaluation.summary import InventorDisambiguationSummary

summarizer = InventorDisambiguationSummary("rawinventor.tsv", processed_data_dir=".", name="current disambiguation")
```

```{python}
summarizer.plot_cluster_size_distribution(range=(0.5,10.5))
```

```{python}
summarizer.get_top_inventors()
```

```{python}
summarizer.plot_entropy_curve()
```

```{python}
summarizer.plot_cluster_unique_name_distribution(range=(0, 100))
```

```{python}
summarizer.plot_homonymy_rate_distribution()
```

## Benchmark Evaluation

### 2022-05-20 pv_evaluation/benchmark/data.py

@@ -14,6 +14,8 @@ def load_unique_id_series(module, filename):
 def load_harvard_inventors_benchmark():
     """TODO: Document this dataset.
     """
+    # TODO: Fix inventor mention order in this dataset. Right now inventor sequence numbers are mixed up.
+    pass
     return load_unique_id_series(INVENTOR_DATA_MODULE, "harvard-inventors-benchmark.csv")
         
 def load_israeli_inventors_benchmark():

### 2022-05-20 examples/benchmark/full-report.qmd
update

@@
         code-block-border-left: "#31BAE9"
+        echo: false
+        include-in-header: header.html
+        include-after-body: footer.html
+execute:
+  cache: true
+  warning: false
+  message: false
 jupyter: python3
@@
 
+<!--
 ## Data Preparation
@@
 represents the first listed inventor on US patent number 5811073.
-
+-->
 ```{python}
@@
 
-Next, we define a dictionary describing the two disambiguations to compare, i.e. the "current" disambiguation and the "one cluster" trivial disambiguation.
+<!--
+Next, we define a dictionary describing the two disambiguations to compare, i.e. the "current" disambiguation and the "one cluster" trivial disambiguation.-->
 
@@
 
+<!--
 We can now generate the disambiguation report using `disambiguations` and `rawinventor.tsv` as the input.
+-->
 
@@
 from pv_evaluation.summary import InventorDisambiguationSummary
+from pv_evaluation.benchmark import inventor_benchmark_plot
 
@@
 ```
+
+::: {.panel-tabset}
+
+### Cluster Sizes
 
@@
 
+### Top Inventors
+
 ```{python}
@@
 ```
+
+### Entropy Curve
 
@@
 
+### Cluster Homogeneity
+
 ```{python}
@@
 ```
+
+### Cluster Separation
 
@@
 
+:::
+
 ## Benchmark Evaluation
+
+::: {.panel-tabset}
+
+### Evaluation Results
+
+```{python}
+inventor_benchmark_plot(disambiguations)
+```
+
+### Predicted Cluster Errors
+
+::: {.panel-tabset}
+
+#### Israeli Inventors
+
+```{python}
+#| column: page
+from pv_evaluation.benchmark import (
+    load_israeli_inventors_benchmark,
+    load_patentsview_inventors_benchmark,
+    inspect_clusters_to_split,
+    inspect_clusters_to_merge
+)
+
+inspect_clusters_to_split(disambiguations["current"], load_israeli_inventors_benchmark()).to_html()
+```
+
+#### PatentsView Inventors
+
+```{python}
+#| column: page
+inspect_clusters_to_split(disambiguations["current"], load_patentsview_inventors_benchmark()).to_html()
+```
+
+:::
+
+### Reference Cluster Errors
+
+::: {.panel-tabset}
+
+#### Israeli Inventors
+
+```{python}
+#| column: page
+inspect_clusters_to_merge(disambiguations["current"], load_israeli_inventors_benchmark()).to_html()
+```
+
+#### PatentsView Inventors
+
+```{python}
+#| column: page
+inspect_clusters_to_merge(disambiguations["current"], load_patentsview_inventors_benchmark()).to_html()
+```
+
+:::
+
+:::
+
+## Representative Performance Estimates

### 2022-05-20 pv_evaluation/benchmark/__init__.py
update

@@ -9,6 +9,7 @@ from .report import (
     inventor_benchmark_plot,
     inspect_clusters_to_split,
     inspect_clusters_to_merge,
+    style_cluster_inspection,
 )
 
 __all__ = [
@@ -19,4 +20,5 @@ __all__ = [
     "inventor_benchmark_plot",
     "inspect_clusters_to_split",
     "inspect_clusters_to_merge",
+    "style_cluster_inspection",
 ]

### 2022-05-20 pv_evaluation/benchmark/report.py

@@ -11,7 +11,6 @@ from pv_evaluation.metrics import (
     cluster_fscore,
 )
 from pv_evaluation.benchmark import (
-    load_harvard_inventors_benchmark,
     load_israeli_inventors_benchmark,
     load_patentsview_inventors_benchmark
 )
@@ -20,7 +19,6 @@ from pv_evaluation.benchmark import (
 benchmarks = {
     "patentsview-inventors": load_patentsview_inventors_benchmark,
     "israeli-inventors": load_israeli_inventors_benchmark,
-    "harvard-inventors": load_harvard_inventors_benchmark
 }
 metrics = {
     #"pairwise precision": pairwise_precision,
@@ -57,6 +55,20 @@ def inventor_benchmark_plot(disambiguations, **kwargs):
     computed_metrics = inventor_benchmark_table(disambiguations)
     return px.bar(computed_metrics, y="value", x="metric", color="algorithm", facet_col="benchmark", barmode='group', **kwargs)
 
+def style_cluster_inspection(table):
+    def format_color_groups(df):
+        # From https://datascientyst.com/pandas-dataframe-background-color-based-condition-value-alternate-row-color-based-group/
+        colors = ['white', 'lightblue']
+        x = df.copy()
+        factors = list(x['prediction'].unique())
+        i = 0
+        for factor in factors:
+            style = f'background-color: {colors[i]}'
+            x.loc[x['prediction'] == factor, :] = style
+            i = not i
+        return x
+        
+    return table.style.apply(format_color_groups, axis=None)
 
 def inspect_clusters_to_split(disambiguation, benchmark, join_with=None):
     data = pd.concat({"prediction":disambiguation, "reference":benchmark}, axis=1, join="inner")
@@ -68,12 +80,13 @@ def inspect_clusters_to_split(disambiguation, benchmark, join_with=None):
             .rename("ref_count"), 
         on="prediction")
         .query("ref_count > 1")
+        .sort_values("reference")
         .sort_values("prediction")
         .drop("ref_count", axis=1)    
     )
     
     if join_with is not None:
-        return clusters_to_split.join(join_with, rsuffix="_joined")
+        clusters_to_split = clusters_to_split.join(join_with, rsuffix="_joined")
     else:
         return clusters_to_split
 

### 2022-05-21 examples/benchmark/full-report.qmd
update

@@
 
-summarizer = InventorDisambiguationSummary("rawinventor.tsv", processed_data_dir=".", name="current disambiguation")
+#summarizer = InventorDisambiguationSummary("rawinventor.tsv", processed_data_dir=".", name="current disambiguation")
 ```
@@
 ```{python}
-summarizer.plot_cluster_size_distribution(range=(0.5,10.5))
+#summarizer.plot_cluster_size_distribution(range=(0.5,10.5))
 ```
@@
 ```{python}
-summarizer.get_top_inventors()
+#summarizer.get_top_inventors()
 ```
@@
 ```{python}
-summarizer.plot_entropy_curve()
+#summarizer.plot_entropy_curve()
 ```
@@
 ```{python}
-summarizer.plot_cluster_unique_name_distribution(range=(0, 100))
+#summarizer.plot_cluster_unique_name_distribution(range=(0, 100))
 ```
@@
 ```{python}
-summarizer.plot_homonymy_rate_distribution()
+#summarizer.plot_homonymy_rate_distribution()
 ```
@@
 ```{python}
-inventor_benchmark_plot(disambiguations)
+#inventor_benchmark_plot(disambiguations)
 ```
@@
 ```{python}
+from IPython.core.display import display, HTML
+
 #| column: page
@@
     inspect_clusters_to_split,
-    inspect_clusters_to_merge
+    inspect_clusters_to_merge,
+    style_cluster_inspection,
 )
 
-inspect_clusters_to_split(disambiguations["current"], load_israeli_inventors_benchmark()).to_html()
+def style_and_display(table, by="prediction"):
+    return display(HTML(style_cluster_inspection(table.reset_index(), by=by).hide_index().to_html()))
+
+style_and_display(inspect_clusters_to_split(disambiguations["current"], load_israeli_inventors_benchmark()), by="prediction")
 ```
@@
 #| column: page
-inspect_clusters_to_split(disambiguations["current"], load_patentsview_inventors_benchmark()).to_html()
+style_and_display(inspect_clusters_to_split(disambiguations["current"], load_patentsview_inventors_benchmark()), by="prediction")
 ```
@@
 #| column: page
-inspect_clusters_to_merge(disambiguations["current"], load_israeli_inventors_benchmark()).to_html()
+style_and_display(inspect_clusters_to_merge(disambiguations["current"], load_israeli_inventors_benchmark()), by="reference")
 ```
@@
 #| column: page
-inspect_clusters_to_merge(disambiguations["current"], load_patentsview_inventors_benchmark()).to_html()
+style_and_display(inspect_clusters_to_merge(disambiguations["current"], load_patentsview_inventors_benchmark()), by="reference")
 ```

### 2022-05-21 pv_evaluation/benchmark/report.py
update

@@ -55,16 +55,16 @@ def inventor_benchmark_plot(disambiguations, **kwargs):
     computed_metrics = inventor_benchmark_table(disambiguations)
     return px.bar(computed_metrics, y="value", x="metric", color="algorithm", facet_col="benchmark", barmode='group', **kwargs)
 
-def style_cluster_inspection(table):
+def style_cluster_inspection(table, by="prediction"):
     def format_color_groups(df):
         # From https://datascientyst.com/pandas-dataframe-background-color-based-condition-value-alternate-row-color-based-group/
-        colors = ['white', 'lightblue']
+        colors = ['white', '#c5dcf5']
         x = df.copy()
-        factors = list(x['prediction'].unique())
+        factors = list(x[by].unique())
         i = 0
         for factor in factors:
             style = f'background-color: {colors[i]}'
-            x.loc[x['prediction'] == factor, :] = style
+            x.loc[x[by] == factor, :] = style
             i = not i
         return x
         
@@ -82,7 +82,7 @@ def inspect_clusters_to_split(disambiguation, benchmark, join_with=None):
         .query("ref_count > 1")
         .sort_values("reference")
         .sort_values("prediction")
-        .drop("ref_count", axis=1)    
+        .drop("ref_count", axis=1)
     )
     
     if join_with is not None:

### 2022-05-21 examples/benchmark/full-report.qmd
update

@@
 
-#summarizer = InventorDisambiguationSummary("rawinventor.tsv", processed_data_dir=".", name="current disambiguation")
+summarizer = InventorDisambiguationSummary("rawinventor.tsv", processed_data_dir=".", name="current disambiguation")
 ```
@@
 ```{python}
-#summarizer.plot_cluster_size_distribution(range=(0.5,10.5))
+summarizer.plot_cluster_size_distribution(range=(0.5,10.5))
 ```
@@
 ```{python}
-#summarizer.get_top_inventors()
+summarizer.get_top_inventors()
 ```
@@
 ```{python}
-#summarizer.plot_entropy_curve()
+summarizer.plot_entropy_curve()
 ```
@@
 ```{python}
-#summarizer.plot_homonymy_rate_distribution()
+summarizer.plot_homonymy_rate_distribution()
 ```
@@
 ```{python}
-#inventor_benchmark_plot(disambiguations)
+inventor_benchmark_plot(disambiguations)
 ```
@@
 ```{python}
+#| column: page
+
 from IPython.core.display import display, HTML
 
-#| column: page
 from pv_evaluation.benchmark import (

### 2022-05-23 examples/benchmark/full-report.qmd
update

@@
 title: Inventor Disambiguation Report
+date: today
+author: PatentsView-Evaluation
+toc: true
+toc-location: left
 format:
@@
         theme: cosmo
+        echo: false
+        fig-cap-location: margin
         code-fold: true
         code-tools: true
+        code-line-numbers: true
         code-block-border-left: true
@@
         code-block-border-left: "#31BAE9"
-        echo: false
+        code-link: true
         include-in-header: header.html
@@
   cache: true
+  freeze: true
   warning: false
@@
 ```{python}
+#| label: cluster-size-distribution-plot
+#| fig-cap: This is a test caption
+#| cap-location: margin
 summarizer.plot_cluster_size_distribution(range=(0.5,10.5))
 ```
+
+:::{.callout-tip collapse="true"}
+
+## Detailed Explanation (click to expand)
+
+The above plot provides information about the number of inventors with a given number of (co-)authored patents.
+
+We can read from the plot the number of inventors with a single (co-)authored patent, with exactly two (co-)authored patents, and so forth.
+This distribution of the number of (co-)authored patents patents per inventor is equivalently called the **cluster sizes distribution** of the disambiguation.
+
+When comparing disambiguation results, look for major shifts in the cluster size distribution.
+Is one of the distribution more skewed to the left than another?
+This could indicate that one of the disambiguation favors smaller clusters, possibly resulting in higher precision but lower recall.
+
+:::
 

### 2022-05-23 examples/benchmark/full-report.qmd
update

@@
 
-The above plot provides information about the number of inventors with a given number of (co-)authored patents.
+The above plot provides the number of inventors with a given number of (co-)authored patents.
 
-We can read from the plot the number of inventors with a single (co-)authored patent, with exactly two (co-)authored patents, and so forth.
-This distribution of the number of (co-)authored patents patents per inventor is equivalently called the **cluster sizes distribution** of the disambiguation.
+We can read from the plot the number of inventors with a single authored patent, with exactly two authored patents, and so forth.
+This distribution of the number of authored patents patents per inventor is called the **cluster sizes distribution** of the disambiguation.
 
-When comparing disambiguation results, look for major shifts in the cluster size distribution.
+When comparing disambiguation results, look for shifts in shape of the cluster sizes distribution.
 Is one of the distribution more skewed to the left than another?

### 2022-05-23 examples/benchmark/full-report.qmd
sync

@@
     html:
-        theme: cosmo
+        #theme: cosmo
         echo: false

### 2022-05-23 pv_evaluation/templates/inventor/0-report.qmd
Add templates

{% include 'inventor/1-header.qmd' %}

This is report has been automatically generated for the following data sources:

- **Disambiguation summary tables:**
{% for filename in summary_table_files %}
    - {{ filename }}
{% endfor %}
- **Disambiguation results:**
{% for filename in disambiguation_files %}
    - {{ filename }}
{% endfor %}

For more information, please refer to the [PatentsView-Evaluation project homepage](https://github.com/PatentsView/PatentsView-Evaluation/) or to the report [source code](index.qmd).

{% include 'inventor/2-summary.qmd' %}

{% include 'inventor/3-benchmark.qmd' %}

### 2022-05-23 pv_evaluation/templates/inventor/callouts/between-cluster-tips.qmd
Add templates

:::{.callout-tip collapse="true"}

## Detailed Explanation (click to expand)

Between-cluster similarity is the level of similarity between different clusters. For inventor disambiguation, this is about different inventors that have similar representations on some patents, such as having the same names.

Here we look at between-cluster similarity from a binary perspective -- whether or not an inventor's name is shared with another inventor. The proportion of inventors sharing their name with someone else is our metric of between-cluster similarity which we call the **homonymy rate**.

In the plot below, the homonymy rate is plotted as a function of cluster sizes.

:::

### 2022-05-23 pv_evaluation/templates/inventor/callouts/entropy-tips.qmd
Add templates

:::{.callout-tip collapse="true"}

## Detailed Explanation (click to expand)

The Hill Numbers entropy curve is a characterization of the cluster sizes distribution.

It is based on [Hill Numbers](https://en.wikipedia.org/wiki/Diversity_index) of order $q$, which are exponentiated Rényi $q$-entropy. That is, for a given $q > 0$ and for $p_i$ the proportion of inventors with $i$ authored patents, the corresponding Hills Number is defined as 
$$
    H_q = \left ( \sum_{i=1}^{\infty} p_i^{q}\right )^{1/(1-q)}
$$
The Hill Numbers entropy curve is the plot of Hill Numbers as a function of $q > 0$.

For $q=0$, the Hill Number is defined as the number of indices $i$ such that $p_i > 0$. This is the size of the support of the cluster sizes distribution
$$
    H_0 = \# \left\{ i > 0 \,:\, p_i > 0  \right\}.
$$

For $q=1$, the Hill Number is defined as the exponentiated Shannon entropy
$$
    H_1 = \exp \left ( - \sum_{i=1}^{\infty} p_i \log p_i \right ).
$$

For $q=2$, the Hill number is the probability that two randomly sampled inventors have the same number of authored patents:
$$
    H_2 = \sum_{i=1}^{\infty} p_i^2.
$$

When comparing disambiguation results, look for major relative differences between entropy curves. These represent differences in the cluster sizes distribution which can be further investigated using the cluster sizes distribution plot.

Higher Hill Numbers represent a more spread out cluster sizes distribution, while lower values represent more peaked distributions. The order $q$ of the Hill Numbers represent how the cluster sizes proportions $p_i > 0$ are accounted for. At $q = 0$, we have the number of possible cluster sizes in the data. As $q \rightarrow \infty$, the Hill Number tends to the proportion of inventors with the most common cluster size.

:::

### 2022-05-23 pv_evaluation/templates/inventor/2-summary.qmd
Add templates

```{python}
import pandas as pd
import plotly.io as pio
pio.templates.default = "plotly_white" # Set plotly theme

from pv_evaluation.utils import compare_plots
from pv_evaluation.summary import InventorDisambiguationSummary
from pv_evaluation.benchmark import inventor_benchmark_plot
```

# Summary Statistics

```{python}
summarizers = {filename: InventorDisambiguationSummary(filename, processed_data_dir=".") for filename in {{ summary_table_files }} }
```

::: {.panel-tabset}

## Cluster Sizes

{% include 'inventor/callouts/cluster-sizes-tips.qmd' %}

```{python}
compare_plots(*[s.plot_cluster_size_distribution(range=(0.5,10.5)) for s in summarizers.values()])
```

## Top Inventors

{% include 'inventor/callouts/top-inventors-tips.qmd' %}

::: {.panel-tabset}

{% for filename in  summary_table_files%}

## {{ filename }}

```{python}
summarizers["{{ filename }}"].get_top_inventors(n=20)
```

{% endfor %}

:::

## Entropy Curve

{% include 'inventor/callouts/entropy-tips.qmd' %}

```{python}
compare_plots(*[s.plot_entropy_curve() for s in summarizers.values()])
```

## Cluster Homogeneity

{% include 'inventor/callouts/cluster-homogeneity-tips.qmd' %}

```{python}
compare_plots(*[s.plot_cluster_unique_name_distribution(range=(0, 100)) for s in summarizers.values()])
```

## Between-cluster similarity

{% include 'inventor/callouts/between-cluster-tips.qmd'%}

```{python}
compare_plots(*[s.plot_homonymy_rate_distribution() for s in summarizers.values()])
```

:::

### 2022-05-23 pv_evaluation/templates/inventor/callouts/cluster-homogeneity-tips.qmd
Add templates

:::{.callout-tip collapse="true"}

## Detailed Explanation (click to expand)

Cluster homogeneity is the level similarity of among a cluster's elements. For inventor disambiguation, this is about the variation between the way that an inventor is represented on its patents (e.g., different name spellings).

Here we look at cluster homogeneity from a binary perspective -- whether or not there is variation, within a cluster, in how an inventor's name is spelled. The proportion of inventors with a unique name (no name variation within its cluster) is our metric of cluster homogeneity called the **homogeneity rate**.

In the plot below, the homogeneity rate (i.e., clusters with no name variation) is plotted as a function of cluster size. For inventors with a single patent, the proportion of homogeneous clusters is trivially 1. For inventors with two patents, we can read off the proportion of them with no name variation, and so forth.

When comparing two disambiguation results, look for changes in the homogeneity rate across cluster sizes. A higher homogeneity rate means possibly smaller, more robust clusters. On the other hand, lower homogeneity rates may be associated with an increased error probability.

:::

### 2022-05-23 pv_evaluation/templates/inventor/callouts/cluster-sizes-tips.qmd
Add templates

--- 2022-05-23 examples/benchmark/full-report.qmd
@@
----
-title: Inventor Disambiguation Report
-date: today
-author: PatentsView-Evaluation
-toc: true
-toc-location: left
-format:
-    html:
-        theme: cosmo
-        echo: false
-        fig-cap-location: margin
-        code-fold: true
-        code-tools: true
-        code-line-numbers: true
-        code-block-border-left: true
-        code-copy: true
-        code-block-border-left: "#31BAE9"
-        code-link: true
-        include-in-header: header.html
-        include-after-body: footer.html
-execute:
-  cache: true
-  freeze: true
-  warning: false
-  message: false
-jupyter: python3
----
-
-<!--
-## Data Preparation
-
-First, we prepare the disambiguation result data to evaluate.
-We consider the current PatentsView disambiguation, obtained from the `rawinventor.tsv` data file, as well as one trivial disambiguation where all inventor mentions are clustered together.
-
-The code below reads the disambiguation result from `rawinventor.tsv`.
-A disambiguation result is defined as a pandas Series with an index representing mention IDs and values representing cluster assignement.
-
-Mention IDs are standardized to be of the form `<OFFICE><PATENT_NUMBER>-<INVENTOR_SEQUENCE>`, where OFFICE is the patent issuer office abbreviation (e.g.
-"US" or "EPO"), PATENT_NUMBER is the standard patent number form, and INVENTOR_SEQUENCE is the inventor's position on the given patent, starting from 0.
-For example, the mention ID
-> US5811073-0
-represents the first listed inventor on US patent number 5811073.
--->
-```{python}
-#| label: data-prep
-#| code-fold: true
-import pandas as pd
-
-import wget
-import zipfile
-import os
-
-import plotly.io as pio
-pio.templates.default = "plotly_white" # Set plotly theme
-
-if not os.path.isfile("rawinventor.tsv"):
-    wget.download("https://s3.amazonaws.com/data.patentsview.org/download/rawinventor.tsv.zip")
-    with zipfile.ZipFile("rawinventor.tsv.zip", 'r') as zip_ref:
-        zip_ref.extractall(".")
-    os.remove("rawinventor.tsv.zip")
-
-if not os.path.isfile("disambiguation.tsv"):
-    rawinventor = pd.read_csv("rawinventor.tsv", sep="\t")
-    rawinventor["mention-id"] = "US" + rawinventor.patent_id.astype(str) + "-" + rawinventor.sequence.astype(str)
-    rawinventor[["mention-id", "inventor_id"]].to_csv("disambiguation.tsv", sep="\t", index=False)
-    del(rawinventor)
-
-data = pd.read_csv("disambiguation.tsv", sep="\t")
-data.set_index("mention-id", inplace=True)
-current_disambiguation = data["inventor_id"]
-```
-
-<!--
-Next, we define a dictionary describing the two disambiguations to compare, i.e. the "current" disambiguation and the "one cluster" trivial disambiguation.-->
-
-```{python}
-#| label: disambiguations
-#| code-fold: false
-
-disambiguations = {
-    "current": current_disambiguation,
-    "one cluster": 0*current_disambiguation
-}
-```
-
-<!--
-We can now generate the disambiguation report using `disambiguations` and `rawinventor.tsv` as the input.
--->
-
-## Summary Statistics
-
-```{python}
-#| label: imports
-
-import wget
-import zipfile
-import os
-
-import plotly.io as pio
-pio.templates.default = "plotly_white" # Set plotly theme
-
-from pv_evaluation.summary import InventorDisambiguationSummary
-from pv_evaluation.benchmark import inventor_benchmark_plot
-
-summarizer = InventorDisambiguationSummary("rawinventor.tsv", processed_data_dir=".", name="current disambiguation")
-```
-
-::: {.panel-tabset}
-
-### Cluster Sizes
-
-```{python}
-#| label: cluster-size-distribution-plot
-#| fig-cap: This is a test caption
-#| cap-location: margin
-summarizer.plot_cluster_size_distribution(range=(0.5,10.5))
-```
-
 :::{.callout-tip collapse="true"}
@@
 
-The above plot provides the number of inventors with a given number of (co-)authored patents.
+The plot below provides the number of inventors with a given number of (co-)authored patents.
 
@@
 :::
-
-### Top Inventors
-
-```{python}
-#summarizer.get_top_inventors()
-```
-
-### Entropy Curve
-
-```{python}
-#summarizer.plot_entropy_curve()
-```
-
-### Cluster Homogeneity
-
-```{python}
-#summarizer.plot_cluster_unique_name_distribution(range=(0, 100))
-```
-
-### Cluster Separation
-
-```{python}
-#summarizer.plot_homonymy_rate_distribution()
-```
-
-:::
-
-## Benchmark Evaluation
-
-::: {.panel-tabset}
-
-### Evaluation Results
-
-```{python}
-inventor_benchmark_plot(disambiguations)
-```
-
-### Predicted Cluster Errors
-
-::: {.panel-tabset}
-
-#### Israeli Inventors
-
-```{python}
-#| column: page
-
-from IPython.core.display import display, HTML
-
-from pv_evaluation.benchmark import (
-    load_israeli_inventors_benchmark,
-    load_patentsview_inventors_benchmark,
-    inspect_clusters_to_split,
-    inspect_clusters_to_merge,
-    style_cluster_inspection,
-)
-
-def style_and_display(table, by="prediction"):
-    return display(HTML(style_cluster_inspection(table.reset_index(), by=by).hide_index().to_html()))
-
-style_and_display(inspect_clusters_to_split(disambiguations["current"], load_israeli_inventors_benchmark()), by="prediction")
-```
-
-#### PatentsView Inventors
-
-```{python}
-#| column: page
-style_and_display(inspect_clusters_to_split(disambiguations["current"], load_patentsview_inventors_benchmark()), by="prediction")
-```
-
-:::
-
-### Reference Cluster Errors
-
-::: {.panel-tabset}
-
-#### Israeli Inventors
-
-```{python}
-#| column: page
-style_and_display(inspect_clusters_to_merge(disambiguations["current"], load_israeli_inventors_benchmark()), by="reference")
-```
-
-#### PatentsView Inventors
-
-```{python}
-#| column: page
-style_and_display(inspect_clusters_to_merge(disambiguations["current"], load_patentsview_inventors_benchmark()), by="reference")
-```
-
-:::
-
-:::
-
-## Representative Performance Estimates

### 2022-05-23 pv_evaluation/templates/__init__.py

@@ -1,0 +1,1 @@
+from .render import render_inventor_disambiguation_report

### 2022-05-23 pv_evaluation/templates/render.py

@@ -1,0 +1,21 @@
+import os
+import quarto
+from jinja2 import Environment, PackageLoader
+import shutil
+from pkg_resources import resource_filename
+
+
+def render_inventor_disambiguation_report(outdir, disambiguation_files, summary_table_files, execute=True, cache=True, **kwargs):
+    env = Environment(loader=PackageLoader("pv_evaluation", package_path="templates"))
+    template = env.get_template("inventor/0-report.qmd")
+
+    qmdpath = os.path.join(outdir, "index.qmd")
+    htmlpath = os.path.join(outdir, "index.html")
+
+    shutil.copyfile(resource_filename("pv_evaluation", "templates/inventor/header.html"), os.path.join(outdir, "header.html"))
+    shutil.copyfile(resource_filename("pv_evaluation", "templates/inventor/footer.html"), os.path.join(outdir, "footer.html"))
+
+    with open(qmdpath, "w+") as file:
+        file.write(template.render(disambiguation_files=disambiguation_files, summary_table_files=summary_table_files))
+    
+    quarto.render(qmdpath, output_format = "html", output_file = htmlpath, execute = execute, cache = cache, **kwargs)

### 2022-05-23 pv_evaluation/summary/inventor_disambiguation_summary.py
update

@@ -21,7 +21,7 @@ def read_auto(datapath) -> dd.DataFrame:
 
 
 class InventorDisambiguationSummary:
-    def __init__(self, datapath, processed_data_dir=None, name=""):
+    def __init__(self, datapath, processed_data_dir=None, name=None):
         """Report inventor disambiguation summaries. Object instanciation is used to manage data pre-processing and speed up some of the computations.
 
         Args:
@@ -32,7 +32,10 @@ class InventorDisambiguationSummary:
                 Defaults to None for a temporary directory.
             name (str): Name of the disambiguation algorithm to show in plots.
         """
-        self.name = name
+        if name is None:
+            self.name = datapath
+        else:
+            self.name = name
 
         if processed_data_dir is None:
             processed_data_dir = tempfile.mkdtemp()

### 2022-05-25 examples/templates/index.qmd
update; not enough memory

---
title: Inventor Disambiguation Report
date: today
author: PatentsView-Evaluation
toc: true
toc-location: left
toc-depth: 3
format:
    html:
        self-contained: true
        theme: cosmo
        echo: false
        fig-cap-location: margin
        code-fold: true
        code-tools: true
        code-line-numbers: true
        code-block-border-left: true
        code-copy: true
        code-block-border-left: "#31BAE9"
        code-link: true
        include-in-header: header.html
        include-after-body: footer.html
execute:
  cache: true
  freeze: auto
  warning: false
  message: false
jupyter: python3
---

This is report has been automatically generated for the following data sources:

- **Disambiguation summary tables:**

    - rawinventor.parquet

For more information, please refer to the [PatentsView-Evaluation project homepage](https://github.com/PatentsView/PatentsView-Evaluation/) or to the report [source code](index.qmd).

```{python}
import pandas as pd
import plotly.io as pio
pio.templates.default = "plotly_white" # Set plotly theme

from pv_evaluation.utils import compare_plots
from pv_evaluation.summary import InventorDisambiguationSummary
from pv_evaluation.benchmark import inventor_benchmark_plot
```

# Summary Statistics

```{python}
summarizers = {filename: InventorDisambiguationSummary(filename) for filename in ['rawinventor.parquet'] }
```

::: {.panel-tabset}

## Cluster Sizes

:::{.callout-tip collapse="true"}

## Detailed Explanation (click to expand)

The plot below provides the number of inventors with a given number of (co-)authored patents.

We can read from the plot the number of inventors with a single authored patent, with exactly two authored patents, and so forth. This distribution of the number of authored patents patents per inventor is called the **cluster sizes distribution** of the disambiguation.

When comparing disambiguation results, look for shifts in shape of the cluster sizes distribution. Is one of the distribution more skewed to the left than another? This could indicate that one of the disambiguation favors smaller clusters, possibly resulting in higher precision but lower recall.

:::

```{python}
compare_plots(*[s.plot_cluster_size_distribution() for s in summarizers.values()])
```

## Top Inventors

:::{.callout-tip collapse="true"}

## Detailed Explanation (click to expand)

The table below provides the inventors with the largest number of authored patents.

Make sure to sort the table by number of patents.

When comparing disambiguation results, look for large changes in the ranking of inventors. Large changes in the estimated numbers of authored patents may also warrant the need to investigate the behavior of the disambiguation for these prolific inventors.

:::

::: {.panel-tabset}

## rawinventor.parquet

```{python}
summarizers["rawinventor.parquet"].get_top_inventors(n=20)
```

:::

## Entropy Curve

:::{.callout-tip collapse="true"}

## Detailed Explanation (click to expand)

The Hill Numbers entropy curve is a characterization of the cluster sizes distribution.

It is based on [Hill Numbers](https://en.wikipedia.org/wiki/Diversity_index) of order $q$, which are exponentiated Rényi $q$-entropy. That is, for a given $q > 0$ and for $p_i$ the proportion of inventors with $i$ authored patents, the corresponding Hills Number is defined as 
$$
    H_q = \left ( \sum_{i=1}^{\infty} p_i^{q}\right )^{1/(1-q)}
$$
The Hill Numbers entropy curve is the plot of Hill Numbers as a function of $q > 0$.

For $q=0$, the Hill Number is defined as the number of indices $i$ such that $p_i > 0$. This is the size of the support of the cluster sizes distribution
$$
    H_0 = \# \left\{ i > 0 \,:\, p_i > 0  \right\}.
$$

For $q=1$, the Hill Number is defined as the exponentiated Shannon entropy
$$
    H_1 = \exp \left ( - \sum_{i=1}^{\infty} p_i \log p_i \right ).
$$

For $q=2$, the Hill number is the probability that two randomly sampled inventors have the same number of authored patents:
$$
    H_2 = \sum_{i=1}^{\infty} p_i^2.
$$

When comparing disambiguation results, look for major relative differences between entropy curves. These represent differences in the cluster sizes distribution which can be further investigated using the cluster sizes distribution plot.

Higher Hill Numbers represent a more spread out cluster sizes distribution, while lower values represent more peaked distributions. The order $q$ of the Hill Numbers represent how the cluster sizes proportions $p_i > 0$ are accounted for. At $q = 0$, we have the number of possible cluster sizes in the data. As $q \rightarrow \infty$, the Hill Number tends to the proportion of inventors with the most common cluster size.

:::

```{python}
compare_plots(*[s.plot_entropy_curve() for s in summarizers.values()])
```

## Cluster Homogeneity

:::{.callout-tip collapse="true"}

## Detailed Explanation (click to expand)

Cluster homogeneity is the level similarity of among a cluster's elements. For inventor disambiguation, this is about the variation between the way that an inventor is represented on its patents (e.g., different name spellings).

Here we look at cluster homogeneity from a binary perspective -- whether or not there is variation, within a cluster, in how an inventor's name is spelled. The proportion of inventors with a unique name (no name variation within its cluster) is our metric of cluster homogeneity called the **homogeneity rate**.

In the plot below, the homogeneity rate (i.e., clusters with no name variation) is plotted as a function of cluster size. For inventors with a single patent, the proportion of homogeneous clusters is trivially 1. For inventors with two patents, we can read off the proportion of them with no name variation, and so forth.

When comparing two disambiguation results, look for changes in the homogeneity rate across cluster sizes. A higher homogeneity rate means possibly smaller, more robust clusters. On the other hand, lower homogeneity rates may be associated with an increased error probability.

:::

```{python}
compare_plots(*[s.plot_cluster_unique_name_distribution() for s in summarizers.values()])
```

## Between-cluster similarity

:::{.callout-tip collapse="true"}

## Detailed Explanation (click to expand)

Between-cluster similarity is the level of similarity between different clusters. For inventor disambiguation, this is about different inventors that have similar representations on some patents, such as having the same names.

Here we look at between-cluster similarity from a binary perspective -- whether or not an inventor's name is shared with another inventor. The proportion of inventors sharing their name with someone else is our metric of between-cluster similarity which we call the **homonymy rate**.

In the plot below, the homonymy rate is plotted as a function of cluster sizes.

:::

```{python}
compare_plots(*[s.plot_homonymy_rate_distribution() for s in summarizers.values()])
```

:::

```{python}
import pandas as pd
import os

def read_disambiguation(filename):
    _, ext = os.path.splitext(filename)

    if ext == ".csv":
        df = pd.read_csv(filename)
    elif ext == ".tsv":
        df = pd.read_csv(filename, sep="\t")
    elif ext in [".parquet", ".pq", ".parq"]:
        df = pd.read_parquet(filename)
    else:
        raise Exception("Unsupported file type. Should be one of csv, tsv, or parquet.")

    df.set_index("mention-id", inplace=True)

    return df["patent_id"]

disambiguations = {filename: read_disambiguation(filename) for filename in ['rawinventor.parquet'] }
```

# Benchmark Evaluation

::: {.panel-tabset}

## Evaluation Results

```{python}
inventor_benchmark_plot(disambiguations)
```

## Predicted Cluster Errors

```{python}
from IPython.core.display import display, HTML

from pv_evaluation.benchmark import (
    load_israeli_inventors_benchmark,
    load_patentsview_inventors_benchmark,
    inspect_clusters_to_split,
    inspect_clusters_to_merge,
    style_cluster_inspection,
)

def style_and_display(table, by="prediction"):
    return display(HTML(style_cluster_inspection(table.reset_index(), by=by).hide_index().to_html()))
```

::: {.panel-tabset}

### rawinventor.parquet

::: {.panel-tabset}

#### Israeli Inventors

```{python}
#| column: page
style_and_display(inspect_clusters_to_split(disambiguations["rawinventor.parquet"], load_israeli_inventors_benchmark()), by="prediction")
```

#### PatentsView Inventors

```{python}
#| column: page
style_and_display(inspect_clusters_to_split(disambiguations["rawinventor.parquet"], load_patentsview_inventors_benchmark()), by="prediction")
```

:::

:::

## Reference Cluster Errors

::: {.panel-tabset}

### rawinventor.parquet

::: {.panel-tabset}

#### Israeli Inventors

```{python}
#| column: page
style_and_display(inspect_clusters_to_merge(disambiguations["rawinventor.parquet"], load_israeli_inventors_benchmark()), by="reference")
```

#### PatentsView Inventors

```{python}
#| column: page
style_and_display(inspect_clusters_to_merge(disambiguations["rawinventor.parquet"], load_patentsview_inventors_benchmark()), by="reference")
```

:::

:::

:::

### 2022-05-25 pv_evaluation/summary/inventor_disambiguation_summary.py

@@ -21,36 +21,17 @@ def read_auto(datapath) -> dd.DataFrame:
 
 
 class InventorDisambiguationSummary:
-    def __init__(self, datapath, processed_data_dir=None, name=None):
-        """Report inventor disambiguation summaries. Object instanciation is used to manage data pre-processing and speed up some of the computations.
+    def __init__(self, datapath, name=None):
+        """Report inventor disambiguation summaries.
 
         Args:
             datapath (str): Path to the inventor disambiguation data (csv, tsv or parquet format).
                 The data should have four columns: "patent_id", "inventor_id", "name_first", and "name_last".
-            processed_data_dir (str, optional): Path to a directory where to store processed data.
-                Data from past runs will be re-used if it is found in this directory.
-                Defaults to None for a temporary directory.
-            name (str): Name of the disambiguation algorithm to show in plots.
+            name (str): Name of the disambiguation algorithm to show in plots. Defaults to the provided datapath.
         """
-        if name is None:
-            self.name = datapath
-        else:
-            self.name = name
+        self.name = datapath if name is None else name
 
-        if processed_data_dir is None:
-            processed_data_dir = tempfile.mkdtemp()
-            self.tempdir = processed_data_dir
-
-        self._parquet_datapath = os.path.join(processed_data_dir, "processed_inventor_disambiguation_data.parquet")
-        if os.path.exists(self._parquet_datapath):
-            self._data = dd.read_parquet(self._parquet_datapath)
-        else:
-            self._data = read_auto(datapath)
-
-            # Save indexed data as a parquet file.
-            self._data.set_index("inventor_id").to_parquet(self._parquet_datapath)
-            self._data = dd.read_parquet(self._parquet_datapath)
-
+        self._data = read_auto(datapath)
         self._validate_data()
 
         # Lazy initialization

### 2022-05-25 pv_evaluation/templates/inventor/callouts/cluster-errors-tips.qmd
add callout tips

:::{.callout-tip collapse="true"}

## Detailed Explanation (click to expand)

Cluster error tabs (predicted cluster errors and reference cluster errors) allow you to investigate clusters which contain errors.

**Predicted cluster errors** are about predicted clusters which should have been split up in two or more parts, according to the reference data.

To investigate predicted cluster errors, sort the table by `prediction` id and look for mismatching `reference` ids within predicted clusters.

**Reference cluster errors are about predicted clusters which should be merged together, according to the reference data.

To investigate reference cluster errors, sort the table by `reference` id and look for mismatching `cluster` ids within reference clusters.

:::

### 2022-05-25 pv_evaluation/templates/inventor/callouts/metrics-tips.qmd
add callout tips

:::{.callout-tip collapse="true"}

## Detailed Explanation (click to expand)

Performance evaluation metrics compare predicted clusters to a reference clustering from benchmark datasets.

Note that to compute performance evaluation metrics, predicted clusters are first restricted to mentions which appear in the reference data. Performance evaluation metrics on benchmark datasets are not at all representative of performance on the full data.

Commonly used metrics are defined below.

- **Pairwise precision:** Proportion of predicted links (pairs of mentions in the same predicted cluster) which are also linked under the reference clustering.
- **Pairwise recall:** Proportion of links in the reference clustering (pairs of mentions in the same reference cluster) which are also linked under the predicted clustering.
- **Pairwise f-score:** Harmonic mean between pairwise precision and pairwise recall.
- **Cluster precision:** Proportion of predicted clusters which are entirely contained within a single reference cluster. That is, cluster precision is the proportion of predicted clusters which are not split up in the reference clustering.
- **Cluster recall:** Proportion of reference clusters which are entirely contained within a single predicted cluster. That is, cluster recall is the proportion of reference clusters which are not split up in the predicted clusters.
- **Cluster f-score:** Harmonic mean between pairwise precision and pairwise recall.

:::

### 2022-05-25 pv_evaluation/benchmark/data.py
Docs (#9)
* update

* add sphinx doc

* update

* add html docs

* add module docs

* update

@@ -4,6 +4,15 @@ import pandas as pd
 INVENTOR_DATA_MODULE = "pv_evaluation.data.inventor"
 
 def load_unique_id_series(module, filename):
+    """Load disambiguation series from csv file with columns "unique-id" and "mention-id".
+
+    Args:
+        module (str): module where file is located.
+        filename (str): csv filename.
+
+    Returns:
+        Series: pandas series named "unique-id" and with "mention-id" as an index.
+    """
     with resources.open_text(module, filename) as f:
         data = pd.read_csv(f)
     

### 2022-05-25 pv_evaluation/data/__init__.py

@@ -1,0 +1,2 @@
+"""Benchmark datasets.
+"""

### 2022-05-25 pv_evaluation/metrics/__init__.py

@@ -1,3 +1,6 @@
+"""Performance evaluation metrics.
+"""
+
 from .pairwise import (
     cluster_sizes,
     links_count,
@@ -19,7 +22,9 @@ from .cluster import (
     cluster_fowlkes_mallows,
     cluster_homogeneity,
     cluster_completeness,
-    cluster_v_measure
+    cluster_v_measure,
+    rand_score,
+    adjusted_rand_score,
 )
 
 __all__ = [
@@ -40,5 +45,8 @@ __all__ = [
     "cluster_fowlkes_mallows",
     "cluster_homogeneity",
     "cluster_completeness",
-    "cluster_v_measure"
+    "cluster_v_measure",
+    "rand_score",
+    "adjusted_rand_score",
+
 ]

### 2022-05-25 pv_evaluation/summary/__init__.py

@@ -1,3 +1,6 @@
+"""Disambiguation summary statistics.
+"""
+
 from .inventor_disambiguation_summary import InventorDisambiguationSummary
 
 __all__ = ["InventorDisambiguationSummary"]

### 2022-05-25 pv_evaluation/summary/inventor_disambiguation_summary.py

@@ -94,7 +94,7 @@ class InventorDisambiguationSummary:
             .rename(columns={"patent_id": "Number of patents"})
         )
 
-    def plot_cluster_size_distribution(self, range=(0, 10)):
+    def plot_cluster_size_distribution(self, range=(0, 20)):
         """Plot the distribution of the number of patents per inventor
 
         Args:
@@ -164,7 +164,7 @@ class InventorDisambiguationSummary:
 
         return self._cluster_unique_name_distribution.copy()
 
-    def plot_cluster_unique_name_distribution(self, range=(0, 200)):
+    def plot_cluster_unique_name_distribution(self, range=(0, 100)):
         """Plot the proportion of homogeneous clusters (no name variation) by cluster size."""
         data = self.get_cluster_unique_name_distribution()
         fig = px.bar(
@@ -178,6 +178,7 @@ class InventorDisambiguationSummary:
         ylim = max(data["Proportion of unique name"][data["Number of patents"].between(range[0], range[1])])
         fig.update_yaxes(range=(0, ylim), autorange=False)
 
+        fig.update_traces(name=self.name)
         return fig
 
     def get_homonymy_rate_distribution(self):
@@ -209,7 +210,7 @@ class InventorDisambiguationSummary:
 
         return self._homonymy_rate_distribution.copy()
 
-    def plot_homonymy_rate_distribution(self, range=(0, 10)):
+    def plot_homonymy_rate_distribution(self, range=(0, 100)):
         """Plot homonymy rate by cluster size.
 
         The homonymy rate is the proportion of clusters which share at least one name mention with another cluster.

### 2022-05-25 pv_evaluation/templates/render.py

@@ -5,7 +5,14 @@ import shutil
 from pkg_resources import resource_filename
 
 
-def render_inventor_disambiguation_report(outdir, disambiguation_files, summary_table_files, execute=True, cache=True, **kwargs):
+def render_inventor_disambiguation_report(outdir, summary_table_files, cache=True, **kwargs):
+    """Create html report based on disambiguation results.
+
+    Args:
+        outdir (str): Directory where to output html files.
+        summary_table_files (list): List of paths to disambiguation table files (tables with the five columns "mention-id", "inventor_id", "patent_id", "name_first", and "name_last").
+        cache (bool, optional): Whether or not to cache jupyter chunk execution between runs. Defaults to True.
+    """
     env = Environment(loader=PackageLoader("pv_evaluation", package_path="templates"))
     template = env.get_template("inventor/0-report.qmd")
 
@@ -16,6 +23,9 @@ def render_inventor_disambiguation_report(outdir, disambiguation_files, summary_
     shutil.copyfile(resource_filename("pv_evaluation", "templates/inventor/footer.html"), os.path.join(outdir, "footer.html"))
 
     with open(qmdpath, "w+") as file:
-        file.write(template.render(disambiguation_files=disambiguation_files, summary_table_files=summary_table_files))
+        file.write(template.render(summary_table_files=summary_table_files))
     
-    quarto.render(qmdpath, output_format = "html", output_file = htmlpath, execute = execute, cache = cache, **kwargs)
+    if quarto.path() is None:
+        raise Exception("Could not find quarto. Is quarto (quarto.org) installed?")
+
+    quarto.render(qmdpath, output_format = "html", output_file = htmlpath, execute = True, cache = cache, **kwargs)

### 2022-05-25 examples/templates/index.qmd
Docs (#9)
* update

* add sphinx doc

* update

* add html docs

* add module docs

* update

@@
 
-    - rawinventor.parquet
+    - rawinventor.tsv
+
+- **Disambiguation results:**
+
+    - disambiguation.tsv
 
@@
 ```{python}
-summarizers = {filename: InventorDisambiguationSummary(filename) for filename in ['rawinventor.parquet'] }
+summarizers = {filename: InventorDisambiguationSummary(filename, processed_data_dir=".") for filename in ['rawinventor.tsv'] }
 ```
@@
 ```{python}
-compare_plots(*[s.plot_cluster_size_distribution() for s in summarizers.values()])
+compare_plots(*[s.plot_cluster_size_distribution(range=(0.5,10.5)) for s in summarizers.values()])
 ```
@@
 
-## rawinventor.parquet
+## rawinventor.tsv
 
 ```{python}
-summarizers["rawinventor.parquet"].get_top_inventors(n=20)
+summarizers["rawinventor.tsv"].get_top_inventors(n=20)
 ```
@@
 ```{python}
-compare_plots(*[s.plot_cluster_unique_name_distribution() for s in summarizers.values()])
+compare_plots(*[s.plot_cluster_unique_name_distribution(range=(0, 100)) for s in summarizers.values()])
 ```
@@
 
-    return df["patent_id"]
+    return df[df.columns[0]]
 
-disambiguations = {filename: read_disambiguation(filename) for filename in ['rawinventor.parquet'] }
+disambiguations = {filename: read_disambiguation(filename) for filename in ['disambiguation.tsv'] }
 ```
@@
 
-### rawinventor.parquet
+### disambiguation.tsv
 
@@
 #| column: page
-style_and_display(inspect_clusters_to_split(disambiguations["rawinventor.parquet"], load_israeli_inventors_benchmark()), by="prediction")
+style_and_display(inspect_clusters_to_split(disambiguations["disambiguation.tsv"], load_israeli_inventors_benchmark()), by="prediction")
 ```
@@
 #| column: page
-style_and_display(inspect_clusters_to_split(disambiguations["rawinventor.parquet"], load_patentsview_inventors_benchmark()), by="prediction")
+style_and_display(inspect_clusters_to_split(disambiguations["disambiguation.tsv"], load_patentsview_inventors_benchmark()), by="prediction")
 ```
@@
 #| column: page
-style_and_display(inspect_clusters_to_merge(disambiguations["rawinventor.parquet"], load_israeli_inventors_benchmark()), by="reference")
+style_and_display(inspect_clusters_to_merge(disambiguations["disambiguation.tsv"], load_israeli_inventors_benchmark()), by="reference")
 ```
@@
 #| column: page
-style_and_display(inspect_clusters_to_merge(disambiguations["rawinventor.parquet"], load_patentsview_inventors_benchmark()), by="reference")
+style_and_display(inspect_clusters_to_merge(disambiguations["disambiguation.tsv"], load_patentsview_inventors_benchmark()), by="reference")
 ```

### 2022-05-25 pv_evaluation/templates/inventor/0-report.qmd
Docs (#9)
* update

* add sphinx doc

* update

* add html docs

* add module docs

* update

@@
 {% endfor %}
-- **Disambiguation results:**
-{% for filename in disambiguation_files %}
-    - {{ filename }}
-{% endfor %}
 

### 2022-05-25 pv_evaluation/templates/inventor/2-summary.qmd
Docs (#9)
* update

* add sphinx doc

* update

* add html docs

* add module docs

* update

@@
 ```{python}
-compare_plots(*[s.plot_cluster_size_distribution(range=(0.5,10.5)) for s in summarizers.values()])
+compare_plots(*[s.plot_cluster_size_distribution() for s in summarizers.values()])
 ```
@@
 ```{python}
-compare_plots(*[s.plot_cluster_unique_name_distribution(range=(0, 100)) for s in summarizers.values()])
+compare_plots(*[s.plot_cluster_unique_name_distribution() for s in summarizers.values()])
 ```

### 2022-05-25 pv_evaluation/benchmark/__init__.py

@@ -1,3 +1,6 @@
+"""Evaluation datasets and standardized benchmarks.
+"""
+
 from .data import (
     load_israeli_inventors_benchmark,
     load_harvard_inventors_benchmark,

### 2022-05-25 pv_evaluation/metrics/cluster.py

@@ -1,3 +1,6 @@
+"""Cluster performance metrics.
+"""
+
 from textwrap import wrap
 import numpy as np
 from scipy.special import comb
@@ -123,17 +126,48 @@ def wrap_sklearn_metric(sklearn_metric):
     return func
 
 def cluster_homogeneity(prediction, reference):
-    
-    
+    """Cluster homogeneity score (based on conditional entropy).
+
+    This wraps scikit-learn's [homogeneity score function](https://scikit-learn.org/stable/modules/generated/sklearn.metrics.homogeneity_score.html).
+
+    Args:
+        prediction (Series):  membership vector for predicted clusters, i.e. a pandas Series indexed by mention ids and with values representing predicted cluster assignment. 
+        reference (Series):  membership vector for reference clusters, i.e. a pandas Series indexed by mention ids and with values representing reference cluster assignment. 
+
+    Returns:
+        float: homogeneity score
+    """
     return wrap_sklearn_metric(sm.homogeneity_score)(prediction, reference)
 
 def cluster_completeness(prediction, reference):
+    """Cluster completeness score (based on conditional entropy)
+
+    This wraps scikit-learn's [completeness score function](https://scikit-learn.org/stable/modules/generated/sklearn.metrics.completeness_score.html).
+
+    Args:
+        prediction (Series):  membership vector for predicted clusters, i.e. a pandas Series indexed by mention ids and with values representing predicted cluster assignment. 
+        reference (Series):  membership vector for reference clusters, i.e. a pandas Series indexed by mention ids and with values representing reference cluster assignment. 
+
+    Returns:
+        float: completeness score
+    """
     return wrap_sklearn_metric(sm.completeness_score)(prediction, reference)
 
 def cluster_v_measure(prediction, reference, beta=1.0):
     return wrap_sklearn_metric(sm.v_measure_score)(prediction, reference, beta=beta)
 
 def rand_score(prediction, reference):
+    """Compute the Rand index.
+
+    This wraps scikit-learn's [rand index function](https://scikit-learn.org/stable/modules/generated/sklearn.metrics.rand_score.html#sklearn.metrics.rand_score).
+
+    Args:
+        prediction (Series):  membership vector for predicted clusters, i.e. a pandas Series indexed by mention ids and with values representing predicted cluster assignment. 
[…]

### 2022-05-25 pv_evaluation/metrics/pairwise.py

@@ -1,3 +1,6 @@
+"""Pairwise link-based classification metrics.
+"""
+
 import numpy as np
 from scipy.special import comb
 import pandas as pd

### 2022-05-25 pv_evaluation/templates/__init__.py

@@ -1,1 +1,8 @@
+"""HTML report templates.
+"""
+
 from .render import render_inventor_disambiguation_report
+
+__all__ = [
+    "render_inventor_disambiguation_report",
+]

### 2022-05-31 examples/templates/index.qmd
update

--- 2022-05-25 examples/templates/index.qmd
@@
 
-    - rawinventor.parquet
+    - rawinventor.tsv
 
@@
 
-disambiguations = {filename: read_disambiguation(filename) for filename in ['rawinventor.parquet'] }
+disambiguations = {filename: read_disambiguation(filename) for filename in ['rawinventor.tsv'] }
 ```
@@
 
-### rawinventor.parquet
+### rawinventor.tsv
 
@@
 #| column: page
-style_and_display(inspect_clusters_to_split(disambiguations["rawinventor.parquet"], load_israeli_inventors_benchmark()), by="prediction")
+style_and_display(inspect_clusters_to_split(disambiguations["rawinventor.tsv"], load_israeli_inventors_benchmark()), by="prediction")
 ```
@@
 #| column: page
-style_and_display(inspect_clusters_to_split(disambiguations["rawinventor.parquet"], load_patentsview_inventors_benchmark()), by="prediction")
+style_and_display(inspect_clusters_to_split(disambiguations["rawinventor.tsv"], load_patentsview_inventors_benchmark()), by="prediction")
 ```
@@
 #| column: page
-style_and_display(inspect_clusters_to_merge(disambiguations["rawinventor.parquet"], load_israeli_inventors_benchmark()), by="reference")
+style_and_display(inspect_clusters_to_merge(disambiguations["rawinventor.tsv"], load_israeli_inventors_benchmark()), by="reference")
 ```
@@
 #| column: page
-style_and_display(inspect_clusters_to_merge(disambiguations["rawinventor.parquet"], load_patentsview_inventors_benchmark()), by="reference")
+style_and_display(inspect_clusters_to_merge(disambiguations["rawinventor.tsv"], load_patentsview_inventors_benchmark()), by="reference")
 ```

### 2022-05-31 pv_evaluation/estimators.py

@@ -23,7 +23,7 @@ def pairwise_precision_estimator(prediction, reference, sampling_type=["record",
     inner = pd.concat({"prediction":prediction, "reference":reference}, axis=1, join="inner", copy=False)
     vals = inner.groupby(["prediction", "reference"]).size()
     f_sum = vals.to_frame().assign(cmb=comb(vals.values, 2)).groupby("reference").sum().cmb
-    cluster_sizes = reference.value_counts(sort=False).values
+    cluster_sizes = inner.reference.value_counts(sort=False).values
     P = np.sum(comb(prediction.value_counts(sort=False).values, 2))
 
     if sampling_type == "record":
@@ -39,7 +39,7 @@ def pairwise_precision_estimator(prediction, reference, sampling_type=["record",
     elif sampling_type == "single_block":
         TP_block = np.sum(comb(vals.values, 2))
         P_block = np.sum(comb(inner.prediction.value_counts(sort=False).values, 2))
-        I = [i for i in prediction.index if prediction[i] in inner.prediction.values]
+        I = prediction.isin(inner.prediction)
         P_block_plus = np.sum(comb(prediction[I].value_counts(sort=False).values, 2))
         return 2 * TP_block / (P_block + P_block_plus)
     else:

### 2022-06-01 setup.py
Refactor (#10)
* update

* add sphinx doc

* update

* add html docs

* add module docs

* update

* update; not enough memory

* add callout tips

@@ -11,5 +11,16 @@ if __name__ == "__main__":
         url="https://github.com/OlivierBinette/PatentsView-Evaluation",
         include_package_data=True,
         packages=find_packages(),
-        install_requires=["pandas", "dask", "matplotlib", "fastparquet", "numpy", "plotly", "sklearn"],
+        install_requires=[
+            "pandas", 
+            "dask", 
+            "matplotlib", 
+            "pyarrow", 
+            "python-snappy",
+            "numpy", 
+            "plotly", 
+            "sklearn", 
+            "quarto",
+            "jinja2",
+        ],
     )

### 2022-06-03 pv_evaluation/metrics/pairwise.py
Estimators (#11)
* Add precision estimators

* update

* update

* run black

* update

* Add first example notebook and figure

* tweak figures

* Fix bug

* update

Co-authored-by: Ubuntu <ubuntu@ip-172-31-17-126.ec2.internal>

@@ -6,6 +6,7 @@ from scipy.special import comb
 import pandas as pd
 from .utils import validate_membership
 
+
 def cluster_sizes(membership_vect):
     """Get cluster sizes for a given membership vector.
 
@@ -16,7 +17,7 @@ def cluster_sizes(membership_vect):
         Series: cluster sizes
     """
     validate_membership(membership_vect)
-    
+
     return membership_vect.value_counts(sort=False).values
 
 
@@ -30,7 +31,7 @@ def links_count(membership_vect):
         
     Returns:
         int: number of links
-    """    
+    """
     return np.sum(comb(cluster_sizes(membership_vect), 2))
 
 
@@ -47,8 +48,8 @@ def true_positives_count(prediction, reference):
     """
     validate_membership(prediction)
     validate_membership(reference)
-    
-    data = pd.concat({"prediction":prediction, "reference":reference}, axis=1, join="inner", copy=False)
+
+    data = pd.concat({"prediction": prediction, "reference": reference}, axis=1, join="inner", copy=False)
     TP_cluster_sizes = data.groupby(["prediction", "reference"]).size().values
 
     return np.sum(comb(TP_cluster_sizes, 2))

### 2022-06-03 pv_evaluation/metrics/utils.py

@@ -1,5 +1,6 @@
 import pandas as pd
 
+
 def validate_membership(membership_vect):
     """Validate membership vector
     
@@ -8,4 +9,6 @@ def validate_membership(membership_vect):
     assert isinstance(membership_vect, pd.Series), "Membership vector should be a pandas Series."
     assert membership_vect.hasnans == False, "Membership vector should not contain NA values."
     assert membership_vect.index.hasnans == False, "Membership vetor index should not contain NA values."
-    assert membership_vect.index.has_duplicates == False, "Membership vector index (mention ids) should not contain duplicate values."
+    assert (
+        membership_vect.index.has_duplicates == False
+    ), "Membership vector index (mention ids) should not contain duplicate values."

### 2022-06-03 tests/benchmark/test_data.py

@@ -1,5 +1,6 @@
 from testbook import testbook
 
-@testbook('tests/notebooks/benchmark/benchmark-datasets.ipynb', execute=True)
+
+@testbook("tests/notebooks/benchmark/benchmark-datasets.ipynb", execute=True)
 def test_executable_notebook(tb):
     pass

### 2022-06-03 pv_evaluation/estimators.py
Estimators (#11)
* Add precision estimators

* update

* update

* run black

* update

* Add first example notebook and figure

* tweak figures

* Fix bug

* update

Co-authored-by: Ubuntu <ubuntu@ip-172-31-17-126.ec2.internal>

@@ -1,0 +1,66 @@
+import numpy as np
+import pandas as pd
+from scipy.special import comb
+
+from .metrics.utils import validate_membership
+
+
+def ratio_estimator(B, A):
+    """Ratio estimator for mean(B)/mean(A)
+    """
+    assert len(A) == len(B)
+
+    A_mean = np.mean(A)
+    B_mean = np.mean(B)
+    n = len(A)
+
+    adj = 1 + ((n-1)*A_mean)**(-1) * np.mean(A*(B/B_mean - A/A_mean))
+
+    return adj * B_mean / A_mean
+
+def pairwise_precision_estimator(
+    prediction, reference, sampling_type=["record", "cluster", "single_block"], weights=["uniform", "cluster_size"]
+):
+    """Pairwise precision estimates for small non-replacement samples.
+    
+    Args:
+        prediction (Series):  membership vector for predicted clusters, i.e. a pandas Series indexed by mention ids and with values representing predicted cluster assignment. 
+        reference (Series):  membership vector for sampled reference clusters, i.e. a pandas Series indexed by mention ids and with values representing reference cluster assignment. 
+        sampling_type (list, optional): Sampling mechanism used to obtain reference clusters. Should be one of "record", "cluster", or "single_block". 
+            Note that, for "record" sampling, it is assumed that no two different sampled records had the same associated cluster. 
+        weights (list, optional): Sampling probability weights. Should be one of "uniform" or "cluster_size".
+        
+    Returns:
+        float: pairwise precision estimate.
+    """
+    validate_membership(prediction)
+    validate_membership(reference)
+
+    inner = pd.concat({"prediction": prediction, "reference": reference}, axis=1, join="inner", copy=False)
+    vals = inner.groupby(["prediction", "reference"]).size()
+    f_sum = vals.to_frame().assign(cmb=comb(vals.values, 2)).groupby("reference").sum().cmb.sort_index().values
+    cluster_sizes = inner.reference.value_counts(sort=False).sort_index().values
+    P = np.sum(comb(prediction.value_counts(sort=False).values, 2))
+
+    if sampling_type == "record":
+        if weights == "uniform":
+            return len(prediction) * np.mean(f_sum / cluster_sizes) / P
+        elif weights == "cluster_size":
+            raise Exception("'cluster_size' weights are not used with 'record' sampling type.")
+        else:
[…]

### 2022-06-03 pv_evaluation/metrics/cluster.py

@@ -17,7 +17,7 @@ def clusters_count(membership_vect):
         int: number of clusters
     """
     validate_membership(membership_vect)
-    
+
     return membership_vect.nunique()
 
 
@@ -38,7 +38,7 @@ def cluster_precision(prediction, reference):
     validate_membership(prediction)
     validate_membership(reference)
 
-    data = pd.concat({"prediction":prediction, "reference":reference}, axis=1, join="inner", copy=False)
+    data = pd.concat({"prediction": prediction, "reference": reference}, axis=1, join="inner", copy=False)
     n_correct_clusters = np.sum(data.groupby(["prediction"]).nunique()["reference"].values == 1)
 
     return n_correct_clusters / clusters_count(prediction)
@@ -58,10 +58,12 @@ def cluster_recall(prediction, reference):
     """
     return cluster_precision(reference, prediction)
 
+
 def cluster_precision_recall(prediction, reference):
     """TODO
     """
     return (cluster_precision(prediction, reference), cluster_recall(prediction, reference))
+
 
 def cluster_fscore(prediction, reference, beta=1.0):
     """F-score between cluster precision and cluster recall.
@@ -79,7 +81,7 @@ def cluster_fscore(prediction, reference, beta=1.0):
     Returns:
         float: f-score
     """
-    
+
     P = cluster_precision(prediction, reference)
     R = cluster_recall(prediction, reference)
 
@@ -110,17 +112,19 @@ def wrap_sklearn_metric(sklearn_metric):
     Args:
         sklearn_metric (function): cluster metric to wrap.
     """
+
     def func(prediction, reference, **kw):
         validate_membership(prediction)
         validate_membership(reference)
 
-        data = pd.concat({"prediction":prediction, "reference":reference}, axis=1, join="inner", copy=False)
+        data = pd.concat({"prediction": prediction, "reference": reference}, axis=1, join="inner", copy=False)
         prediction_codes = pd.Categorical(data.prediction).codes.astype(np.int64)
         reference_codes = pd.Categorical(data.reference).codes.astype(np.int64)
 
         return sklearn_metric(reference_codes, prediction_codes, **kw)
 
     return func
+
 
 def cluster_homogeneity(prediction, reference):
     """Cluster homogeneity score (based on conditional entropy).
@@ -136,6 +140,7 @@ def cluster_homogeneity(prediction, reference):
     """
[…]

### 2022-06-03 scripts/israeli-inventors-benchmark.py

@@ -4,7 +4,9 @@ except:
     raise Exception("Unable to import pandas. Please install required dependencies.")
 
 data = pd.read_csv("data-raw/israeli-dataset/uniq_pat.csv")
-data["mention-id"] = 'US' + data.patent.astype(str).map(lambda x:x.lstrip('0')) + '-' + (data.invseq - 1).astype(str)
+data["mention-id"] = "US" + data.patent.astype(str).map(lambda x: x.lstrip("0")) + "-" + (data.invseq - 1).astype(str)
 data["unique-id"] = data.id
 
-data[["mention-id", "unique-id", "lastnam", "firstnam", "country"]].to_csv("pv_evaluation/data/inventor/israeli-inventors-benchmark.csv", index=False)
+data[["mention-id", "unique-id", "lastnam", "firstnam", "country"]].to_csv(
+    "pv_evaluation/data/inventor/israeli-inventors-benchmark.csv", index=False
+)

### 2022-06-03 tests/resources/make.py

@@ -14,7 +14,7 @@ except:
 # Download rawinventor.tsv if not already done.
 if not os.path.isfile("rawinventor.tsv"):
     wget.download("https://s3.amazonaws.com/data.patentsview.org/download/rawinventor.tsv.zip")
-    with zipfile.ZipFile("rawinventor.tsv.zip", 'r') as zip_ref:
+    with zipfile.ZipFile("rawinventor.tsv.zip", "r") as zip_ref:
         zip_ref.extractall(".")
     os.remove("rawinventor.tsv.zip")
 

### 2022-06-10 pv_evaluation/estimators.py
Finish simulation

@@ -64,7 +64,17 @@ def pairwise_precision_estimator(prediction, reference, sampling_type, weights):
         return TP_block / (P_block + 0.5 * P_block_minus)
     elif sampling_type == "cluster_block":
         if weights == "uniform":
-            raise NotImplementedError()
+            N = f_sum
+            K = prediction.isin(inner.prediction)
+            def lambd(x):
+                I = inner.prediction.index.isin(x.index)
+                J = prediction[K].isin(inner.prediction[I])
+                A = inner.prediction[I].value_counts(sort=False).sort_index().values
+                B = prediction[K][J].value_counts(sort=False).sort_index().values
+                return np.sum(A*(B-A))
+            P_minus = inner.groupby("reference").apply(lambd)
+            D = (f_sum + 0.5 * P_minus)
+            return ratio_estimator(N, D)
         elif weights == "cluster_size":
             N = f_sum / cluster_sizes
             K = prediction.isin(inner.prediction)
@@ -119,5 +129,67 @@ def pairwise_recall_estimator(prediction, reference, sampling_type, weights):
         TP_block = np.sum(comb(vals.values, 2))
         T_block = np.sum(comb(inner.reference.value_counts(sort=False).values, 2))
         return TP_block / (T_block)
+    elif sampling_type == "cluster_block":
+        if weights == "uniform":
+            N = f_sum
+            D = comb(cluster_sizes, 2)
+            return ratio_estimator(N, D)
+        elif weights == "cluster_size":
+            N = f_sum / cluster_sizes
+            D = comb(cluster_sizes, 2) / cluster_sizes
+            return ratio_estimator(N, D)
+    else:
+        raise Exception("Unrecognized 'sampling_type' option. Should be one of 'record', 'cluster', or 'single_block'")
+
+def std_dev(B, A):
+    assert len(A) == len(B)
+
+    A_mean = np.mean(A)
+    B_mean = np.mean(B)
+    n = len(A)
+
+    return (B_mean/A_mean) * np.sqrt(np.sum((A/A_mean)**2 + (B/B_mean)**2 - 2*(A*B)/(A_mean*B_mean))/(n*(n-1)))
+
+def pairwise_precision_std(prediction, reference, sampling_type, weights):
+    validate_membership(prediction)
+    validate_membership(reference)
+
+    inner = pd.concat({"prediction": prediction, "reference": reference}, axis=1, join="inner", copy=False)
+    vals = inner.groupby(["prediction", "reference"]).size()
[…]

### 2022-06-10 analyses/2-simulation/src/3-make-sim-records-precision.py
Simulation (#14)
* Begin work on simulations

* add table

* Finish simulation

* Add hand-disambiguation sample data

@@ -1,0 +1,40 @@
+#! /usr/bin/env python3
+
+sample_size = [100, 200, 400]
+
+import numpy as np 
+import pandas as pd
+import os
+from parse import findall
+from pv_evaluation.utils import expand_grid
+from pv_evaluation.metrics import pairwise_precision, pairwise_recall
+from pv_evaluation.estimators import pairwise_precision_estimator
+
+rates = [x.named["rate"] for x in findall("prediction_rate_{rate}.tsv", "".join(os.listdir("output/")))]
+predictions = {rate: pd.read_csv(f"output/prediction_rate_{rate}.tsv", sep="\t").set_index("mention-id")["inventor_id"] for rate in rates}
+
+reference = pd.read_csv("output/disambiguation.tsv", sep="\t").set_index("mention-id")["inventor_id"]
+
+estimators = {
+    "P_naive": lambda ref, benchmark: pairwise_precision(ref, benchmark),
+    "P_single_block": lambda ref, benchmark: pairwise_precision_estimator(ref, benchmark, sampling_type="single_block", weights="uniform"),
+    "P_record": lambda ref, benchmark: pairwise_precision_estimator(ref, benchmark, sampling_type="record", weights="uniform"),
+    "P_cluster_block": lambda ref, benchmark: pairwise_precision_estimator(ref, benchmark, sampling_type="cluster_block", weights="cluster_size")
+}
+
+def sample_clusters(reference, sample_size):
+    clusters = np.random.choice(reference.values, size=sample_size, replace=True)
+    return reference[reference.isin(clusters)]
+
+def simulation(estimator, sample_size, rate, repetitions=1):
+    estimates = np.zeros(repetitions)
+    for i in range(repetitions):
+        np.random.seed(i)
+        benchmark = sample_clusters(reference, sample_size)
+        estimates[i] = estimator(predictions[rate], benchmark)
+    return estimates
+
+data = expand_grid(sample_size=sample_size, rate=rates, estimator=estimators.keys())
+data["estimates"] = data.apply(lambda row: simulation(estimators[row.estimator], row.sample_size, row.rate, repetitions=100), axis=1, result_type="reduce")
+
+data.to_pickle("output/estimates_sim_records_precision.pickle")

### 2022-06-23 pv_evaluation/benchmark/__init__.py
update

@@ -1,7 +1,11 @@
 """Evaluation datasets and standardized benchmarks
 """
 
-from pv_evaluation.data import load_israeli_inventors_benchmark, load_patentsview_inventors_benchmark, load_lai_2011_inventors_benchmark
+from pv_evaluation.benchmark.data import (
+    load_israeli_inventors_benchmark,
+    load_patentsview_inventors_benchmark,
+    load_lai_2011_inventors_benchmark,
+)
 
 from pv_evaluation.benchmark.report import (
     inventor_benchmark_table,

### 2022-06-23 pv_evaluation/benchmark/report.py

@@ -21,11 +21,11 @@ DEFAULT_BENCHMARKS = {
 DEFAULT_METRICS = {
     "pairwise precision": pairwise_precision,
     "pairwise recall": pairwise_recall,
-    #"pairwise f1": pairwise_fscore,
+    # "pairwise f1": pairwise_fscore,
     "cluster precision": cluster_precision,
     "cluster recall": cluster_recall,
-    #"cluster f1": cluster_fscore
-    #"rand index": rand_score,
+    # "cluster f1": cluster_fscore
+    # "rand index": rand_score,
 }
 
 
@@ -36,7 +36,7 @@ def inventor_benchmark_table(disambiguations, metrics=None, benchmarks=None):
         disambiguations (dict): dictionary of disambiguation results (disambiguation results are pandas Series with "mention-id" index and cluster assignment values).
         metrics (dict, optional): dictionary of metrics (from the metrics submodule) to compute. Defaults to `DEFAULT_METRICS`.
         benchmarks (dict, optional): benchmark datasets loading functions to use from the benchmark submodule. Defaults to `DEFAULT_BENCHMARK`.
-    
+
     Returns:
         DataFrame of computed metrics for every disambiguations and every benchmark dataset.
     """
@@ -88,7 +88,6 @@ def inventor_benchmark_plot(disambiguations, metrics=None, benchmarks=None, **kw
     if benchmarks is None:
         benchmarks = DEFAULT_BENCHMARKS
 
-    
     computed_metrics = inventor_benchmark_table(disambiguations, metrics=metrics, benchmarks=benchmarks)
     return px.bar(computed_metrics, y="value", x="metric", color="algorithm", facet_col="benchmark", barmode="group", **kwargs)
 

### 2022-06-23 pv_evaluation/estimators/__init__.py

@@ -3,9 +3,4 @@
 from pv_evaluation.estimators.pairwise_precision import pairwise_precision_estimator, pairwise_precision_std
 from pv_evaluation.estimators.pairwise_recall import pairwise_recall_estimator, pairwise_recall_std
 
-__all__ = [
-    "pairwise_precision_estimator",
-    "pairwise_precision_std",
-    "pairwise_recall_estimator",
-    "pairwise_recall_std"
-]
+__all__ = ["pairwise_precision_estimator", "pairwise_precision_std", "pairwise_recall_estimator", "pairwise_recall_std"]

### 2022-06-23 pv_evaluation/estimators/pairwise_precision.py

@@ -5,6 +5,7 @@ import scipy.special as sp
 from pv_evaluation.metrics.utils import validate_membership
 from pv_evaluation.estimators.ratio_estimators import ratio_estimator, std_dev
 
+
 def pairwise_precision_arrays(prediction, reference, sampling_type, weights):
     """Raw data for use with ratio estimator and standard deviation estimators."""
     validate_membership(prediction)
@@ -27,7 +28,7 @@ def pairwise_precision_arrays(prediction, reference, sampling_type, weights):
         if weights == "uniform":
             return (len(prediction) * f_sum / P, cluster_sizes)
         elif weights == "cluster_size":
-            return (len(prediction) * np.mean(f_sum / cluster_sizes) / P, 1)
+            return (len(prediction) * np.mean(f_sum / cluster_sizes) / P, np.ones(len(f_sum)))
         else:
             raise Exception("Unrecognized 'weight' option. Should be one of 'uniform' or 'cluster_size'.")
     elif sampling_type == "single_block":
@@ -37,7 +38,7 @@ def pairwise_precision_arrays(prediction, reference, sampling_type, weights):
         A = inner.prediction.value_counts(sort=False).sort_index().values
         B = prediction[I].value_counts(sort=False).sort_index().values
         P_block_minus = np.sum(A * (B - A))
-        return (TP_block / (P_block + 0.5 * P_block_minus), 1)
+        return (np.array([TP_block / (P_block + 0.5 * P_block_minus)]), np.array([1]))
     elif sampling_type == "cluster_block":
         if weights == "uniform":
             N = f_sum
@@ -103,6 +104,7 @@ def pairwise_precision_estimator(prediction, reference, sampling_type, weights):
     """
     N, D = pairwise_precision_arrays(prediction, reference, sampling_type, weights)
     return ratio_estimator(N, D)
+
 
 def pairwise_precision_std(prediction, reference, sampling_type, weights):
     """Standard deviation estimates for the pairwise precision estimator."""

### 2022-06-23 pv_evaluation/estimators/pairwise_recall.py

@@ -18,7 +18,7 @@ def pairwise_recall_arrays(prediction, reference, sampling_type, weights):
 
     if sampling_type == "record":
         if weights == "uniform":
-            return (2 *f_sum / cluster_sizes, cluster_sizes - 1)
+            return (2 * f_sum / cluster_sizes, cluster_sizes - 1)
         elif weights == "cluster_size":
             raise Exception("'cluster_size' weights are not used with 'record' sampling type.")
         else:
@@ -33,7 +33,7 @@ def pairwise_recall_arrays(prediction, reference, sampling_type, weights):
     elif sampling_type == "single_block":
         TP_block = np.sum(sp.comb(vals.values, 2))
         T_block = np.sum(sp.comb(inner.reference.value_counts(sort=False).values, 2))
-        return TP_block / (T_block)
+        return (np.array([TP_block / (T_block)]), np.array([1]))
     elif sampling_type == "cluster_block":
         if weights == "uniform":
             N = f_sum
@@ -45,7 +45,6 @@ def pairwise_recall_arrays(prediction, reference, sampling_type, weights):
             return (N, D)
     else:
         raise Exception("Unrecognized 'sampling_type' option. Should be one of 'record', 'cluster', or 'single_block'")
-
 
 
 def pairwise_recall_estimator(prediction, reference, sampling_type, weights):
@@ -86,5 +85,3 @@ def pairwise_recall_std(prediction, reference, sampling_type, weights):
     """Standard deviation estimates for the pairwise recall estimator."""
     N, D = pairwise_recall_arrays(prediction, reference, sampling_type, weights)
     return std_dev(N, D)
-
-

### 2022-06-23 pv_evaluation/estimators/ratio_estimators.py

@@ -1,5 +1,6 @@
 import numpy as np
 
+
 def ratio_estimator(B, A):
     """Ratio estimator for mean(B)/mean(A) with bias adjustment."""
     assert len(A) == len(B)
@@ -8,9 +9,13 @@ def ratio_estimator(B, A):
     B_mean = np.mean(B)
     n = len(A)
 
-    adj = 1 + ((n - 1) * A_mean) ** (-1) * np.mean(A * (B / B_mean - A / A_mean))
+    if len(A) == 1:
+        adj = 1
+    else:
+        adj = 1 + ((n - 1) * A_mean) ** (-1) * np.mean(A * (B / B_mean - A / A_mean))
 
     return adj * B_mean / A_mean
+
 
 def std_dev(B, A):
     """Standard deviation estimator for ratio estimator."""

### 2022-06-23 pv_evaluation/metrics/cluster.py

@@ -5,7 +5,7 @@ import pandas as pd
 import sklearn.metrics as sm
 from functools import wraps
 
-from pv_evaluation.utils import validate_membership
+from pv_evaluation.metrics.utils import validate_membership
 
 
 def clusters_count(membership_vect):
@@ -137,6 +137,7 @@ def wrap_sklearn_metric(sklearn_metric):
     Args:
         sklearn_metric (function): cluster metric to wrap.
     """
+
     @wraps(sklearn_metric)
     def func(prediction, reference, **kw):
         validate_membership(prediction)

### 2022-06-23 pv_evaluation/metrics/pairwise.py

@@ -4,7 +4,7 @@
 import numpy as np
 from scipy.special import comb
 import pandas as pd
-from pv_evaluation.utils import validate_membership
+from pv_evaluation.metrics.utils import validate_membership
 
 
 def cluster_sizes(membership_vect):

### 2022-06-23 pv_evaluation/summary/inventor_disambiguation_summary.py

@@ -111,7 +111,7 @@ class InventorDisambiguationSummary:
     def entropy_curve(self, q_range=None):
         if q_range is None:
             q_range = np.linspace(0, 2)
-        
+
         data = self.get_cluster_size_distribution()
         data["Number of inventors"] = data["Number of inventors"] / sum(data["Number of inventors"])
 
@@ -129,7 +129,7 @@ class InventorDisambiguationSummary:
     def plot_entropy_curve(self, q_range=None):
         if q_range is None:
             q_range = np.linspace(0, 2)
-        
+
         ent, q = self.entropy_curve(q_range)
         fig = px.line(x=q, y=ent, title="Hill Numbers entropy curve", labels={"x": "q", "y": "Entropy"})
         fig.update_traces(name=self.name)

### 2022-06-23 pv_evaluation/templates/render.py

@@ -10,10 +10,10 @@ def render_inventor_disambiguation_report(outdir, summary_table_files, cache=Tru
 
     Args:
         outdir (str): directory where to output html files.
-        summary_table_files (list): list of paths to disambiguation table files (tables with the five columns "mention-id", "inventor_id", "patent_id", "name_first", and "name_last"). 
+        summary_table_files (list): list of paths to disambiguation table files (tables with the five columns "mention-id", "inventor_id", "patent_id", "name_first", and "name_last").
             File format can be one of tsv, csv, or parquet.
         cache (bool, optional): whether or not to cache jupyter chunk execution between runs. Defaults to True.
-    
+
     Notes:
         * Summary table filenames are used for figure legends. Keep them short.
     """

### 2022-06-23 pv_evaluation/utils.py

@@ -20,6 +20,5 @@ def compare_plots(*figs):
 
 
 def expand_grid(**kwargs):
-    """Get all value combinations.
-    """
+    """Get all value combinations."""
     return pd.DataFrame.from_records(itertools.product(*kwargs.values()), columns=kwargs.keys())

### 2022-06-23 pv_evaluation/benchmark/data.py
update

@@ -26,15 +26,15 @@ def load_lai_2011_inventors_benchmark():
 
     This is adapted from the benchmark dataset reported in Li et al. (2014) to evaluate their disambiguation of the  U.S. Patent Inventor Database (1975-2010).
 
-    Notes:
-        * A number of patent IDs which could not be found were removed from Lai's original dataset.
-        * Inventor sequence numbers were assigned through automatic matching and manual review. There could be some errors.
-
     See:
         Li, G. C., Lai, R., D'Amour, A., Doolin, D. M., Sun, Y., Torvik, V. I., ... & Fleming, L. (2014). Disambiguation and co-authorship networks of the US patent inventor database (1975-2010). Research Policy, 43(6), 941-955.
 
     Returns:
         Series: pandas Series indexed by mention ID and with values corresponding to cluster assignment.
+
+    Notes:
+        * A number of patent IDs which could not be found were removed from Lai's original dataset.
+        * Inventor sequence numbers were assigned through automatic matching and manual review. There could be some errors.
     """
     return load_unique_id_series(INVENTOR_DATA_MODULE, "lai-2011-benchmark.csv")
 

### 2022-06-23 pv_evaluation/estimators/pairwise_precision.py

@@ -87,11 +87,6 @@ def pairwise_precision_estimator(prediction, reference, sampling_type, weights):
         * **uniform**: uniform probability weights.
         * **cluster_size**: probability weights proportional to cluster size.
 
-    Notes:
-        * We recommend using the **cluster_block** estimator when possible since it is the most efficient.
-        * This is meant for use with relatively small non-replacement samples.
-        * For unknown sampling processes, the **single_block** estimator can be used.
-
     Args:
         prediction (Series):  membership vector for predicted clusters, i.e. a pandas Series indexed by mention ids and with values representing predicted cluster assignment.
         reference (Series):  membership vector for sampled reference clusters, i.e. a pandas Series indexed by mention ids and with values representing reference cluster assignment.
@@ -101,6 +96,11 @@ def pairwise_precision_estimator(prediction, reference, sampling_type, weights):
 
     Returns:
         float: pairwise precision estimate.
+
+    Notes:
+        * We recommend using the **cluster_block** estimator when possible since it is the most efficient.
+        * This is meant for use with relatively small non-replacement samples.
+        * For unknown sampling processes, the **single_block** estimator can be used.
     """
     N, D = pairwise_precision_arrays(prediction, reference, sampling_type, weights)
     return ratio_estimator(N, D)

### 2022-06-23 pv_evaluation/estimators/pairwise_recall.py

@@ -62,11 +62,6 @@ def pairwise_recall_estimator(prediction, reference, sampling_type, weights):
         * **uniform**: uniform probability weights.
         * **cluster_size**: probability weights proportional to cluster size.
 
-    Notes:
-        * We recommend using the **cluster_block** estimator when possible since it is the most efficient.
-        * This is meant for use with relatively small non-replacement samples.
-        * For unknown sampling processes, the **single_block** estimator can be used.
-
     Args:
         prediction (Series):  membership vector for predicted clusters, i.e. a pandas Series indexed by mention ids and with values representing predicted cluster assignment.
         reference (Series):  membership vector for sampled reference clusters, i.e. a pandas Series indexed by mention ids and with values representing reference cluster assignment.
@@ -76,6 +71,11 @@ def pairwise_recall_estimator(prediction, reference, sampling_type, weights):
 
     Returns:
         float: pairwise recall estimate.
+
+    Notes:
+        * We recommend using the **cluster_block** estimator when possible since it is the most efficient.
+        * This is meant for use with relatively small non-replacement samples.
+        * For unknown sampling processes, the **single_block** estimator can be used.
     """
     N, D = pairwise_recall_arrays(prediction, reference, sampling_type, weights)
     return ratio_estimator(N, D)

### 2022-06-23 pv_evaluation/metrics/cluster.py

@@ -29,15 +29,15 @@ def cluster_precision(prediction, reference):
 
     A perfect cluster precision means that all predicted links are correct.
 
-    Notes:
-        * The prediction and reference membership vectors are inner joined before cluster precision is computed.
-
     Args:
         prediction (Series):  membership vector for predicted clusters, i.e. a pandas Series indexed by mention ids and with values representing predicted cluster assignment.
         reference (Series):  membership vector for reference clusters, i.e. a pandas Series indexed by mention ids and with values representing reference cluster assignment.
 
     Returns:
         float: cluster precision
+
+    Notes:
+        * The prediction and reference membership vectors are inner joined before cluster precision is computed.
     """
     validate_membership(prediction)
     validate_membership(reference)
@@ -53,16 +53,16 @@ def cluster_recall(prediction, reference):
 
     A perfect cluster recall means that all reference links are correctly predicted.
 
-    Notes:
-        * The prediction and reference membership vectors are inner joined before cluster recall is computed.
-        * This is the same as `cluster_precision(reference, prediction)`_.
-
     Args:
         prediction (Series):  membership vector for predicted clusters, i.e. a pandas Series indexed by mention ids and with values representing predicted cluster assignment.
         reference (Series):  membership vector for reference clusters, i.e. a pandas Series indexed by mention ids and with values representing reference cluster assignment.
 
     Returns:
         float: cluster recall
+
+    Notes:
+        * The prediction and reference membership vectors are inner joined before cluster recall is computed.
+        * This is the same as `cluster_precision(reference, prediction)`_.
     """
     return cluster_precision(reference, prediction)
 
@@ -70,15 +70,15 @@ def cluster_recall(prediction, reference):
 def cluster_precision_recall(prediction, reference):
     """Cluster precision and cluster recall tuple.
 
-    Notes:
-        * The prediction and reference membership vectors are inner joined before metrics are computed.
-
     Args:
         prediction (Series):  membership vector for predicted clusters, i.e. a pandas Series indexed by mention ids and with values representing predicted cluster assignment.
         reference (Series):  membership vector for reference clusters, i.e. a pandas Series indexed by mention ids and with values representing reference cluster assignment.
 
     Returns:
         tuple: (cluster precision, cluster recall)
+
+    Notes:
[…]

### 2022-06-23 pv_evaluation/metrics/pairwise.py

@@ -72,15 +72,15 @@ def false_positives_count(prediction, reference):
 def pairwise_precision(prediction, reference):
     """Pairwise precision: number of correct links divided by the number of predicted links.
 
-    Note:
-        The prediction and reference membership vectors are inner joined before precision is computed.
-
     Args:
         prediction (Series):  membership vector for predicted clusters, i.e. a pandas Series indexed by mention ids and with values representing predicted cluster assignment.
         reference (Series):  membership vector for reference clusters, i.e. a pandas Series indexed by mention ids and with values representing reference cluster assignment.
 
     Returns:
         float: pairwise precision
+
+    Note:
+        The prediction and reference membership vectors are inner joined before precision is computed.
     """
 
     inner = pd.concat({"prediction": prediction, "reference": reference}, axis=1, join="inner", copy=False)
@@ -95,16 +95,16 @@ def pairwise_precision(prediction, reference):
 def pairwise_recall(prediction, reference):
     """Pairwise recall: number of correct links divided by the number of reference links.
 
-    Notes:
-        * The prediction and reference membership vectors are inner joined before recall is computed.
-        * This is the same as `pairwise_precision(reference, prediction)`_.
-
     Args:
         prediction (Series):  membership vector for predicted clusters, i.e. a pandas Series indexed by mention ids and with values representing predicted cluster assignment.
         reference (Series):  membership vector for reference clusters, i.e. a pandas Series indexed by mention ids and with values representing reference cluster assignment.
 
     Returns:
         float: pairwise recall
+
+    Notes:
+        * The prediction and reference membership vectors are inner joined before recall is computed.
+        * This is the same as `pairwise_precision(reference, prediction)`_.
     """
 
     return pairwise_precision(reference, prediction)
@@ -113,15 +113,15 @@ def pairwise_recall(prediction, reference):
 def pairwise_precision_recall(prediction, reference):
     """Pairwise precision and recall
 
-    Notes:
-        * The prediction and reference membership vectors are inner joined before precision and recall are computed.
-
     Args:
         prediction (Series):  membership vector for predicted clusters, i.e. a pandas Series indexed by mention ids and with values representing predicted cluster assignment.
         reference (Series):  membership vector for reference clusters, i.e. a pandas Series indexed by mention ids and with values representing reference cluster assignment.
 
     Returns:
         tuple: tuple (precision, recall).
+
+    Notes:
[…]

### 2022-06-23 pv_evaluation/templates/inventor/2-summary.qmd
Refactor (#10)
* update

* add sphinx doc

* update

* add html docs

* add module docs

* update

* update; not enough memory

* add callout tips
Tweaks (#22)
* update record sampling analysis

* update docs; fix bug with cluster_precision_recall

* update

* refactor estimators

* refactor estimators

* refactor estimators

* update

* update

* update

@@
 ```{python}
-summarizers = {filename: InventorDisambiguationSummary(filename, processed_data_dir=".") for filename in {{ summary_table_files }} }
+summarizers = {filename: InventorDisambiguationSummary(filename) for filename in {{ summary_table_files }} }
 ```
@@
 
+:::{.column-body-outset}
 ```{python}
-compare_plots(*[s.plot_cluster_size_distribution() for s in summarizers.values()])
+fig = compare_plots(*[s.plot_cluster_size_distribution() for s in summarizers.values()])
+fig.update_layout(autosize=False, width=800)
+fig.show()
 ```
+:::
 
@@
 
+:::{.column-body-outset}
 ```{python}
-compare_plots(*[s.plot_entropy_curve() for s in summarizers.values()])
+fig = compare_plots(*[s.plot_entropy_curve() for s in summarizers.values()])
+fig.update_layout(autosize=False, width=800)
+fig.show()
 ```
+:::
 
@@
 
+:::{.column-body-outset}
 ```{python}
-compare_plots(*[s.plot_cluster_unique_name_distribution() for s in summarizers.values()])
+fig = compare_plots(*[s.plot_cluster_unique_name_distribution() for s in summarizers.values()])
+fig.update_layout(autosize=False, width=800)
+fig.show()
 ```
+:::
 
@@
 
+:::{.column-body-outset}
 ```{python}
-compare_plots(*[s.plot_homonymy_rate_distribution() for s in summarizers.values()])
+fig = compare_plots(*[s.plot_homonymy_rate_distribution() for s in summarizers.values()])
+fig.update_layout(autosize=False, width=800)
+fig.show()
 ```
+:::
 

### 2022-06-23 pv_evaluation/benchmark/__init__.py

@@ -1,9 +1,13 @@
 """Evaluation datasets and standardized benchmarks
 """
 
-from .data import load_israeli_inventors_benchmark, load_patentsview_inventors_benchmark, load_lai_2011_inventors_benchmark
+from pv_evaluation.benchmark.data import (
+    load_israeli_inventors_benchmark,
+    load_patentsview_inventors_benchmark,
+    load_lai_2011_inventors_benchmark,
+)
 
-from .report import (
+from pv_evaluation.benchmark.report import (
     inventor_benchmark_table,
     inventor_benchmark_plot,
     inspect_clusters_to_split,

### 2022-06-23 pv_evaluation/benchmark/data.py

@@ -22,25 +22,25 @@ def load_unique_id_series(module, filename):
 
 
 def load_lai_2011_inventors_benchmark():
-    """Lai's 2011 inventors benchmark dataset
+    """Lai's 2011 inventors benchmark dataset (also referred to as as Lai's 2014 inventors benchmark).
 
-    This is adapted from the benchmark dataset reported in Lai et al. (2011) to evaluate their disambiguation of the  U.S. Patent Inventor Database (1975-2010).
-
-    Notes:
-        A number of patent IDs which could not be found were removed from Lai's original dataset.
-        Inventor sequence numbers were assigned through automatic matching and manual review. There could be some errors.
+    This is adapted from the benchmark dataset reported in Li et al. (2014) to evaluate their disambiguation of the  U.S. Patent Inventor Database (1975-2010).
 
     See:
         Li, G. C., Lai, R., D'Amour, A., Doolin, D. M., Sun, Y., Torvik, V. I., ... & Fleming, L. (2014). Disambiguation and co-authorship networks of the US patent inventor database (1975-2010). Research Policy, 43(6), 941-955.
 
     Returns:
         Series: pandas Series indexed by mention ID and with values corresponding to cluster assignment.
+
+    Notes:
+        * A number of patent IDs which could not be found were removed from Lai's original dataset.
+        * Inventor sequence numbers were assigned through automatic matching and manual review. There could be some errors.
     """
     return load_unique_id_series(INVENTOR_DATA_MODULE, "lai-2011-benchmark.csv")
 
 
 def load_israeli_inventors_benchmark():
-    """Israeli inventors benchmark dataset
+    """Israeli inventors benchmark dataset.
 
     This is adapted from Trajenberg and Shiff (2008). The data covers U.S. patents granted between 1963 and 1999 for Israeli inventors.
 
@@ -54,7 +54,7 @@ def load_israeli_inventors_benchmark():
 
 
 def load_patentsview_inventors_benchmark():
-    """PatentsView hand-disambiguated inventors benchmark
+    """PatentsView hand-disambiguated inventors benchmark.
 
     This is the hand-disambiguation of a set of particularly ambiguous inventor names.
 

### 2022-06-23 pv_evaluation/estimators/pairwise_precision.py

@@ -1,0 +1,112 @@
+import numpy as np
+import pandas as pd
+import scipy.special as sp
+
+from pv_evaluation.metrics.utils import validate_membership
+from pv_evaluation.estimators.ratio_estimators import ratio_estimator, std_dev
+
+
+def pairwise_precision_arrays(prediction, reference, sampling_type, weights):
+    """Raw data for use with ratio estimator and standard deviation estimators."""
+    validate_membership(prediction)
+    validate_membership(reference)
+
+    inner = pd.concat({"prediction": prediction, "reference": reference}, axis=1, join="inner", copy=False)
+    vals = inner.groupby(["prediction", "reference"]).size()
+    f_sum = vals.to_frame().assign(cmb=sp.comb(vals.values, 2)).groupby("reference").sum().cmb.sort_index().values
+    cluster_sizes = inner.reference.value_counts(sort=False).sort_index().values
+    P = np.sum(sp.comb(prediction.value_counts(sort=False).values, 2))
+
+    if sampling_type == "record":
+        if weights == "uniform":
+            return len(prediction) * np.mean(f_sum / cluster_sizes) / P
+        elif weights == "cluster_size":
+            raise Exception("'cluster_size' weights are not used with 'record' sampling type.")
+        else:
+            raise Exception("Unrecognized 'weight' option. Should be one of 'uniform' or 'cluster_size'.")
+    elif sampling_type == "cluster":
+        if weights == "uniform":
+            return (len(prediction) * f_sum / P, cluster_sizes)
+        elif weights == "cluster_size":
+            return (len(prediction) * np.mean(f_sum / cluster_sizes) / P, np.ones(len(f_sum)))
+        else:
+            raise Exception("Unrecognized 'weight' option. Should be one of 'uniform' or 'cluster_size'.")
+    elif sampling_type == "single_block":
+        TP_block = np.sum(sp.comb(vals.values, 2))
+        P_block = np.sum(sp.comb(inner.prediction.value_counts(sort=False).values, 2))
+        I = prediction.isin(inner.prediction)
+        A = inner.prediction.value_counts(sort=False).sort_index().values
+        B = prediction[I].value_counts(sort=False).sort_index().values
+        P_block_minus = np.sum(A * (B - A))
+        return (np.array([TP_block / (P_block + 0.5 * P_block_minus)]), np.array([1]))
+    elif sampling_type == "cluster_block":
+        if weights == "uniform":
+            N = f_sum
[…]

### 2022-06-23 pv_evaluation/estimators/pairwise_recall.py

@@ -1,0 +1,87 @@
+import numpy as np
+import pandas as pd
+import scipy.special as sp
+
+from pv_evaluation.metrics.utils import validate_membership
+from pv_evaluation.estimators.ratio_estimators import ratio_estimator, std_dev
+
+
+def pairwise_recall_arrays(prediction, reference, sampling_type, weights):
+    """Raw data for use with ratio estimator and standard deviation estimators."""
+    validate_membership(prediction)
+    validate_membership(reference)
+
+    inner = pd.concat({"prediction": prediction, "reference": reference}, axis=1, join="inner", copy=False)
+    vals = inner.groupby(["prediction", "reference"]).size()
+    f_sum = vals.to_frame().assign(cmb=sp.comb(vals.values, 2)).groupby("reference").sum().cmb.sort_index().values
+    cluster_sizes = inner.reference.value_counts(sort=False).sort_index().values
+
+    if sampling_type == "record":
+        if weights == "uniform":
+            return (2 * f_sum / cluster_sizes, cluster_sizes - 1)
+        elif weights == "cluster_size":
+            raise Exception("'cluster_size' weights are not used with 'record' sampling type.")
+        else:
+            raise Exception("Unrecognized 'weight' option. Should be one of 'uniform' or 'cluster_size'.")
+    elif sampling_type == "cluster":
+        if weights == "uniform":
+            return (f_sum, sp.comb(cluster_sizes, 2))
+        elif weights == "cluster_size":
+            return (2 * f_sum / cluster_sizes, cluster_sizes - 1)
+        else:
+            raise Exception("Unrecognized 'weight' option. Should be one of 'uniform' or 'cluster_size'.")
+    elif sampling_type == "single_block":
+        TP_block = np.sum(sp.comb(vals.values, 2))
+        T_block = np.sum(sp.comb(inner.reference.value_counts(sort=False).values, 2))
+        return (np.array([TP_block / (T_block)]), np.array([1]))
+    elif sampling_type == "cluster_block":
+        if weights == "uniform":
+            N = f_sum
+            D = sp.comb(cluster_sizes, 2)
+            return (N, D)
+        elif weights == "cluster_size":
+            N = f_sum / cluster_sizes
+            D = sp.comb(cluster_sizes, 2) / cluster_sizes
+            return (N, D)
+    else:
+        raise Exception("Unrecognized 'sampling_type' option. Should be one of 'record', 'cluster', or 'single_block'")
+
+
[…]

### 2022-06-23 pv_evaluation/estimators/ratio_estimators.py

@@ -1,0 +1,30 @@
+import numpy as np
+
+
+def ratio_estimator(B, A):
+    """Ratio estimator for mean(B)/mean(A) with bias adjustment."""
+    assert len(A) == len(B)
+
+    A_mean = np.mean(A)
+    B_mean = np.mean(B)
+    n = len(A)
+
+    if len(A) == 1:
+        adj = 1
+    else:
+        adj = 1 + ((n - 1) * A_mean) ** (-1) * np.mean(A * (B / B_mean - A / A_mean))
+
+    return adj * B_mean / A_mean
+
+
+def std_dev(B, A):
+    """Standard deviation estimator for ratio estimator."""
+    assert len(A) == len(B)
+
+    A_mean = np.mean(A)
+    B_mean = np.mean(B)
+    n = len(A)
+
+    return (B_mean / A_mean) * np.sqrt(
+        np.sum((A / A_mean) ** 2 + (B / B_mean) ** 2 - 2 * (A * B) / (A_mean * B_mean)) / (n * (n - 1))
+    )

### 2022-06-23 pv_evaluation/metrics/pairwise.py

@@ -4,7 +4,7 @@
 import numpy as np
 from scipy.special import comb
 import pandas as pd
-from .utils import validate_membership
+from pv_evaluation.metrics.utils import validate_membership
 
 
 def cluster_sizes(membership_vect):
@@ -78,6 +78,9 @@ def pairwise_precision(prediction, reference):
 
     Returns:
         float: pairwise precision
+
+    Note:
+        The prediction and reference membership vectors are inner joined before precision is computed.
     """
 
     inner = pd.concat({"prediction": prediction, "reference": reference}, axis=1, join="inner", copy=False)
@@ -92,14 +95,16 @@ def pairwise_precision(prediction, reference):
 def pairwise_recall(prediction, reference):
     """Pairwise recall: number of correct links divided by the number of reference links.
 
-    This is the same as `pairwise_precision(reference, prediction)`.
-
     Args:
         prediction (Series):  membership vector for predicted clusters, i.e. a pandas Series indexed by mention ids and with values representing predicted cluster assignment.
         reference (Series):  membership vector for reference clusters, i.e. a pandas Series indexed by mention ids and with values representing reference cluster assignment.
 
     Returns:
         float: pairwise recall
+
+    Notes:
+        * The prediction and reference membership vectors are inner joined before recall is computed.
+        * This is the same as `pairwise_precision(reference, prediction)`_.
     """
 
     return pairwise_precision(reference, prediction)
@@ -114,6 +119,9 @@ def pairwise_precision_recall(prediction, reference):
 
     Returns:
         tuple: tuple (precision, recall).
+
+    Notes:
+        * The prediction and reference membership vectors are inner joined before precision and recall are computed.
     """
     return (pairwise_precision(prediction, reference), pairwise_recall(prediction, reference))
 
@@ -133,6 +141,9 @@ def pairwise_fscore(prediction, reference, beta=1.0):
 
     Returns:
         float: f-score
+
+    Notes:
+        * The prediction and reference membership vectors are inner joined before f-score is computed.
     """
     P = pairwise_precision(prediction, reference)
     R = pairwise_recall(prediction, reference)
@@ -151,6 +162,9 @@ def pairwise_fowlkes_mallows(prediction, reference):
 
     Returns:
         float: Fowlks-Mallows index
+
+    Notes:
+        * The prediction and reference membership vectors are inner joined before the fowlks-mallows score is computed.
     """
     P = pairwise_precision(prediction, reference)
     R = pairwise_recall(prediction, reference)

### 2022-06-23 pv_evaluation/summary/inventor_disambiguation_summary.py

@@ -18,17 +18,23 @@ def read_auto(datapath):
 
 
 class InventorDisambiguationSummary:
-    def __init__(self, datapath, name=None):
-        """Report inventor disambiguation summaries.
+    """Report inventor disambiguation summaries."""
+
+    def __init__(self, data, name=None):
+        """Constructor.
 
         Args:
-            datapath (str): path to the inventor disambiguation data (csv, tsv or parquet format).
+            data (str or DataFrame): pandas DataFrame or string path to the inventor disambiguation data (csv, tsv or parquet format).
                 The data should have four columns: "patent_id", "inventor_id", "name_first", and "name_last".
             name (str): name of the disambiguation algorithm to show in plots. Defaults to the provided datapath.
         """
-        self.name = datapath if name is None else name
-
-        self._data = read_auto(datapath)
+        self.name = name
+        if isinstance(data, str):
+            self._data = read_auto(data)
+            if self.name is None:
+                self.name = data
+        else:
+            self._data = data
         self._validate_data()
 
         # Lazy initialization
@@ -68,7 +74,7 @@ class InventorDisambiguationSummary:
         )
 
     def plot_cluster_size_distribution(self, range=(0, 20)):
-        """Plot the distribution of the number of patents per inventor
+        """Plot the distribution of the number of patents per inventor.
 
         Args:
             range (tuple, optional): x-axis limits (inclusive range for the number of patents by inventor). Defaults to (1, 10).
@@ -92,7 +98,7 @@ class InventorDisambiguationSummary:
         return fig
 
     def get_top_inventors(self, n=10):
-        """Get DataFrame of n most prolific inventors
+        """Get DataFrame of n most prolific inventors.
 
         Args:
             n (int, optional): Number of inventors to return. Defaults to 10.
@@ -105,7 +111,7 @@ class InventorDisambiguationSummary:
     def entropy_curve(self, q_range=None):
         if q_range is None:
             q_range = np.linspace(0, 2)
-        
+
         data = self.get_cluster_size_distribution()
         data["Number of inventors"] = data["Number of inventors"] / sum(data["Number of inventors"])
 
@@ -123,7 +129,7 @@ class InventorDisambiguationSummary:
     def plot_entropy_curve(self, q_range=None):
         if q_range is None:
             q_range = np.linspace(0, 2)
-        
+
         ent, q = self.entropy_curve(q_range)
[…]

### 2022-06-23 docs/source/conf.py
Tweaks (#22)
* update record sampling analysis

* update docs; fix bug with cluster_precision_recall

* update

* refactor estimators

* refactor estimators

* refactor estimators

* update

* update

* update

@@ -12,15 +12,16 @@
 #
 import os
 import sys
-sys.path.insert(0, os.path.abspath('../pv_evaluation'))
-sys.path.insert(0, os.path.abspath('../examples'))
+
+sys.path.insert(0, os.path.abspath("../pv_evaluation"))
+sys.path.insert(0, os.path.abspath("../examples"))
 
 
 # -- Project information -----------------------------------------------------
 
-project = 'PatentsView-Evaluation'
-copyright = '2022, PatentsView.org'
-author = 'Olivier Binette, Sarvo Madhavan'
+project = "PatentsView-Evaluation"
+copyright = "2022, PatentsView.org"
+author = "Olivier Binette, Sarvo Madhavan"
 
 
 # -- General configuration ---------------------------------------------------
@@ -32,16 +33,16 @@ extensions = [
     "sphinx.ext.autodoc",
     "sphinx.ext.napoleon",
     "sphinx.ext.autosummary",
-    'm2r2',
+    "m2r2",
     "sphinx_lesson",
 ]
 
 nb_execution_mode = "off"
 
-source_suffix = ['.rst', '.md', '.ipynb']
+source_suffix = [".rst", ".md", ".ipynb"]
 
 # Add any paths that contain templates here, relative to this directory.
-templates_path = ['_templates']
+templates_path = ["_templates"]
 
 # List of patterns, relative to source directory, that match files and
 # directories to ignore when looking for source files.
@@ -54,10 +55,9 @@ exclude_patterns = []
 # The theme to use for HTML and HTML Help pages.  See the documentation for
 # a list of builtin themes.
 #
-html_theme = 'pydata_sphinx_theme'
+html_theme = "pydata_sphinx_theme"
 
 # Add any paths that contain custom static files (such as style sheets) here,
 # relative to this directory. They are copied after the builtin static files,
 # so a file named "default.css" will overwrite the builtin "default.css".
-html_static_path = ['_static']
-
+html_static_path = ["_static"]

### 2022-06-23 pv_evaluation/benchmark/report.py

@@ -21,11 +21,11 @@ DEFAULT_BENCHMARKS = {
 DEFAULT_METRICS = {
     "pairwise precision": pairwise_precision,
     "pairwise recall": pairwise_recall,
-    #"pairwise f1": pairwise_fscore,
-    #"cluster precision": cluster_precision,
-    #"cluster recall": cluster_recall,
-    #"cluster f1": cluster_fscore
-    #"rand index": rand_score,
+    # "pairwise f1": pairwise_fscore,
+    "cluster precision": cluster_precision,
+    "cluster recall": cluster_recall,
+    # "cluster f1": cluster_fscore
+    # "rand index": rand_score,
 }
 
 
@@ -36,6 +36,9 @@ def inventor_benchmark_table(disambiguations, metrics=None, benchmarks=None):
         disambiguations (dict): dictionary of disambiguation results (disambiguation results are pandas Series with "mention-id" index and cluster assignment values).
         metrics (dict, optional): dictionary of metrics (from the metrics submodule) to compute. Defaults to `DEFAULT_METRICS`.
         benchmarks (dict, optional): benchmark datasets loading functions to use from the benchmark submodule. Defaults to `DEFAULT_BENCHMARK`.
+
+    Returns:
+        DataFrame of computed metrics for every disambiguations and every benchmark dataset.
     """
     if metrics is None:
         metrics = DEFAULT_METRICS
@@ -85,7 +88,6 @@ def inventor_benchmark_plot(disambiguations, metrics=None, benchmarks=None, **kw
     if benchmarks is None:
         benchmarks = DEFAULT_BENCHMARKS
 
-    
     computed_metrics = inventor_benchmark_table(disambiguations, metrics=metrics, benchmarks=benchmarks)
     return px.bar(computed_metrics, y="value", x="metric", color="algorithm", facet_col="benchmark", barmode="group", **kwargs)
 
@@ -134,7 +136,7 @@ def inspect_clusters_to_split(disambiguation, benchmark, join_with=None):
     )
 
     if join_with is not None:
-        clusters_to_split = clusters_to_split.join(join_with, rsuffix="_joined")
+        return clusters_to_split.join(join_with, rsuffix="_joined")
     else:
         return clusters_to_split
 

### 2022-06-23 pv_evaluation/estimators.py

@@ -1,212 +1,0 @@
-"""Estimate full-data performance from biased samples"""
-
-import numpy as np
-import pandas as pd
-import scipy.special as sp
-
-from .metrics.utils import validate_membership
-
-
-def ratio_estimator(B, A):
-    """Ratio estimator for mean(B)/mean(A)"""
-    assert len(A) == len(B)
-
-    A_mean = np.mean(A)
-    B_mean = np.mean(B)
-    n = len(A)
-
-    adj = 1 + ((n - 1) * A_mean) ** (-1) * np.mean(A * (B / B_mean - A / A_mean))
-
-    return adj * B_mean / A_mean
-
-
-def pairwise_precision_estimator(prediction, reference, sampling_type, weights):
-    """Pairwise precision estimates for small non-replacement samples.
-
-    Args:
-        prediction (Series):  membership vector for predicted clusters, i.e. a pandas Series indexed by mention ids and with values representing predicted cluster assignment.
-        reference (Series):  membership vector for sampled reference clusters, i.e. a pandas Series indexed by mention ids and with values representing reference cluster assignment.
-<<<<<<< HEAD
-        sampling_type (str): Sampling mechanism used to obtain reference clusters. Should be one of "record", "cluster", "single_block", or "cluster_block".
-=======
-        sampling_type (str): sampling mechanism used to obtain reference clusters. Should be one of "record", "cluster", "single_block", or "cluster_block".
->>>>>>> main
-            Note that, for "record" sampling, it is assumed that no two different sampled records had the same associated cluster.
-        weights (str): sampling probability weights. Should be one of "uniform" or "cluster_size".
-
-    Returns:
-        float: pairwise precision estimate.
-    """
-    validate_membership(prediction)
-    validate_membership(reference)
-
-    inner = pd.concat({"prediction": prediction, "reference": reference}, axis=1, join="inner", copy=False)
-    vals = inner.groupby(["prediction", "reference"]).size()
-    f_sum = vals.to_frame().assign(cmb=sp.comb(vals.values, 2)).groupby("reference").sum().cmb.sort_index().values
-    cluster_sizes = inner.reference.value_counts(sort=False).sort_index().values
-    P = np.sum(sp.comb(prediction.value_counts(sort=False).values, 2))
-
-    if sampling_type == "record":
-        if weights == "uniform":
-            return len(prediction) * np.mean(f_sum / cluster_sizes) / P
-        elif weights == "cluster_size":
[…]

### 2022-06-23 pv_evaluation/estimators/__init__.py

@@ -1,0 +1,6 @@
+"""Estimate full-data performance from biased samples"""
+
+from pv_evaluation.estimators.pairwise_precision import pairwise_precision_estimator, pairwise_precision_std
+from pv_evaluation.estimators.pairwise_recall import pairwise_recall_estimator, pairwise_recall_std
+
+__all__ = ["pairwise_precision_estimator", "pairwise_precision_std", "pairwise_recall_estimator", "pairwise_recall_std"]

### 2022-06-23 pv_evaluation/templates/render.py

@@ -10,9 +10,12 @@ def render_inventor_disambiguation_report(outdir, summary_table_files, cache=Tru
 
     Args:
         outdir (str): directory where to output html files.
-        summary_table_files (list): list of paths to disambiguation table files (tables with the five columns "mention-id", "inventor_id", "patent_id", "name_first", and "name_last"). 
+        summary_table_files (list): list of paths to disambiguation table files (tables with the five columns "mention-id", "inventor_id", "patent_id", "name_first", and "name_last").
             File format can be one of tsv, csv, or parquet.
         cache (bool, optional): whether or not to cache jupyter chunk execution between runs. Defaults to True.
+
+    Notes:
+        * Summary table filenames are used for figure legends. Keep them short.
     """
     env = Environment(loader=PackageLoader("pv_evaluation", package_path="templates"))
     template = env.get_template("inventor/0-report.qmd")

### 2022-06-23 pv_evaluation/utils.py

@@ -20,4 +20,5 @@ def compare_plots(*figs):
 
 
 def expand_grid(**kwargs):
+    """Get all value combinations."""
     return pd.DataFrame.from_records(itertools.product(*kwargs.values()), columns=kwargs.keys())

### 2022-06-23 setup.py

@@ -22,6 +22,6 @@ if __name__ == "__main__":
             "sklearn",
             "quarto",
             "jinja2",
-            "kaleido"
+            "kaleido",
         ],
     )

### 2022-06-24 pv_evaluation/templates/inventor/0-report.qmd
update

@@
 
-This is report has been automatically generated for the following data sources:
+This is report has been automatically generated for the following data source(s) at {{ datetime }}:
 
-- **Disambiguation summary tables:**
 {% for filename in summary_table_files %}

### 2022-06-24 pv_evaluation/templates/render.py

@@ -3,6 +3,7 @@ import quarto
 from jinja2 import Environment, PackageLoader
 import shutil
 from pkg_resources import resource_filename
+from datetime import datetime
 
 
 def render_inventor_disambiguation_report(outdir, summary_table_files, cache=True, **kwargs):
@@ -27,7 +28,9 @@ def render_inventor_disambiguation_report(outdir, summary_table_files, cache=Tru
     shutil.copyfile(resource_filename("pv_evaluation", "templates/inventor/footer.html"), os.path.join(outdir, "footer.html"))
 
     with open(qmdpath, "w+") as file:
-        file.write(template.render(summary_table_files=summary_table_files))
+        file.write(
+            template.render(summary_table_files=summary_table_files, datetime=datetime.now().strftime("%I:%M%p on %B %d, %Y"))
+        )
 
     if quarto.path() is None:
         raise Exception("Could not find quarto. Is quarto (quarto.org) installed?")

### 2022-06-24 pv_evaluation/benchmark/report.py
update

@@ -11,12 +11,17 @@ from pv_evaluation.metrics import (
     cluster_fscore,
     rand_score,
 )
-from pv_evaluation.benchmark import load_israeli_inventors_benchmark, load_patentsview_inventors_benchmark
+from pv_evaluation.benchmark import (
+    load_israeli_inventors_benchmark,
+    load_patentsview_inventors_benchmark,
+    load_lai_2011_inventors_benchmark,
+)
 
 # Default benchmarks to run.
 DEFAULT_BENCHMARKS = {
     "patentsview-inventors": load_patentsview_inventors_benchmark,
     "israeli-inventors": load_israeli_inventors_benchmark,
+    "lai-benchmark": load_lai_2011_inventors_benchmark,
 }
 DEFAULT_METRICS = {
     "pairwise precision": pairwise_precision,

### 2022-06-25 docs/source/conf.py
update docs

@@ -35,6 +35,8 @@ extensions = [
     "sphinx.ext.autosummary",
     "m2r2",
     "sphinx_lesson",
+    "sphinx.ext.viewcode",
+    "sphinx_design",
 ]
 
 nb_execution_mode = "off"
@@ -61,3 +63,17 @@ html_theme = "pydata_sphinx_theme"
 # relative to this directory. They are copied after the builtin static files,
 # so a file named "default.css" will overwrite the builtin "default.css".
 html_static_path = ["_static"]
+
+html_theme_options = {
+  #"logo_link": "index",
+  "github_url": "https://github.com/patentsview/patentsview-evaluation",
+  #"twitter_url": "https://twitter.com/",
+  "collapse_navigation": True,
+  #"external_links": [
+  #    {"name": "Learn", "url": "https://numpy.org/numpy-tutorials/"}
+  #    ],
+  # Add light/dark mode and documentation version switcher:
+  "navbar_end": ["navbar-icon-links"],
+}
+
+html_last_updated_fmt = '%b %d, %Y'

### 2022-06-25 paper/main.tex

\documentclass[fontsize=11pt]{article}

\renewcommand{\baselinestretch}{2}

\usepackage[english]{babel}

\usepackage[letterpaper,top=1in,bottom=1in,left=1in,right=1in]{geometry}

\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}
\usepackage{natbib}
\usepackage{amssymb, amsthm}
\usepackage{listings}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{authblk}
\usepackage{lineno}
\linenumbers

\newtheorem{theorem}{Theorem}
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}
\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{example}{Example}
\newtheorem{remark}{Remark}

\title{Practical Performance Evaluation of Entity Resolution Algorithms: Lessons Learned at PatentsView.org}

\author[1,2]{Olivier Binette}
\author[1]{Youngsoo Baek}
\author[2]{Aida York}
\author[2]{Emma Hickerson}
\author[2]{Sarvo Madhavan}
\author[2]{Christina Jones}
\affil[1]{Department of Statistical Science, Duke University}
\affil[2]{American Institutes for Research}

\date{\today}

\begin{document}
\maketitle

\begin{abstract}
This paper introduces a novel evaluation methodology for entity resolution algorithms. It is motivated by PatentsView.org, a publicly-available patent data analysis tool which disambiguates patent inventors based on an entity resolution algorithm. We provide a data collection methodology and performance estimators which account for sampling biases. Our approach is simple, practical and principled -- key characteristics which allow us to paint the first representative picture of PatentsView's disambiguation performance. This is used to inform PatentsView's users of the reliability of the data and to allow the comparison of competing disambiguation algorithms.
\end{abstract}

\section{Introduction}
Entity resolution is the task of identifying records in a database which refer to the same entity. An entity may be a person, a company, an object or an event. Records are assumed to contain partially identifying information about these entities. When there is no unique identifier (such as a social security number) available for all records, entity resolution becomes a complex problem which requires sophisticated algorithmic solutions \citep{Herzog2007, Christen2012, Dong2015, Ilyas2019, Christophides2019, Christen2019, Papadakis2021, Binette2022a}.

For instance, the U.S. Patents and Trademarks Office (USPTO) makes available patent data dating back to 1790. However, there is no standard for uniquely identifying inventors on patent applications. The result is a set of ambiguous mentions to inventors, where a single person's name may be spelled in different ways on two applications, and where two different inventors with the same name may be difficult to distinguish. Much research has ben done within the fields of economics, computer science and statistics to disambiguate inventor mentions \citep{trajtenberg2008identification, ferreira2012brief, ventura2013methods, Li2014, Ventura2015, kim2016random, yang2017mixture, morrison2017disambiguation, muller2017semantic, traylor2017learning, balsmeier2018machine,tam2019optimal, monath2019scalable, doherr2021disambiguation}.

The Office of the Chief Economist at the USPTO and the American Institutes for Research (AIR) currently maintain \textbf{PatentsView.org}, a patents knowledge discovery service which provides disambiguated patents data based on statistical entity resolution \citep{toole2021patentsview}. Our paper is motivated by this disambiguation service. Specifically, we are interested in the problem of \textit{evaluating} the accuracy of PatentsView's disambiguation, for the purpose of informing users of the reliability of the data and in order to support methodological research to improve upon PatentsView's disambiguation algorithm. We expand on the evaluation problem below.

\subsection{The Evaluation Problem}\label{sec:challenges}

The entity resolution evaluation problem is to extrapolate from observed performance on small samples to real performance in a database with millions of records. \cite{Wang2022} refers to this as bridging the ``reality-ideality gap" in entity matching, where high performance on benchmark datasets often does not translate in the real world. Here, performance may be defined as any combination of commonly used evaluation metrics for entity resolution, such as precision and recall, cluster homogeneity and completeness, rand index, or generalized merge distance \citep{Maidasani2012}. These metrics can be computed on benchmark datasets for which we have a ground truth disambiguation. However, the key evaluation problem is to obtain estimates which are representative of performance on the full data for which no ground truth disambiguation is available. This is challenging for the following reasons.

First, entity resolution problems scale non-linearly. While it may be easy to disambiguate a small dataset, the opportunity for errors grows \textit{quadratically} in the number of records. As such, we may observe good performance of an algorithm on a small benchmark dataset, while the true performance of on the entire data may be something else entirely.\footnote{This particular effect of dataset size in entity resolution is explored in \cite{Draisbach2013} in the context of choosing similarity thresholds.} This is a problem that PatentsView.org currently faces. Despite encouraging performance evaluation metrics on benchmark datasets, with nearly perfect precision and recall reported in the latest methodological report \citep{Monath2021}, the data science team at AIR observes lower real-world accuracy.

A second problem is large class imbalance in entity resolution \citep{Marchant2017}. Among all pairs of records, only a small fraction (usually much less than a fraction of a percent) refer to the same entity. The vast majority of record pairs are not a match. This makes it difficult to evaluate performance through random sampling.

A third problem is the multiplicity of sampling mechanisms used to obtain benchmark datasets. To construct hand-disambiguated datasets, blocks, entity clusters, or predicted clusters may be sampled with various probability weights. These sampling approaches must be accounted for in order to obtain representative performance estimates \citep{fuller2011sampling}.

Our approach, detailed in sections \ref{sec:approach} and \ref{sec:proposed_estimators}, addresses these challenges by putting forward cluster-based expressions for performance metrics which reflect various sampling schemes. Each of these representations immediately suggests simple estimators which properly account for the above issues.

\begin{example}[Bias of precision computed on benchmark datasets]\label{first_example}
    To exemplify the problem with the trivial use of performance evaluation metrics on benchmark datasets, we have carried out a simple experiment which is described in detail in appendix \ref{appendix:example}. In short, we considered evaluating a disambiguation algorithm by sampling ground truth clusters and computing pairwise precision\footnote{Pairwise precision is the probability that a pair of record predicted to be a match is indeed a match. See section \ref{sec:proposed_estimators} for a formal definition} on this set of sampled clusters. This is analogous to the way that many real-world benchmark data sets are obtained and used. For reference, it is known that the disambiguation algorithm has a precision of $52\%$ for the entire dataset.

    \begin{figure}[h]
        \centering
        \includegraphics[width=5.5in]{first-example}
        \caption{Distribution of precision estimates versus the true precision of $52\%$ (shown as a dotted vertical line). Panel \textbf{A} shows the trivial precision estimates computed for sampled records. Panel \textbf{B} shows our proposed precision estimates which accounts for the sampling mechanism. Sample bias and root mean squared error (rmse) are reported on each figure.}
        \label{fig:precision_problem}
    \end{figure}

    In panel \textbf{A} of figure \ref{fig:precision_problem} below, we see the distribution of precision estimates versus the true precision of $52\%$ shown as a dotted vertical line. Precision estimates are most of the time very close to $100\%$ and always higher than $80\%$, despite the truth being a precision of only $52\%$. In contrast, panel \textbf{B} shows the distribution of our proposed precision estimator which is nearly unbiased. Both precision estimators rely on exactly the same data. They only differ in how they account for the underlying sampling process and the extrapolation from small benchmark datasets to full data.

\end{example}

\subsubsection{Why Bother With Evaluation?}

There are two main uses for accurate and statistically rigorous evaluation methodology.

The first is model selection and comparison. PatentsView.org continually works at improving disambiguation methodology. This requires choosing between alternative methods and evaluating the results of methodological experiments. Without sound evaluation methodology, decisions regarding the disambiguation algorithm may be misaligned from real-world use and real-world performance. Notably, for a performance metric such as the pairwise f-score, one algorithm may perform better than another on a small benchmark dataset, while the opposite may hold true for performance on the entire data. This problem happens on typical benchmark datasets obtained from randomly sampling blocks or randomly sampling clusters (see section \ref{sec:proposed_estimators} for a definition of different sampling mechanisms).

The second is adequate use of disambiguated data. PatentsView.org's disambiguation results have been used in numerous scientific studies \citep{toole2021patentsview}. These studies make assumptions about the reliability of the data which need to be validated and upheld. In short, users of disambiguated data need to understand its reliability in order to make scientifically appropriate use of it. Evaluation aims to provide this rigorous reliability information.

\subsubsection{Past Work}

Much of past work has focused on defining and using relevant clustering evaluation metrics. The topic of estimating performance from samples has received much less attention, usually focusing on importance sampling estimators based on record pairs. We review contributions to these two main topics in the paragraphs below.

\paragraph{Metrics}

Pairwise precision and recall metrics were first reported in \cite{Newcombe1959}, with \cite{Bilenko2003, Christen2007} emphasizing the importance of precision-recall curves for algorithm evaluation. Now, there are issues with the use of pairwise precision and recall in entity resolution applications, such as the large relative importance of large clusters. As such, other clustering metrics have been proposed, including cluster precision and recall, cluster homogeneity and completeness, and the generalized merge distance \citep{Michelson2009, Menestrina2010, Maidasani2012, Barnes2015}. Important practical issues regarding the use of aggregate metrics are discussed in \cite{Hand2018}.

\paragraph{Estimation}

Regarding the reliable estimation of performance metrics, \cite{Belin1995} first proposed a semi-supervised approach to calibrate error rates when using a Fellegi-Sunter model \citep{fellegi_theory_1969}. \cite{Marchant2017} proposed an adaptive importance sampling estimator to estimate precision and recall from sampled record pairs. Other approaches to the estimation of performance metrics are model-based, where estimated precision and recall can be obtained from predicted match probabilities between record pairs \citep{enamorado2019using}. However, these model-based approaches cannot be used when working with black-box machine learning models or ad hoc clustering algorithms.

\subsubsection{Our Approach}\label{sec:approach}

Our approach to estimating performance metrics is based on the use of benchmark datasets which are already existing or which can be collected in a cost-effective way. This data contains entity clusters corresponding to sampling records and recovering all associated instances, to directly sampling clusters, or to sampling blocks. For each of these sampling processes, we propose estimators which correct for the issues discussed in section \ref{sec:challenges}, which are nearly unbiased, and which are easy to use in practice.

Our approach has the following advantages:
\begin{enumerate}
    \item It can leverage existing benchmark datasets as well as new datasets collected specifically for performance evaluation.
    \item It can easily be generalized to estimate other clustering metrics, such as cluster precision, cluster recall, cluster homogeneity and completeness, and other generalized merge distances.
    \item For evaluation, the review of entity clusters is much more efficient than the review of record pairs. We can achieve high accuracy with small samples without relying on any sophisticated sampling scheme.
\end{enumerate}

In short, the proposed approach is simple, principled, and practical. It is simple to use, it is statistically principled in its account of sampling processes and in its uncertainty quantification, and it is practical in the way that it can provide cost-effective estimates for any disambiguation algorithm.

\subsection{Structure of the Paper}

The rest of the paper is organized as follows. In section \ref{sec:data_methods}, we introduce motivating benchmark datasets, we describe our data collection process for evaluation, we introduce the proposed estimators, and we summarize our simulation study used to validate the performance of our estimators. Section \ref{sec:results} then shows the results -- our performance estimates and results from the simulation study. Finally, section \ref{sec:discussion} summarizes the paper and discusses open research directions.

\section{Data and Methodology}\label{sec:data_methods}

In this section, we review motivating datasets used at PatentsView, we introduce our hand-disambiguation methodology, we describe our proposed performance metric estimators, and we describe our simulation framework used to compare estimators.

\subsection{Benchmark Datasets for Inventor Disambiguation}

We consider the following benchmark datasets for inventor disambiguation.

\paragraph{Israeli Inventors Benchmark}
\cite{trajtenberg2008identification} disambiguated the US patents of Israeli inventors which were granted between 1963 and 1999. A total of 6,023 Israeli inventors were identified for this time period with 15,310 associated patents.

\paragraph{\cite{Li2014}'s Inventors Benchmark}

Based on an original dataset from \cite{gu2008march}, \cite{Li2014} disambiguated the patent history (between 1975 and 2010) of 95 US inventors.

\subsection{Hand-Disambiguation Protocol}\label{sec:hand-disambiguation}

In addition to the above benchmark datasets, we have carried out a data collection experiment which was motivated by the evaluation, using the proposed estimators discussed in section \ref{sec:proposed_estimators}, of the current PatentsView inventor disambiguation.

In total, 100 inventors were sampled with probability proportional to their number of granted patents. This was done by sampling inventor mentions uniformly at random and recovering all patents for a given inventor. These inventor mentions were from US patents granted between 1976 and December 31, 2021.

Two AIR staff were tasked with recovering inventors' patents given sampled inventor mentions. To do this, they were assisted by tools available on PatentsView.org. First, given a sampled inventor, the associated predicted cluster was reviewed and wrongly assigned patents were removed. Next, PatentsView's search tools were used to find additional mentions of similarly named inventors. These were reviewed and added to the predicted cluster if appropriate. The two AIR staff had an initial training session, followed by a test run on 10 inventors, before carrying out the rest of the data collection. They worked independently so that two resulting datasets were obtained for the same inventor mentions. In section \ref{sec:results}, these are referred to as the \textbf{Staff 1} and \textbf{Staff 2} datasets.

Note that our data collection methodology is biased towards PantentsView's current disambiguation. In cases where no errors were found, the current disambiguation was assumed to be correct. Performance estimates based on this data might therefore be slightly optimistic.

\subsection{Proposed Performance Estimators}\label{sec:proposed_estimators}

Throughout the rest of the paper, we focus on pairwise precision and pairwise recall (defined below in \eqref{eq:def_P_R}) as our performance evaluation metrics.

%We propose precision and recall estimators based on different sampling processes for ground truth data. In practice, ground truth data may be obtained by sampling records and recovering the clusters associated to each record. For example, patents may be sampled and, for each inventor mention, we can find all other patents authored by the same person. Alternatively, disjoint \textit{blocks} may be sampled and hand-disambiguated. Here, a block is a set of records assumed to cover complete clusters. For example, we can sample inventors from specific disciplines or from specific nationalities. The Israeli Benchmark dataset described in XX is an example of a single block sample. The choice of sampling process and sampling weights naturally suggests estimators which are described next. Note that all proofs are in appendix \ref{appendix:proofs}.

\subsubsection{Representation Lemmas}

First, we define pairwise precision and recall in terms of the number of links between records. Let $\mathcal{D} = \{1, 2, 3, \dots, N\}$ index a set of records let $\mathcal{C}$ be the partition of $\mathcal{D}$ representing ground truth clustering, and let $\widehat{\mathcal{C}}$ be a set of predicted clusters. Now let $\mathcal{T}$ be the set of record pairs which appear in the same cluster in $\mathcal{C}$ (matching pairs), and let $\mathcal{P}$ be the set of record pairs which appear in the same predicted cluster in $\widehat{\mathcal{C}}$ (predicted links). Pairwise precision ($P$) and pairwise recall ($R$) are then defined as
\begin{equation}\label{eq:def_P_R}
    P = \frac{\lvert \mathcal{T} \cap \mathcal{P} \rvert}{\lvert \mathcal{P} \rvert}, \quad R = \frac{\lvert \mathcal{T} \cap \mathcal{P} \rvert}{\lvert \mathcal{T} \rvert}.
\end{equation}

Note that $P = R \, \lvert \mathcal{T} \rvert / \lvert \mathcal{P} \rvert$. As such, precision and recall are equal if and only if the right number of matching pairs is predicted under $\widehat{\mathcal{C}}$.

We now provide three alternative representations of precision and recall which correspond to the processes of sampling records, sampling true clusters, and sampling blocks. These will be used to obtain precision and recall estimators under these sampling processes.

\paragraph{Record Sampling Representation}
For a given $i \in \mathcal{D}$, let $c(i) \in \mathcal{C}$ be the ground truth cluster associated with $i$ in $\mathcal{C}$. For a given $c \in \mathcal{C}$, we define
\begin{equation}
    f(c,\, \widehat{\mathcal{C}}) = \sum_{\hat c \in \hat{\mathcal{C}}} { \lvert c \cap \hat c \rvert \choose 2 }, \quad g(c,\, \widehat{\mathcal{C}}) = \frac{f(c,\, \widehat{\mathcal{C}}) }{\sum_{\hat c \in \hat{\mathcal{C}}} { \lvert \hat c \rvert \choose 2 }}.
\end{equation}
\begin{lemma}\label{lemma:record_sampling_representation}
If $i$ is distributed over $\mathcal{D}$ with probabilities $p_i > 0$, then
\begin{equation}
    P = \mathbb{E} \left[ \frac{g(c(i),\, \widehat{\mathcal{C}})}{p_i \lvert c(i) \rvert} \right], \quad R = 2\frac{\mathbb{E}\left[ f(c(i),\, \widehat{\mathcal{C}})  \big/ (\lvert c(i) \rvert p_i) \right]}{\mathbb{E}\left[ (\lvert c(i) \rvert - 1) / p_i \right]}.
\end{equation}
\end{lemma}

\paragraph{Cluster Sampling Representation}

In the cluster sampling case, sampling probabilities are typically known only up to normalizing factors. This is due to the fact that the total number of true clusters and other aspects of the ground truth cluster distribution are unknown in practice. As such, we provide expressions for precision and recall which only require knowing sampling probabilities up to normalizing factors. This allows the consideration of sampling uniformly at random and sampling clusters with probability proportional to their size.

\begin{lemma}\label{lemma:cluster_sampling_representation}
If $c$ is distributed over $\mathcal{C}$ with probabilities proportional to $p_c > 0$, then
\begin{equation}\label{eq:lemma_1}
    P = \frac{N\, \mathbb{E} \left[ g(c,\, \widehat{\mathcal{C}})/p_c \right]}{\mathbb{E} \left[ \vert c \rvert /p_c \right]}, \quad R = \frac{\mathbb{E}\left[ f(c, \widehat{\mathcal{C}})/p_c \right]}{\mathbb{E}\left[ {\lvert c \rvert \choose 2}/p_c \right]}.
\end{equation}
\end{lemma}

Note that, with clusters sampled with probability proportional to their size, the expression for precision simplifies to
$
    P = N\, \mathbb{E} \left[ g(c,\, \widehat{\mathcal{C}})/\lvert c \rvert \right].
$

\begin{remark}
    Lemma \ref{lemma:record_sampling_representation} and lemma \ref{lemma:cluster_sampling_representation} can be generalized to apply to any performance metric which can be expressed as a sum $\sum_{c \in \mathcal{C}} h(c, \widehat{\mathcal{C}})$, for some function $h$, or as a function of such sums. For instance, the use of the so-called \textit{cluster} precision and \textit{cluster} recall \citep{}, or of cluster homogeneity and completeness \citep{}, can be more appropriate in the presence of large clusters. We leave these generalizations as extensions of our work.
\end{remark}

\paragraph{Disjoint Block Sampling Representation}

Let $\mathcal{B}$ be a partition of $\mathcal{D}$ such that for every $ c \in \mathcal{C}$, there exists $b \in \mathcal{B}$ with $c \subset b$. For a given $b \in \mathcal{B}$, let $\mathcal{T}_b$ be the set of ground truth links contained within $b$, let $\mathcal{P}_b$ be the set of predicted links contained within $b$, and let $\mathcal{P}_b^{-}$ be the set of predicted links with a single record in $b$ (i.e., $\mathcal{P}_b^{-}$ is the set of outgoing links from $b$).

\begin{lemma}\label{lemma:block_sampling_representation}
If $b$ is distributed over $\mathcal{B}$ with probabilities proportional to $p_b > 0$, then
\begin{equation}\label{eq:lemma_3}
    P = \frac{\mathbb{E}\left[ \lvert \mathcal{T}_b \cap \mathcal{P}_b \rvert / p_b \right]}{\mathbb{E}\left[ (\lvert \mathcal{P}_b \rvert + \tfrac{1}{2} \lvert \mathcal{P}_b^{-} \rvert)/p_b \right]}, \quad R = \frac{\mathbb{E}\left[ \lvert \mathcal{T}_b \cap \mathcal{P}_b \rvert / p_b \right]}{\mathbb{E}\left[ \lvert \mathcal{T}_b \rvert / p_b \right]}.
\end{equation}
\end{lemma}

\begin{remark}
    Lemmas \ref{lemma:record_sampling_representation} -- \ref{lemma:block_sampling_representation} are formulated in terms of sampled ground truth clusters and sampled blocks which do not contain errors. However, given the duality between precision and recall (interchanging the roles between $\mathcal{C}$ and $\widehat{\mathcal{C}}$  interchanges precision and recall), the results also apply to sampling \textit{predicted} clusters.
\end{remark}

\subsubsection{Proposed Estimators}

All of the expressions for precision and recall in lemmas \ref{lemma:record_sampling_representation} -- \ref{lemma:block_sampling_representation} are either population means or ratios of population means. As such, they can be estimated using sample means and ratios of sample means. For readability, we present here a generic formula for an approximately unbiased estimator of the ratio of means, and then specify the needed quantities for each representation below. The estimator applies a first order bias correction to the ratio of sample means, based on Taylor approximation. Approximate confidence intervals can be computed based on the variance estimator of the ratio of sample means by Taylor approximation, assuming the corrected estimator has small bias \citep{fuller2011sampling}. The generic formula for estimating the ratio of $T$-sized ``population'' (of records/clusters/blocks) means of the form
\begin{align}
    E=\frac{1/T\sum_{i=1}^{T} B_i}{1/T\sum_{i=1}^T A_i},
\end{align}
assuming we have sampled $n$ elements (records/clusters/blocks), is
\begin{align}\label{eq:bias_adjustment}
    \widehat{E}=\frac{\bar{B}_n}{\bar{A}_n}\left\{1 + \frac{\theta_{n,T}}{n(n-1)}\frac{1}{\bar{A}_n}\sum_{s=1}^n A_s
    \left(\frac{B_s}{\bar{B}_n} - \frac{A_s}{\bar{A}_n}\right)\right\},\;
    \bar{A}_n = \frac{1}{n}\sum_{s=1}^{n}A_s,\;
    \bar{B}_n = \frac{1}{n}\sum_{s=1}^{n}B_s
\end{align}
We note that an additional symbol $\theta_{n,T}$ is introduced for possible finite population correction when relatively large number of elements are sampled without replacement (see below). Classical adjustment is to set $\theta_{n,T} = (1 - \frac{n-1}{T-1})$ \citep{Cochran1977}. For practical purposes when $T$ is large, often $\theta_{n,T}=1$ will suffice. In fact, knowledge of $T$ is not needed at all as long as it is large enough relative to $n$, which is useful because the total number of true clusters/blocks is not known in advance. Confidence interval can be computed based on the variance estimate of the above, which is
\begin{align} \label{eq:estimated_variance}
    \widehat{V}(\widehat{E})=\left( \frac{\bar{B}_n}{\bar{A}_n} \right)^2\frac{\theta_{n,T}}{n(n-1)}
    \sum_{s=1}^n \left( \frac{A_s^2}{\bar{A}_n^2} + \frac{B_s^2}{\bar{B}_n^2} - 2\frac{A_sB_s}{\bar{A}_n\bar{B}_n} \right).
\end{align}

The specific values for $A_s$, $B_s$, and $T$ in each of our representation is described in appendix X.

%\begin{remark}
%    There are many ways to define ratio estimators. For small samples and given prior knowledge, Bayesian approaches would be the most appropriate. In this paper, we have opted for the simple estimators since they are sufficient for our application and demonstrate the strength of our methodology.
%\end{remark}

\begin{remark}
    In entity resolution applications, we can typically assume that elements have been sampled with replacement (or closely so). Indeed, with a small proportion of sampled elements, non-replacement samples are approximately equivalent to samples with replacement. However, if dealing with relatively large non-replacement samples, then the sampling probabilities used in the definition of the estimators should be adjusted to reflect the size-dependent effect of non-replacement \citep{Horvitz1952}.
\end{remark}

\subsection{Simulation Study}\label{sec:simulation_study}

In order to assess the performance of the proposed estimators, we carry out a simulation study based on PatentsView's inventor disambiguation. Specifically, in the context of the simulation, we consider PatentsView current inventor disambiguation as the ground truth clustering. A simulated set of predicted clusters is obtained by introducing errors (misattribution of inventor mentions) into the current disambiguation. We then estimate the precision and recall of this predicted clustering using our estimators based on random cluster samples. The process of sampling clusters and estimating precision/recall is repeated $100$ times in order to provide the distribution of the estimators and metrics such as bias and root mean squared error (rmse).

To introduce errors, we pick records at random and change their cluster assignment to that of other records picked at random. This is a simple process which ensures that larger clusters are more likely to contain errors. In our simulation, we consider rates of $5\%$, $10\%$, and $25\%$ for the proportion of records that are sampled for cluster misassignment. The larger proportions of error are more realistic. However, the $5\%$ misattribution rate helps showcase properties of our estimators when only a small portion of sampled clusters are associated with errors.

For the sampling process, we consider sampling records uniformly at random and recovering their associated clusters. This is the same as sampling clusters with probability proportional to their size. In the record/cluster sampling cases, we look at the effect of sampling $100$, $200$ and $400$ records/clusters.

Finally, we compare the following three precision and recall estimators:
\begin{description}
    \item[\texttt{P\_naive}, \texttt{R\_naive}] This is the ``naive" precision (resp. recall) estimator obtained by computing precision (resp. recall) when only looking at records which appear in the sampled clusters.
    \item[\texttt{P\_record}, \texttt{R\_record}] These are the precision and recall estimators corresponding to uniformly sampling records in lemma \ref{lemma:record_sampling_representation} ($p_i \propto 1$) with the bias adjustment given in \eqref{eq:bias_adjustment}. Note that these are the same as the estimators obtained from lemma \ref{lemma:cluster_sampling_representation} when sampling clusters with probability proportional to their size ($p_c \propto \lvert c \rvert$).
    \item[\texttt{P\_cluster\_block}] This is the precision estimator obtained by considering each sampled cluster as its own block in lemma \ref{lemma:block_sampling_representation}, where clusters have been sampled with probability proportional to their size ($p_b \propto \lvert b \rvert$), and with bias adjustment given in \eqref{eq:bias_adjustment}. Note that in the case of recall with cluster blocks, the estimator corresponding to lemma \ref{lemma:block_sampling_representation} is the same as the one corresponding to lemma \ref{lemma:cluster_sampling_representation} and lemma \ref{lemma:record_sampling_representation}.
\end{description}

\section{Results}\label{sec:results}

\subsection{Results From the Simulation Study}

Figure \ref{fig:sim_records_precision} shows the distribution of the three precision estimators used in the simulation study (see section \ref{sec:simulation_study}) compared to ground truth precision. The block sampling estimator \texttt{P\_cluster\_block} is highly accurate, while \texttt{P\_record} is more variable and \texttt{P\_naive} is entirely uninformative. Note that \texttt{P\_record} can take values greater than $1$ (not shown in this figure), so that truncating it to be less than $1$ introduces a bias in some cases.

The reason why \texttt{P\_cluster\_block} performs better than \texttt{P\_record} is due to the fact that \texttt{P\_record} has been derived in a generic way which applies to any performance metric which can be expressed in cluster form similar to \eqref{eq:lemma_1}. On the other hand, \texttt{P\_cluster\_block} relies on speific properties of precision. Among other things, this ensures that \texttt{P\_cluster\_block} is constrained to be between $0$ and $1$. In practice, \texttt{P\_cluster\_block} should be preferred as a pairwise precision estimator.

\begin{figure}
    \centering
        \caption{Distribution of precision estimates for various sample sizes and misattribution rates, as described in section \ref{sec:simulation_study}. Ground truth precision is marked by a dotted vertical line. The \texttt{rate} variable represents the percentage misattribution rate. The estimator \texttt{P\_cluster\_block} is highly accurate, while \texttt{P\_naive} is almost always close to $1.0$, having little to do with the true precision.}
    \includegraphics[width=\linewidth]{sim_records_precision}
    \label{fig:sim_records_precision}
\end{figure}

Bias and root mean squared error are reported in table \ref{tab:precision_results}.

\begin{table}\label{tab:precision_results}
    \centering
    \caption{\centering Bias and root mean squared error of precision estimators for the simulation study described in section \ref{sec:simulation_study}. The \texttt{rate} variable represents the percentage misattribution rate.}
\begin{tabular}{llccccccccc}
\toprule
{} & \hfill{\textbf{rate}} & \multicolumn{3}{c}{5} & \multicolumn{3}{c}{10} & \multicolumn{3}{c}{20} \\
\cmidrule(lr){3-5}\cmidrule(lr){6-8}\cmidrule(lr){9-11}
{} & \hfill{\textbf{sample size}} & {100} & {200} & {400} & {100} & {200} & {400} & {100} & {200} & {400} \\
\midrule
\multirow[c]{4}{*}{\textbf{bias}} & P\_cluster\_block & -0.004 & -0.002 & -0.001 & -0.002 & -0.001 & 0.001 & -0.004 & -0.001 & -0.000 \\
 & P\_naive & 0.099 & 0.099 & 0.099 & 0.195 & 0.195 & 0.195 & 0.366 & 0.366 & 0.365 \\
 & P\_record & -0.002 & 0.013 & 0.009 & -0.001 & 0.011 & 0.008 & -0.001 & 0.009 & 0.006 \\
\midrule
\multirow[c]{4}{*}{\textbf{rmse}} & P\_cluster\_block & 0.045 & 0.033 & 0.021 & 0.041 & 0.038 & 0.026 & 0.063 & 0.052 & 0.034 \\
 & P\_naive & 0.099 & 0.099 & 0.099 & 0.195 & 0.195 & 0.195 & 0.366 & 0.366 & 0.365 \\
 & P\_record & 0.294 & 0.232 & 0.169 & 0.260 & 0.205 & 0.150 & 0.207 & 0.162 & 0.117 \\
\bottomrule
\end{tabular}
\end{table}

Regarding recall, figure \ref{fig:recall_results} shows the distribution of the two estimators used in the simulation study. The naive recall estimator performs well in this case. However, the recall estimator accounting for the sampling mechanism is more accurate. Bias and root mean squared error (rmse) are reported in table \ref{tab:recall_results}.

\begin{figure}
    \centering
        \caption{Distribution of recall estimates for various sample sizes and misattribution rates, as described in section \ref{sec:simulation_study}. Ground truth recall is marked by a dotted vertical line. The \texttt{rate} variable represents the percentage misattribution rate.}
    \includegraphics[width=\linewidth]{sim_records_recall}
    \label{fig:recall_results}
\end{figure}

\begin{table}\label{tab:recall_results}
    \centering
    \caption{\centering Bias and root mean squared error of recall estimators for the simulation study described in section \ref{sec:simulation_study}. The \texttt{rate} variable represents the percentage misattribution rate.}
\begin{tabular}{llccccccccc}
\toprule
{} & {\textbf{rate}} & \multicolumn{3}{c}{{5}} & \multicolumn{3}{c}{10} & \multicolumn{3}{c}{20} \\
\cmidrule(lr){3-5}\cmidrule(lr){6-8}\cmidrule(lr){9-11}
{} & {\textbf{sample size}} & {100} & {200} & {400} & {100} & {200} & {400} & {100} & {200} & {400} \\
\midrule
\multirow[c]{2}{*}{\textbf{bias}} & R\_naive & 0.0007 & 0.0001 & 0.0004 & 0.0009 & -0.0015 & -0.0024 & -0.0008 & -0.0010 & -0.0017 \\
 & R\_record & 0.0002 & -0.0001 & -0.0002 & 0.0011 & -0.0002 & -0.0004 & 0.0005 & 0.0001 & -0.0002 \\
 \midrule
\multirow[c]{2}{*}{\textbf{rmse}} & R\_naive & 0.0089 & 0.0056 & 0.0043 & 0.0123 & 0.0089 & 0.0075 & 0.0132 & 0.0109 & 0.0091 \\
 & R\_record & 0.0060 & 0.0037 & 0.0028 & 0.0089 & 0.0056 & 0.0039 & 0.0099 & 0.0071 & 0.0050 \\
\bottomrule
\end{tabular}

\end{table}

\subsection{Evaluation of PatentsView's Disambiguation}

Table \ref{tab:results} shows estimated pairwise precision and recall from benchmark datasets and from our two hand-curated datasets. Note that each estimate is associated with a given population of inventor mentions which is a subset of granted US patents since 1976. We focused on US patents granted since 1976 as this is the main data product of patentsview.org.

The choice of estimators for the results presented in table \ref{tab:results} is as follows.
Since our two hand-curated datasets (see section \ref{sec:hand-disambiguation}) were obtained by sampling inventor clusters with probabilities proportional to cluster sizes, we used the \texttt{P\_cluster\_block} and \texttt{R\_record} estimators with corresponding probability weights. 
For the Israeli benchmark dataset, we assumed that a single block of inventor clusters were sampled alltogether and used the corresponding estimators defined through \eqref{eq:lemma_3} with a single block sample. Note that no variance estimates can be given for single samples.
For \cite{Li2014}'s inventors benchmark, given that inventor clusters were originally obtained from a set of inventor curriculum vitae, we assumed that inventor clusters were sampled uniformly at random. As such, we used cluster block estimators with constant probability weights.

\begin{table}[!h]
    \label{tab:results}
    \centering
    \caption{\centering Estimated pairwise precision and recall (with estimated standard deviation) from our four benchmark datasets.}
    \begin{tabular}{lccc}
    \toprule
    \textbf{dataset} & \textbf{est. precision ($\hat \sigma$)} & \textbf{est. recall ($\hat \sigma$)} & \textbf{scope} \\
    \midrule
    Staff 1 & 86\% (5.6\%) & 94\% (2.1\%)  & 1976 -- Dec. 31, 2022 (US granted)\\
    Staff 2 & 88\% (5.6\%) & 95\% (2.0\%) & 1976 -- Dec. 31, 2022 (US granted)\\
    Israeli Benchmark & 79\% (NA) & 94\% (NA) & 1976 -- 1999 (US granted)\\
    \cite{Li2014}'s Benchmark & 91\% (2.7\%) & 91\% (5.0\%) & 1976 -- 2010 (US granted)\\
    \bottomrule
    \end{tabular}
\end{table}

It is interesting to note that there is a small but notable difference in the estimates from the ``Staff 1" and ``Staff 2" datasets. Since these datasets were obtained by two different people from the same sample of inventor mentions, the difference in estimates is due to differences in the hand-disambiguation provided by the two staff. Staff 2 was slightly more conservative than Staff 1 in flagging errors.

Overall, our performance estimates paint the first realistic picture of PatentsView's disambiguation accuracy in practice. Precision is not nearly 100\%, as would be assumed from naively computing precision on benchmark datasets. Rather, there is significant room for improvement. Our hand-curated datasets and data collection methodology provide the necessary basis to investigate errors and plan for improvements to the disambiguation algorithm.

\section{Discussion}\label{sec:discussion}

Motivated by PatentsView's disambiguation, this paper introduced a novel evaluation methodology for entity resolution algorithms. The methodology relies on benchmark datasets containing ground truth clusters and estimators which account for biases inherent to these datasets. For PatentsView, this provided the first representative estimates of disambiguation performance. Furthermore, all data and code used in this paper, as well as other tools developed to facilitate evaluation at PatentsView, are freely available at \hyperref[https://github.com/PatentsView/PatentsView-Evaluation/]{https://github.com/PatentsView/PatentsView-Evaluation/}.

There are two main resulting products for this work. The first is to provide PatentsView data users with an appropriate understanding of PatentsView data quality. Our performance estimates indicate that, despite an overall accurate disambiguation, there is room for improvement and the disambiguation algorithm estimates more links then there truly are. The second product is the set of tools needed for methodological research and model comparison. Given our evaluation methodology, we can now reliably compare algorithms and decide with confidence on changes which will affect users.

\section*{Data and Code}

All data and code used for this paper are available as part of the PatentsView-Evaluation Python package at \hyperref[https://github.com/PatentsView/PatentsView-Evaluation/]{https://github.com/PatentsView/PatentsView-Evaluation/}.

%\section*{Acknowledgements}

\section*{Author Contributions}

Olivier Binette led the project and wrote the bulk of the manuscript. Youngsoo Baek provided bias adjustment and uncertainty quantification for ratio estimators. Aida York and Emma Hickerson carried out data collection by manually reviewing inventor clusters. Sarvo Madhavan was a technical advisor and contributed to code. Christina Jones was an advisor and project manager. All authors provided input on the manuscript.

\bibliographystyle{chicago}
\bibliography{biblio}

\appendix

\section{Appendix}

\subsection{Bias of precision computed on benchmark datasets}\label{appendix:example}

This section provides more information regarding example \ref{first_example}.

For this example, we considered the RLdata10000 dataset from \citep{}. This is a synthetic dataset containing 10,000 records with first name, last name, and date of birth attributes. There is noise in these attributes and a $10\%$ duplication rate. Ground truth identity is known for all records.

The disambiguation algorithm we consider matches records together if any of the following conditions is met:
\begin{itemize}
    \item records match on first name, last name, and birth year,
    \item records match on first name, birth day, and birth year, or
    \item records match on last name, birth day, and birth year.
\end{itemize}
Note that this is not at all a good disambiguation algorithm. It has $52\%$ precision and $83\%$ recall. However, it allows to to showcase the issue with non-adjusted precision computed on cluster samples.

In our experiment, we have repeated 5,000 times the following 3-steps process:
\begin{enumerate}
    \item First, 200 records were sampled and the ground truth clusters associated to them were recovered. This provided a ``benchmark" dataset which was used for evaluation.
    \item Second, a trivial precision estimate was obtained by computing precision over the benchmark dataset. That is, predicted cluster assignments were restricted to records which appear in the benchmark data and precision was compared for this. Most often than not, the result was an observation of $100\%$ precision.
    \item Third, we computed our proposed precision estimator which corresponds to lemma \ref{lemma:record_sampling_representation} and the estimator $\widehat P_{\text{block}}$ defined in equation \eqref{eq:P_block}, with blocks corresponding to clusters and with sampling probabilities $p_b \propto \lvert b \rvert$.
\end{enumerate}
The distributions of the these two precision estimates over the 5,000 repetitions are shown in figure \ref{fig:precision_problem}. Our proposed estimator is accurate and nearly unbiased, whereas the trivial precision estimates have almost nothing to do with actual algorithmic performance.

\subsection{Precision and Recall Estimator Formulas}

This section describes specific values for $A_s$, $B_s$, and $T$ in \eqref{eq:bias_adjustment} in order to obtained nearly unbiased precision and recall estimators based on each of the representation in XX. We use the symbols $\widehat P$ and $\widehat R$, indexed by one of ``$\text{rec}$", ``$\text{clust}$", and ``$\text{block}$", in order to refer to precision and recall estimators corresponding to record, cluster, and block sampling representations.

\paragraph{Record Sampling Estimators}

\begin{description}
    \item[$\widehat{P}_{\text{rec}}$]{Estimating $P$ is a special case that does not require ratio-of-means estimation. We propose to use a simple unbiased estimator:}
    \begin{align}\label{eq:P_rec}
        \widehat{P}_{\text{rec}} =
        \frac{1}{n}\sum_{s=1}^{n}\frac{g(c(i_s),\widehat{\mathcal{C}})}{|c(i_s)|p_{i_s}}.
    \end{align}
    The unbiased estimator of the variance of $\widehat{P}_{\text{rec}}$ is also available:
    \begin{align}
        \widehat{V}(\widehat{P}_{\text{rec}}) = 
        \frac{\theta_{n,N}}{n(n-1)}\sum_{s=1}^{n}\left(
        \frac{g(c(i_s),\widehat{\mathcal{C}})^2}{|c(i_s)|^2p_{i_s}^2} - 
        \widehat{P}_{\text{rec}}^2.
        \right)
    \end{align}
    \item[$\widehat{R}_{\text{rec}}$]{Going forward, we refer to formulae \eqref{eq:bias_adjustment} and \eqref{eq:estimated_variance}. $\widehat{R}_{\text{rec}}$ and its variance estimate $\widehat{V}(\widehat{R}_{\text{rec}})$ are given by \eqref{eq:bias_adjustment} and \eqref{eq:estimated_variance}, where we substitute in}
    \begin{align}
    T = N,\; A_s = \frac{(\lvert c(i_s) \rvert - 1)}{p_{i_s}},\; 
    B_s = 2\frac{f(c(i_s),\widehat{\mathcal{C}})}{|c(i_s)|p_{i_s}}.
    \end{align}
\end{description}

\paragraph{Cluster Sampling Estimators}

\begin{description}
    \item[$\widehat{P}_{\text{clust}}$]{The estimator and its variance estimate $\widehat{V}(\widehat{P}_{\text{clust}})$ are given by \eqref{eq:bias_adjustment} and \eqref{eq:estimated_variance}, where we substitute in}
    \begin{align}
        T = |\mathcal{C}|,\; A_s = \frac{|c_s|}{p_{c_s}},\; B_s = N\frac{g(c_s,\widehat{\mathcal{C}})}{p_{c_s}}.
    \end{align}
    \item[$\widehat{R}_{\text{clust}}$]{The estimator and its variance estimate $\widehat{V}(\widehat{R}_{\text{clust}})$ are given by \eqref{eq:bias_adjustment} and \eqref{eq:estimated_variance}, where we substitute in}
    \begin{align}
    T = |\mathcal{C}|,\; A_s = \frac{{\lvert c_s \rvert \choose 2}}{p_{c_s}},\; B_s = \frac{f(c_s,\widehat{\mathcal{C}})}{p_{c_s}}. 
    \end{align}
\end{description}

\paragraph{Disjoint Block Sampling Estimators}

\begin{description}
    \item[$\widehat{P}_{\text{block}}$]{The estimator and its variance estimate $\widehat{V}(\widehat{P}_{\text{block}})$ are given by \eqref{eq:bias_adjustment} and \eqref{eq:estimated_variance}, where we substitute in}
    \begin{align}\label{eq:P_block}
        T = |\mathcal{B}|,\; A_s = \frac{\lvert \mathcal{P}_{b_s} \rvert + \frac{1}{2} \lvert \mathcal{P}_{b_s}^{-} \rvert}{p_{b_s}},\;
        B_s = \frac{\lvert \mathcal{T}_{b_s} \cap \mathcal{P}_{b_s} \rvert}{p_{b_s}}.
    \end{align}
    \item[$\widehat{R}_{\text{block}}$]{The estimator and its variance estimate $\widehat{V}(\widehat{R}_{\text{block}})$ are given by \eqref{eq:bias_adjustment} and \eqref{eq:estimated_variance}, where we substitute in}
    \begin{align}
        T = |\mathcal{B}|,\; A_s = \frac{\lvert \mathcal{T}_{b_s} \rvert}{p_{b_s}},\; B_s = 
        \frac{\lvert \mathcal{T}_{b_s} \cap \mathcal{P}_{b_s} \rvert}{p_{b_s}}.
    \end{align}
\end{description}

\subsection{Proofs}\label{appendix:proofs}

\begin{proof}[Proof of lemma \ref{lemma:record_sampling_representation}]
By breaking down $\mathcal{P}$ and $\mathcal{T}$ over predicted clusters, we find
\begin{equation}
    P = \sum_{c\in\mathcal{C}} \sum_{\hat c \in \widehat{\mathcal{C}}} {\lvert c \cap \hat c \rvert \choose 2} \Big/ \sum_{\hat c \in \widehat{\mathcal{C}}} {\lvert \hat c \rvert \choose 2}.
\end{equation}
Now writing $\sum_{c \in \mathcal{C}} \sum_{\hat c \in \widehat{\mathcal{C}}}{\lvert c \cap \hat c \rvert \choose 2} = \sum_{i=1}^{N} \frac{1}{\lvert c(i) \rvert} \sum_{\hat c \in \widehat{\mathcal{C}}} {\lvert c(i) \cap \hat c \rvert \choose 2}$ and substituting $g(c(i), \widehat{\mathcal{C}})$, we obtain
\begin{equation}
    P = \sum_{i=1}^N p_i \frac{g(c(i)), \widehat{\mathcal{C}})}{p_i \lvert c(i) \rvert} = \mathbb{E}\left[ \frac{g(c(i)), \widehat{\mathcal{C}}}{p_i \lvert c(i) \rvert} \right].
\end{equation}
For recall, write 
\begin{equation}\label{eq:recall_cluster_form}
    R = \sum_{c\in\mathcal{C}} \sum_{\hat c \in \widehat{\mathcal{C}}} {\lvert c \cap \hat c \rvert \choose 2} \Big/ \sum_{ c \in {\mathcal{C}}} {\lvert c \rvert \choose 2}.
\end{equation}
Through a similar argument as above, we may express the nominator as 
\begin{equation}\label{eq:nominator}
    \sum_{c\in\mathcal{C}} \sum_{\hat c \in \widehat{\mathcal{C}}} {\lvert c \cap \hat c \rvert \choose 2} = \mathbb{E}\left[ f(c(i),\, \widehat{\mathcal{C}})  \big/ (\lvert c(i) \rvert p_i) \right].
\end{equation}
For the denominator, we have
\begin{equation}\label{eq:denominator}
    \sum_{c \in \mathcal{C}} {\lvert c \rvert \choose 2} = \sum_{i=1}^N \frac{1}{\lvert c(i) \rvert}  {\lvert c(i) \rvert \choose 2} = \mathbb{E}[ (\lvert c(i) \rvert - 1)/(2 p_i)].
\end{equation}
Combining \eqref{eq:nominator} and \eqref{eq:denominator} yields the result. 
\end{proof}

\begin{proof}[Proof of lemma \ref{lemma:cluster_sampling_representation}]
Let $\pi > 0$ be such that $\sum_{c \in \mathcal{C}} \pi p_c= 1$. Now write
\begin{equation}
    P = \sum_{c \in \mathcal{C}} g(c, \widehat{\mathcal{C}}) = \lvert \mathcal{C} \rvert\, \sum _{c \in \mathcal{C}} \pi p_c g(c, \widehat{\mathcal{C}}) / (\pi p_c \lvert \mathcal{C} \rvert)  =  \lvert \mathcal{C}\rvert\, \mathbb{E}\left[ g(c, \widehat{\mathcal{C}})/(\pi p_c \lvert \mathcal{C} \rvert) \right]
\end{equation}
and 
\begin{equation}
    \lvert \mathcal{C} \rvert = \frac{N}{\frac{1}{\lvert \mathcal{C} \rvert} \sum_{c \in \mathcal{C}} \lvert c \rvert} = \frac{N}{\mathbb{E}[\lvert c \rvert / (\pi p_c \lvert \mathcal{C} \rvert)]}.
\end{equation}
Simplifying $\pi \lvert \mathcal{C} \rvert$ from the nominator and denominator then yields the expression for precision.

The expression for recall follows in a straightforward way from equation \eqref{eq:recall_cluster_form}.
\end{proof}

\begin{proof}[Proof of lemma \ref{lemma:block_sampling_representation}]
Since the blocking procedure is assumed to have no error (for every $ c \in \mathcal{C}$, there exists $b \in \mathcal{B}$ with $c \subset b$), we can break down $\mathcal{T}$ as the disjoint union of the $\mathcal{T}_b$'s over $b \in \mathcal{B}$. It follows that $\lvert T \rvert = \sum_{b \in \mathcal{B}} \lvert \mathcal{T}_b \rvert$ and  $\lvert \mathcal{T} \cap \mathcal{P} \rvert = \sum_{b \in \mathcal{B}} \lvert \mathcal{T}_b \cap \mathcal{P}_b \rvert$. The expression for recall in in \eqref{eq:lemma_3} follows directly. For precision, we can express $\lvert \mathcal{P} \rvert$ as the number of links within blocks plus the number of links across blocks. Since the number of links across blocks are counted twice when considering for each block, we obtain $\lvert \mathcal{P} \rvert = \sum_{b \in \mathcal{B}} \left( \lvert \mathcal{P}_b \rvert + \tfrac{1}{2} \lvert \mathcal{P}_b^{-} \rvert \right)$. 
\end{proof}

\end{document}

### 2022-06-27 setup.py
release 0.0.1

@@ -4,7 +4,7 @@ from setuptools import setup, find_packages
 if __name__ == "__main__":
     setup(
         name="pv_evaluation",
-        version="0.0.0",
+        version="0.0.1",
         author="Olivier Binette, Sarvo Madhavan",
         author_email="olivier.binette@gmail.com",
         description="Tools to evaluate disambiguation algorithms",

### 2022-06-27 pv_evaluation/__init__.py
release 0.0.1

@@ -1,0 +1,5 @@
+import pkg_resources
+
+__version__ = pkg_resources.require("stringcompare")[0].version
+
+__all__ = ["__version__"]

### 2022-06-27 paper/main.tex
Updates from Overleaf

@@
 
-The specific values for $A_s$, $B_s$, and $T$ in each of our representation is described in appendix X.
+The specific values for $A_s$, $B_s$, and $T$ in each of our representation is described in appendix \ref{sec:appendix}.
 
@@
 
-\section{Appendix}
+\section{Appendix}\label{sec:appendix}
 
@@
 
-This section describes specific values for $A_s$, $B_s$, and $T$ in \eqref{eq:bias_adjustment} in order to obtained nearly unbiased precision and recall estimators based on each of the representation in XX.
+This section describes specific values for $A_s$, $B_s$, and $T$ in \eqref{eq:bias_adjustment} in order to obtained nearly unbiased precision and recall estimators based on each of the representation in section \ref{sec:proposed_estimators}.
 We use the symbols $\widehat P$ and $\widehat R$, indexed by one of ``$\text{rec}$", ``$\text{clust}$", and ``$\text{block}$", in order to refer to precision and recall estimators corresponding to record, cluster, and block sampling representations.

### 2022-07-20 paper/main.tex

@@
 
+\usepackage{xcolor}
+\newcommand{\ob}[1]{{\color{purple}#1}}
+
 \newtheorem{theorem}{Theorem}
@@
 \author[1]{Youngsoo Baek}
-\author[2]{Aida York}
+\author[2]{Sokhna A York}
 \author[2]{Emma Hickerson}
@@
 This paper introduces a novel evaluation methodology for entity resolution algorithms.
-It is motivated by PatentsView.org, a publicly-available patent data analysis tool which disambiguates patent inventors based on an entity resolution algorithm.
-We provide a data collection methodology and performance estimators which account for sampling biases.
+It is motivated by PatentsView.org, a \ob{U.S.
+Patents and Trademarks Office patent data exploration tool} which disambiguates patent inventors using an entity resolution algorithm.
+We provide a data collection methodology and tailored performance estimators which account for sampling biases.
 Our approach is simple, practical and principled -- key characteristics which allow us to paint the first representative picture of PatentsView's disambiguation performance.
@@
 \section{Introduction}
-Entity resolution is the task of identifying records in a database which refer to the same entity.
+Entity resolution (also called record linkage, deduplication, or disambiguation) is the task of identifying records in a database which refer to the same entity.
 An entity may be a person, a company, an object or an event.
@@
 The result is a set of ambiguous mentions to inventors, where a single person's name may be spelled in different ways on two applications, and where two different inventors with the same name may be difficult to distinguish.
-Much research has ben done within the fields of economics, computer science and statistics to disambiguate inventor mentions \citep{trajtenberg2008identification, ferreira2012brief, ventura2013methods, Li2014, Ventura2015, kim2016random, yang2017mixture, morrison2017disambiguation, muller2017semantic, traylor2017learning, balsmeier2018machine,tam2019optimal, monath2019scalable, doherr2021disambiguation}.
+Much research has been done within the fields of economics, computer science and statistics to disambiguate inventor mentions \citep{trajtenberg2008identification, ferreira2012brief, ventura2013methods, Li2014, Ventura2015, kim2016random, yang2017mixture, morrison2017disambiguation, muller2017semantic, traylor2017learning, balsmeier2018machine,tam2019optimal, monath2019scalable, doherr2021disambiguation}.
 
@@
 The entity resolution evaluation problem is to extrapolate from observed performance on small samples to real performance in a database with millions of records.
-\cite{Wang2022} refers to this as bridging the ``reality-ideality gap" in entity matching, where high performance on benchmark datasets often does not translate in the real world.
+\cite{Wang2022} refers to this as bridging the ``reality-ideality gap" in entity resolution, where high performance on benchmark datasets often does not translate in the real world.
 Here, performance may be defined as any combination of commonly used evaluation metrics for entity resolution, such as precision and recall, cluster homogeneity and completeness, rand index, or generalized merge distance \citep{Maidasani2012}.
@@
 
-First, entity resolution problems scale non-linearly.
+First, entity resolution problems \ob{do not scale linearly}.
 While it may be easy to disambiguate a small dataset, the opportunity for errors grows \textit{quadratically} in the number of records.
@@
 Despite encouraging performance evaluation metrics on benchmark datasets, with nearly perfect precision and recall reported in the latest methodological report \citep{Monath2021}, the data science team at AIR observes lower real-world accuracy.
+\ob{This phenomenon is illustrated in example \ref{first_example} below.}
 
 A second problem is large class imbalance in entity resolution \citep{Marchant2017}.
-Among all pairs of records, only a small fraction (usually much less than a fraction of a percent) refer to the same entity.
+\ob{Viewing entity resolution as a classification problem, the task is to classify record pairs as being a match or non-match.
+However,} among all pairs of records, only a small fraction (usually much less than a fraction of a percent) refer to the same entity.
 The vast majority of record pairs are not a match.
-This makes it difficult to evaluate performance through random sampling.
+This makes it difficult to evaluate performance through random sampling of record pairs.
 
@@
 
-Our approach, detailed in sections \ref{sec:approach} and \ref{sec:proposed_estimators}, addresses these challenges by putting forward cluster-based expressions for performance metrics which reflect various sampling schemes.
+Our approach, detailed in sections \ref{sec:approach} and \ref{sec:proposed_estimators}, addresses these challenges by putting forward novel cluster-based expressions for performance metrics which reflect various sampling schemes.
 Each of these representations immediately suggests simple estimators which properly account for the above issues.
@@
 This is analogous to the way that many real-world benchmark data sets are obtained and used.
-For reference, it is known that the disambiguation algorithm has a precision of $52\%$ for the entire dataset.
+In this experiment, we known that the disambiguation algorithm has a precision of $52\%$ for the entire dataset.
 
@@
 Now, there are issues with the use of pairwise precision and recall in entity resolution applications, such as the large relative importance of large clusters.
-As such, other clustering metrics have been proposed, including cluster precision and recall, cluster homogeneity and completeness, and the generalized merge distance \citep{Michelson2009, Menestrina2010, Maidasani2012, Barnes2015}.
+As such, other clustering metrics have been proposed, including cluster precision and recall, cluster homogeneity and completeness, and generalized merge distances \citep{Michelson2009, Menestrina2010, Maidasani2012, Barnes2015}.
 Important practical issues regarding the use of aggregate metrics are discussed in \cite{Hand2018}.
+
+\ob{While our work focuses on estimating pairwise precision and recall, the general approach also applies to any cluster based performance evaluation metrics, such as those described in \cite{Michelson2009}.}
 
@@
 
+\ob{In contrast to the above, our approach to estimation is more practical than pairwise sampling and applies to any black-box disambiguation algorithms such as those used at PatentsView.}
+
 \subsubsection{Our Approach}\label{sec:approach}
@@
 Our approach to estimating performance metrics is based on the use of benchmark datasets which are already existing or which can be collected in a cost-effective way.
-This data contains entity clusters corresponding to sampling records and recovering all associated instances, to directly sampling clusters, or to sampling blocks.
-For each of these sampling processes, we propose estimators which correct for the issues discussed in section \ref{sec:challenges}, which are nearly unbiased, and which are easy to use in practice.
+These datasets contain entity clusters corresponding to sampling records and recovering all associated instances, to directly sampling clusters, or to sampling blocks.
+For each of these sampling processes, we propose estimators which correct for the issues discussed in section \ref{sec:challenges}, are nearly unbiased, and easy to use in practice.
 
@@
 
+\ob{Furthermore, our approach is novel.
+To our knowledge, we are the first to propose unbiased performance estimators based on cluster and block samples.
+Past work either ignored biases when computing precision and recall from benchmark datasets \citep{frisoli2018exploring, Monath2021, han2019disambiguating}, did not provide estimates for one of precision or recall \citep{mcveigh2019scaling}, or provided solutions that are tailored to very specific record linkage models \citep{Belin1995}.
+We provide the first general solution to entity resolution evaluation which does not rely on sampling record pairs and which applies to any disambiguation algorithm.}
+
 In short, the proposed approach is simple, principled, and practical.
@@
 The rest of the paper is organized as follows.
-In section \ref{sec:data_methods}, we introduce motivating benchmark datasets, we describe our data collection process for evaluation, we introduce the proposed estimators, and we summarize our simulation study used to validate the performance of our estimators.
-Section \ref{sec:results} then shows the results -- our performance estimates and results from the simulation study.
-Finally, section \ref{sec:discussion} summarizes the paper and discusses open research directions.
+In section \ref{sec:data_methods}, \ob{we describe: motivating benchmark datasets, our data collection process for evaluation, the proposed estimators, and our simulation study used to validate the performance of our estimators.} Section \ref{sec:results} then shows the results: our performance estimates and results from the simulation study.
+Finally, section \ref{sec:discussion} summarizes the paper and discusses future research directions.
 
@@
 
-In this section, we review motivating datasets used at PatentsView, we introduce our hand-disambiguation methodology, we describe our proposed performance metric estimators, and we describe our simulation framework used to compare estimators.
+In this section, \ob{we introduce: motivating datasets used at PatentsView, our hand-disambiguation methodology, our proposed performance metric estimators, and our simulation framework used to compare estimators.} \ob{Note that we focus on \textit{inventor} disambiguation throughout, rather than the related problems of assignee and location disambiguation.}
 
@@
 \paragraph{Israeli Inventors Benchmark}
-\cite{trajtenberg2008identification} disambiguated the US patents of Israeli inventors which were granted between 1963 and 1999.
+\cite{trajtenberg2008identification} disambiguated the U.S.
+patents of Israeli inventors which were granted between 1963 and 1999.
 A total of 6,023 Israeli inventors were identified for this time period with 15,310 associated patents.
@@
 
-Based on an original dataset from \cite{gu2008march}, \cite{Li2014} disambiguated the patent history (between 1975 and 2010) of 95 US inventors.
+Based on an original dataset from \cite{gu2008march}, \cite{Li2014} disambiguated the patent history (between 1975 and 2010) of 95 U.S. inventors.
 
@@
 
-In addition to the above benchmark datasets, we have carried out a data collection experiment which was motivated by the evaluation, using the proposed estimators discussed in section \ref{sec:proposed_estimators}, of the current PatentsView inventor disambiguation.
+In addition to the above benchmark datasets, \ob{we have carried out a data collection experiment.
+This was motivated by the evaluation of the current PatentsView inventor disambiguation using the estimators proposed in section \ref{sec:proposed_estimators}.}
 
@@
 This was done by sampling inventor mentions uniformly at random and recovering all patents for a given inventor.
-These inventor mentions were from US patents granted between 1976 and December 31, 2021.
+These inventor mentions were from U.S.
+patents granted between 1976 and December 31, 2021.
 
@@
 Note that our data collection methodology is biased towards PantentsView's current disambiguation.
-In cases where no errors were found, the current disambiguation was assumed to be correct.
+\ob{Indeed, we do not expect the staff to have found all errors or all missing inventor mentions from predicted clusters.
+The staff used their best judgment, supported by a thorough search, to resolve inventor mentions.} In cases where no errors were found, the current disambiguation was assumed to be correct.
 Performance estimates based on this data might therefore be slightly optimistic.
+\ob{This should be acknowledged when reporting performance estimates to PatentsView.org users.
+Otherwise, for the purpose of improving the current disambiguation algorithm, the slightly biased data is still appropriate to use.
+It represents the most visible errors in the current disambiguation rather than the totality of them.}
 
@@
     Lemma \ref{lemma:record_sampling_representation} and lemma \ref{lemma:cluster_sampling_representation} can be generalized to apply to any performance metric which can be expressed as a sum $\sum_{c \in \mathcal{C}} h(c, \widehat{\mathcal{C}})$, for some function $h$, or as a function of such sums.
-For instance, the use of the so-called \textit{cluster} precision and \textit{cluster} recall \citep{}, or of cluster homogeneity and completeness \citep{}, can be more appropriate in the presence of large clusters.
+For instance, the use of the so-called \textit{cluster} precision and \textit{cluster} recall \citep{Barnes2015}, or of cluster homogeneity and completeness \citep{Barnes2015}, can be more appropriate in the presence of large clusters.
 We leave these generalizations as extensions of our work.
@@
 For readability, we present here a generic formula for an approximately unbiased estimator of the ratio of means, and then specify the needed quantities for each representation below.
-The estimator applies a first order bias correction to the ratio of sample means, based on Taylor approximation.
+The estimator applies a first order bias correction to the ratio of sample means, based on a Taylor approximation.
 Approximate confidence intervals can be computed based on the variance estimator of the ratio of sample means by Taylor approximation, assuming the corrected estimator has small bias \citep{fuller2011sampling}.
@@
 \begin{align}\label{eq:bias_adjustment}
-    \widehat{E}=\frac{\bar{B}_n}{\bar{A}_n}\left\{1 + \frac{\theta_{n,T}}{n(n-1)}\frac{1}{\bar{A}_n}\sum_{s=1}^n A_s
-    \left(\frac{B_s}{\bar{B}_n} - \frac{A_s}{\bar{A}_n}\right)\right\},\;
-    \bar{A}_n = \frac{1}{n}\sum_{s=1}^{n}A_s,\;
-    \bar{B}_n = \frac{1}{n}\sum_{s=1}^{n}B_s
+    \widehat{E} = \frac{\bar{B}_n}{\bar{A}_n} \left\{ 1 + \frac{\theta_{n,T}}{n(n-1)} \sum_{s=1}^n \frac{A_s}{\bar{A}_n} \left(\frac{B_s}{\bar{B}_n} - \frac{A_s}{\bar{A}_n} \right) \right\}, \; \bar{A}_n = \frac{1}{n} \sum_{s=1}^{n} A_s, \; \bar{B}_n = \frac{1}{n} \sum_{s=1}^{n} B_s
 \end{align}
 We note that an additional symbol $\theta_{n,T}$ is introduced for possible finite population correction when relatively large number of elements are sampled without replacement (see below).
-Classical adjustment is to set $\theta_{n,T} = (1 - \frac{n-1}{T-1})$ \citep{Cochran1977}.
+Classical adjustment is set to $\theta_{n,T} = (1 - \frac{n-1}{T-1})$ \citep{Cochran1977}.
 For practical purposes when $T$ is large, often $\theta_{n,T}=1$ will suffice.
@@
 \begin{align} \label{eq:estimated_variance}
-    \widehat{V}(\widehat{E})=\left( \frac{\bar{B}_n}{\bar{A}_n} \right)^2\frac{\theta_{n,T}}{n(n-1)}
-    \sum_{s=1}^n \left( \frac{A_s^2}{\bar{A}_n^2} + \frac{B_s^2}{\bar{B}_n^2} - 2\frac{A_sB_s}{\bar{A}_n\bar{B}_n} \right).
+    \widehat{V}(\widehat{E}) = \left( \frac{\bar{B}_n}{\bar{A}_n} \right)^2 \frac{\theta_{n,T}}{n(n-1)} \sum_{s=1}^n \left( \frac{A_s}{\bar{A}_n} - \frac{B_s}{\bar{B}_n}\right)^2.
 \end{align}
-
 The specific values for $A_s$, $B_s$, and $T$ in each of our representation is described in appendix \ref{sec:appendix}.
@@
 The reason why \texttt{P\_cluster\_block} performs better than \texttt{P\_record} is due to the fact that \texttt{P\_record} has been derived in a generic way which applies to any performance metric which can be expressed in cluster form similar to \eqref{eq:lemma_1}.
-On the other hand, \texttt{P\_cluster\_block} relies on speific properties of precision.
+On the other hand, \texttt{P\_cluster\_block} relies on specific properties of precision.
 Among other things, this ensures that \texttt{P\_cluster\_block} is constrained to be between $0$ and $1$.
@@
     \centering
-    \caption{\centering Bias and root mean squared error of precision estimators for the simulation study described in section \ref{sec:simulation_study}.
+    \caption{\centering Bias and root mean squared error (rmse) of precision estimators for the simulation study described in section \ref{sec:simulation_study}.
 The \texttt{rate} variable represents the percentage misattribution rate.}
@@
 Table \ref{tab:results} shows estimated pairwise precision and recall from benchmark datasets and from our two hand-curated datasets.
-Note that each estimate is associated with a given population of inventor mentions which is a subset of granted US patents since 1976.
-We focused on US patents granted since 1976 as this is the main data product of patentsview.org.
+Note that each estimate is associated with a given population of inventor mentions which is a subset of granted U.S.
+patents since 1976.
+We focused on U.S.
+patents granted since 1976 as this is the main data product of PatentsView.org.
 
@@
 Since our two hand-curated datasets (see section \ref{sec:hand-disambiguation}) were obtained by sampling inventor clusters with probabilities proportional to cluster sizes, we used the \texttt{P\_cluster\_block} and \texttt{R\_record} estimators with corresponding probability weights.
-For the Israeli benchmark dataset, we assumed that a single block of inventor clusters were sampled alltogether and used the corresponding estimators defined through \eqref{eq:lemma_3} with a single block sample.
+For the Israeli benchmark dataset, we assumed that a single block of inventor clusters was sampled and used the corresponding estimators defined through \eqref{eq:lemma_3} with a single block sample.
 Note that no variance estimates can be given for single samples.
@@
     \midrule
-    Staff 1 & 86\% (5.6\%) & 94\% (2.1\%)  & 1976 -- Dec. 31, 2022 (US granted)\\
-    Staff 2 & 88\% (5.6\%) & 95\% (2.0\%) & 1976 -- Dec. 31, 2022 (US granted)\\
-    Israeli Benchmark & 79\% (NA) & 94\% (NA) & 1976 -- 1999 (US granted)\\
-    \cite{Li2014}'s Benchmark & 91\% (2.7\%) & 91\% (5.0\%) & 1976 -- 2010 (US granted)\\
+    Staff 1 & 86\% (5.6\%) & 94\% (2.1\%)  & 1976 -- Dec. 31, 2022 (U.S. granted)\\
+    Staff 2 & 88\% (5.6\%) & 95\% (2.0\%) & 1976 -- Dec. 31, 2022 (U.S. granted)\\
+    Israeli Benchmark & 79\% (NA) & 94\% (NA) & 1976 -- 1999 (U.S. granted)\\
+    \cite{Li2014}'s Benchmark & 91\% (2.7\%) & 91\% (5.0\%) & 1976 -- 2010 (U.S. granted)\\
     \bottomrule
@@
 
+\ob{One important topic for future work is the quantification of uncertainty associated with errors in the hand-disambiguation process.
+This is challenging problem given the lack of validation information available.
+Surveying inventors to validate the hand-disambiguation process would be one approach to explore for this.
+Sensitivity analyses involving potential errors in the hand-disambiguation process could also be informative.
+We refer the reader to \citep{bailey2017well} for a state-of-the-art hand-labeling study which evaluated human review accuracy.}
+
+\ob{Another important topic for future work is the development of estimators for additional performance metrics.
+As we have seen in the simulation study, the generically-derived estimators (e.g., from lemma \ref{lemma:cluster_sampling_representation}) do not perform as well as estimators derived using specific properties of pairwise precision and recall (lemma \ref{lemma:block_sampling_representation}).
+As such, care should be taken to obtain efficient estimators for every metric of interest.}
+
 \section*{Data and Code}
@@
 Youngsoo Baek provided bias adjustment and uncertainty quantification for ratio estimators.
-Aida York and Emma Hickerson carried out data collection by manually reviewing inventor clusters.
+Sokhna A York and Emma Hickerson carried out data collection by manually reviewing inventor clusters.
 Sarvo Madhavan was a technical advisor and contributed to code.
@@
 
-For this example, we considered the RLdata10000 dataset from \citep{}.
+For this example, we considered the RLdata10000 dataset from \citep{RecordLinkage}.
 This is a synthetic dataset containing 10,000 records with first name, last name, and date of birth attributes.
@@
 \begin{itemize}
-    \item records match on first name, last name, and birth year,
-    \item records match on first name, birth day, and birth year, or
-    \item records match on last name, birth day, and birth year.
+    \item records agree on first name, last name, and birth year,
+    \item records agree on first name, birth day, and birth year, or
+    \item records agree on last name, birth day, and birth year.
 \end{itemize}
@@
 \begin{enumerate}
-    \item First, 200 records were sampled and the ground truth clusters associated to them were recovered. This provided a ``benchmark" dataset which was used for evaluation.
+    \item First, 100 (resp. 200 and 400) records were sampled and the ground truth clusters associated to them were recovered. This provided a ``benchmark" dataset which was used for evaluation.
     \item Second, a trivial precision estimate was obtained by computing precision over the benchmark dataset.
@@
 \end{enumerate}
-The distributions of the these two precision estimates over the 5,000 repetitions are shown in figure \ref{fig:precision_problem}.
+The distributions of the these two precision estimates over the 5,000 repetitions and for sample of sizes 100, 200, and 400 are shown in figure \ref{fig:precision_problem}.
 Our proposed estimator is accurate and nearly unbiased, whereas the trivial precision estimates have almost nothing to do with actual algorithmic performance.

### 2022-07-21 pv_evaluation/estimators/cluster_precision.py
Cluster estimators (#25)
* Add cluster estimators

* update docs

* update changelog

@@ -1,0 +1,70 @@
+import numpy as np
+import pandas as pd
+
+from pv_evaluation.metrics.utils import validate_membership
+from pv_evaluation.estimators.ratio_estimators import ratio_estimator, std_dev
+
+
+def cluster_precision_arrays(prediction, reference, sampling_type, weights):
+    """Raw data for use with ratio estimator and standard deviation estimators."""
+    validate_membership(prediction)
+    validate_membership(reference)
+
+    inner = pd.concat({"prediction": prediction, "reference": reference}, axis=1, join="inner")
+    K = prediction.isin(inner.prediction)
+    outer = pd.concat({"prediction":prediction[K], "reference":reference}, join="outer", axis=1)
+    pred_count = outer.groupby("reference").nunique(dropna=False)["prediction"]
+
+    contained_within_sample = outer.groupby("prediction").nunique(dropna=False) == 1
+    number_contained_by_reference = inner.merge(contained_within_sample, on="prediction").query("reference_y == True").groupby("reference_x").nunique()
+    data = pd.concat({"pred_count":pred_count, "n_contained":number_contained_by_reference["prediction"]}, join="outer", axis=1)
+    data.n_contained = data.n_contained.fillna(0)
+
+    if sampling_type == "cluster_block":
+        if weights == "uniform":
+            N = data.n_contained
+            D = 0.5 * (N + data.pred_count)
+
+            return (N, D)
+        elif weights == "cluster_size":
+            (N, D) = cluster_precision_arrays(prediction, reference, sampling_type="cluster_block", weights="uniform")
+            cluster_sizes = inner.reference.value_counts(sort=False).values
+
+            return (N/cluster_sizes, D/cluster_sizes)
+    else:
+        raise Exception("Unrecognized 'sampling_type' option. Should be 'cluster_block'.")
+
+
+def cluster_precision_estimator(prediction, reference, sampling_type="cluster_block", weights="cluster_size"):
+    """Cluster precision estimates.
+
+    The only sampling mechanism considered is:
+
+        * **cluster_block** sampling: ground truth clusters are directly sampled and treated as block samples.
+
+    The following probability weights can be used:
+
+        * **uniform**: uniform probability weights.
+        * **cluster_size**: probability weights proportional to cluster size.
+
+    Args:
+        prediction (Series):  membership vector for predicted clusters, i.e. a pandas Series indexed by mention ids and with values representing predicted cluster assignment.
[…]

### 2022-07-21 paper/main.tex
Updates from Overleaf

@@
 
+\usepackage{subcaption}
+\DeclareCaptionFormat{custom}
+{%
+    \textbf{#1#2}\textit{#3}
+}
+\captionsetup{format=custom}
+
 \usepackage{xcolor}
@@
 \author[1,2]{Olivier Binette}
-\author[1]{Youngsoo Baek}
 \author[2]{Sokhna A York}
 \author[2]{Emma Hickerson}
+\author[1]{Youngsoo Baek}
 \author[2]{Sarvo Madhavan}
 \author[2]{Christina Jones}
-\affil[1]{Department of Statistical Science, Duke University}
+\affil[1]{Duke University}
 \affil[2]{American Institutes for Research}
@@
 This paper introduces a novel evaluation methodology for entity resolution algorithms.
-It is motivated by PatentsView.org, a \ob{U.S.
+It is motivated by PatentsView.org, a {U.S.
 Patents and Trademarks Office patent data exploration tool} which disambiguates patent inventors using an entity resolution algorithm.
@@
 
-First, entity resolution problems \ob{do not scale linearly}.
+First, entity resolution problems {do not scale linearly}.
 While it may be easy to disambiguate a small dataset, the opportunity for errors grows \textit{quadratically} in the number of records.
@@
 Despite encouraging performance evaluation metrics on benchmark datasets, with nearly perfect precision and recall reported in the latest methodological report \citep{Monath2021}, the data science team at AIR observes lower real-world accuracy.
-\ob{This phenomenon is illustrated in example \ref{first_example} below.}
+{This phenomenon is illustrated in example \ref{first_example} below.}
 
 A second problem is large class imbalance in entity resolution \citep{Marchant2017}.
-\ob{Viewing entity resolution as a classification problem, the task is to classify record pairs as being a match or non-match.
+{Viewing entity resolution as a classification problem, the task is to classify record pairs as being a match or non-match.
 However,} among all pairs of records, only a small fraction (usually much less than a fraction of a percent) refer to the same entity.
@@
 This is analogous to the way that many real-world benchmark data sets are obtained and used.
-In this experiment, we known that the disambiguation algorithm has a precision of $52\%$ for the entire dataset.
+In this experiment, we know that the disambiguation algorithm has a precision of $52\%$ for the entire dataset.
 
@@
 
-    In panel \textbf{A} of figure \ref{fig:precision_problem} below, we see the distribution of precision estimates versus the true precision of $52\%$ shown as a dotted vertical line.
+    In panel \textbf{A} of figure \ref{fig:precision_problem}, we see the distribution of precision estimates versus the true precision of $52\%$ shown as a dotted vertical line.
 Precision estimates are most of the time very close to $100\%$ and always higher than $80\%$, despite the truth being a precision of only $52\%$.
@@
 
-\ob{While our work focuses on estimating pairwise precision and recall, the general approach also applies to any cluster based performance evaluation metrics, such as those described in \cite{Michelson2009}.}
+{While our work focuses on estimating pairwise precision and recall, the general approach also applies to any cluster based performance evaluation metrics, such as those described in \cite{Michelson2009}.}
 
@@
 
-\ob{In contrast to the above, our approach to estimation is more practical than pairwise sampling and applies to any black-box disambiguation algorithms such as those used at PatentsView.}
+{In contrast to the above, our approach to estimation is more practical than pairwise sampling and applies to any black-box disambiguation algorithms such as those used at PatentsView.}
 
@@
 
-\ob{Furthermore, our approach is novel.
+{Furthermore, our approach is novel.
 To our knowledge, we are the first to propose unbiased performance estimators based on cluster and block samples.
@@
 The rest of the paper is organized as follows.
-In section \ref{sec:data_methods}, \ob{we describe: motivating benchmark datasets, our data collection process for evaluation, the proposed estimators, and our simulation study used to validate the performance of our estimators.} Section \ref{sec:results} then shows the results: our performance estimates and results from the simulation study.
+In section \ref{sec:data_methods}, {we describe: motivating benchmark datasets, our data collection process for evaluation, the proposed estimators, and our simulation study used to validate the performance of our estimators.} Section \ref{sec:results} then shows the results: our performance estimates and results from the simulation study.
 Finally, section \ref{sec:discussion} summarizes the paper and discusses future research directions.
@@
 
-In this section, \ob{we introduce: motivating datasets used at PatentsView, our hand-disambiguation methodology, our proposed performance metric estimators, and our simulation framework used to compare estimators.} \ob{Note that we focus on \textit{inventor} disambiguation throughout, rather than the related problems of assignee and location disambiguation.}
+In this section, {we introduce: motivating datasets used at PatentsView, our hand-disambiguation methodology, our proposed performance metric estimators, and our simulation framework used to compare estimators.} {Note that we focus on \textit{inventor} disambiguation throughout, rather than the related problems of assignee and location disambiguation.}
 
@@
 
-In addition to the above benchmark datasets, \ob{we have carried out a data collection experiment.
+In addition to the above benchmark datasets, {we have carried out a data collection experiment.
 This was motivated by the evaluation of the current PatentsView inventor disambiguation using the estimators proposed in section \ref{sec:proposed_estimators}.}
@@
 To do this, they were assisted by tools available on PatentsView.org.
-First, given a sampled inventor, the associated predicted cluster was reviewed and wrongly assigned patents were removed.
+First, given a sampled inventor, the associated predicted cluster was reviewed \ob{and, if any, wrongly} assigned patents were removed.
 Next, PatentsView's search tools were used to find additional mentions of similarly named inventors.
-These were reviewed and added to the predicted cluster if appropriate.
+These were reviewed \ob{and inventor mentions were added} to the predicted cluster if appropriate.
 The two AIR staff had an initial training session, followed by a test run on 10 inventors, before carrying out the rest of the data collection.
@@
 Note that our data collection methodology is biased towards PantentsView's current disambiguation.
-\ob{Indeed, we do not expect the staff to have found all errors or all missing inventor mentions from predicted clusters.
+{Indeed, we do not expect the staff to have found all errors or all missing inventor mentions from predicted clusters.
 The staff used their best judgment, supported by a thorough search, to resolve inventor mentions.} In cases where no errors were found, the current disambiguation was assumed to be correct.
 Performance estimates based on this data might therefore be slightly optimistic.
-\ob{This should be acknowledged when reporting performance estimates to PatentsView.org users.
-Otherwise, for the purpose of improving the current disambiguation algorithm, the slightly biased data is still appropriate to use.
+{This should be acknowledged when reporting performance estimates to PatentsView.org users.
+Otherwise, for the purpose of improving the current disambiguation \ob{algorithm, this data} is still appropriate to use.
 It represents the most visible errors in the current disambiguation rather than the totality of them.}
@@
 \end{align}
-The specific values for $A_s$, $B_s$, and $T$ in each of our representation is described in appendix \ref{sec:appendix}.
+The specific values for $A_s$, $B_s$, and $T$ in each of our representation are described in appendix \ref{sec:appendix}.
 
@@
 
-\begin{table}[!h]
+\begin{table}
     \label{tab:results}
@@
 The first is to provide PatentsView data users with an appropriate understanding of PatentsView data quality.
-Our performance estimates indicate that, despite an overall accurate disambiguation, there is room for improvement and the disambiguation algorithm estimates more links then there truly are.
-The second product is the set of tools needed for methodological research and model comparison.
+Our performance estimates indicate that, despite an overall accurate disambiguation, there is significant room for \ob{improvement.
+Notably, the current disambiguation over-estimates the number of matching inventor mention pairs.} The second product is the set of tools needed for methodological research and model comparison.
 Given our evaluation methodology, we can now reliably compare algorithms and decide with confidence on changes which will affect users.
 
-\ob{One important topic for future work is the quantification of uncertainty associated with errors in the hand-disambiguation process.
+{One important topic for future work is the quantification of uncertainty associated with errors in the hand-disambiguation process.
 This is challenging problem given the lack of validation information available.
@@
 
-\ob{Another important topic for future work is the development of estimators for additional performance metrics.
+{Another important topic for future work is the development of estimators for additional performance metrics.
 As we have seen in the simulation study, the generically-derived estimators (e.g., from lemma \ref{lemma:cluster_sampling_representation}) do not perform as well as estimators derived using specific properties of pairwise precision and recall (lemma \ref{lemma:block_sampling_representation}).
 As such, care should be taken to obtain efficient estimators for every metric of interest.}
+
+\ob{Finally, we note that the performance of estimators can degrade when dealing with heavy-tailed cluster size distributions.
+Bias of ratio estimators can be high in this case, especially when using small samples and when sampling clusters uniformly at random rather than with probability proportional to their size.
+Model-based estimators which exploit known properties of the cluster size distribution could be developed to improve estimation accuracy in this situation.}
 
@@
 
-Olivier Binette led the project and wrote the bulk of the manuscript.
+Olivier Binette led the project and wrote most of the manuscript.
+Sokhna A York and Emma Hickerson carried out data collection by manually reviewing inventor clusters.
 Youngsoo Baek provided bias adjustment and uncertainty quantification for ratio estimators.
-Sokhna A York and Emma Hickerson carried out data collection by manually reviewing inventor clusters.
 Sarvo Madhavan was a technical advisor and contributed to code.

### 2022-07-21 paper/main.tex
Update paper

@@
 For instance, the U.S.
-Patents and Trademarks Office (USPTO) makes available patent data dating back to 1790.
+Patents and Trademarks Office (USPTO) makes available patent data dating back to 1790 \ob{(numerized full-text data is available from 1976)}.
 However, there is no standard for uniquely identifying inventors on patent applications.
 The result is a set of ambiguous mentions to inventors, where a single person's name may be spelled in different ways on two applications, and where two different inventors with the same name may be difficult to distinguish.
-Much research has been done within the fields of economics, computer science and statistics to disambiguate inventor mentions \citep{trajtenberg2008identification, ferreira2012brief, ventura2013methods, Li2014, Ventura2015, kim2016random, yang2017mixture, morrison2017disambiguation, muller2017semantic, traylor2017learning, balsmeier2018machine,tam2019optimal, monath2019scalable, doherr2021disambiguation}.
+\ob{Inventor mobility further complicates the use of contextual information for disambiguation.} Much research has been done within the fields of economics, computer science and statistics to disambiguate inventor mentions \ob{in this situation} \citep{trajtenberg2008identification, ferreira2012brief, ventura2013methods, Li2014, Ventura2015, kim2016random, yang2017mixture, morrison2017disambiguation, muller2017semantic, traylor2017learning, balsmeier2018machine,tam2019optimal, monath2019scalable, doherr2021disambiguation}.
 
@@
 See section \ref{sec:proposed_estimators} for a formal definition} on this set of sampled clusters.
-This is analogous to the way that many real-world benchmark data sets are obtained and used.
+This is analogous to the way that many real-world benchmark data sets are obtained and typically used.
 In this experiment, we know that the disambiguation algorithm has a precision of $52\%$ for the entire dataset.
@@
 As such, precision and recall are equal if and only if the right number of matching pairs is predicted under $\widehat{\mathcal{C}}$.
+
+\begin{figure}[h]
+    \centering
+    \includegraphics{paper/clustering-example.pdf}
+    \caption{\ob{Example of ground truth clustering $\mathcal{C}$ (represented by boxes with a full border) and predicted clustering $\widehat{\mathcal{C}}$ (rounded boxes with a dotted border) of elements $\mathcal{D} = \{1,2,\dots, 8\}$.
+Here $\mathcal{T} = \{(1,2), (2,3), (1,3), (4,5), (6,7)\}$ and $\mathcal{P} = \{(1,4), (2,3), (6,7), (7,8), (6,8)\}$.
+As such, $P = R = 2/5$ in this example.}}
+    \label{fig:my_label}
+\end{figure}
 
@@
 \begin{table}
-    \label{tab:results}
     \centering
     \caption{\centering Estimated pairwise precision and recall (with estimated standard deviation) from our four benchmark datasets.}
+    \label{tab:results}
     \begin{tabular}{lccc}
@@
 \begin{enumerate}
-    \item First, 100 (resp. 200 and 400) records were sampled and the ground truth clusters associated to them were recovered. This provided a ``benchmark" dataset which was used for evaluation.
+    \item First, 200 records were sampled and the ground truth clusters associated to them were recovered. This provided a ``benchmark" dataset which was used for evaluation.
     \item Second, a trivial precision estimate was obtained by computing precision over the benchmark dataset.
@@
 \end{enumerate}
-The distributions of the these two precision estimates over the 5,000 repetitions and for sample of sizes 100, 200, and 400 are shown in figure \ref{fig:precision_problem}.
+The distributions of the these two precision estimates over the 5,000 repetitions are shown in figure \ref{fig:precision_problem}.
 Our proposed estimator is accurate and nearly unbiased, whereas the trivial precision estimates have almost nothing to do with actual algorithmic performance.

### 2022-07-27 analyses/2-simulation/src/2-make-predicted-clusters.py
change naming conventions

@@ -20,7 +20,7 @@ for rate in rates:
     prediction.to_csv(f"output/prediction_rate_{rate}.tsv", sep="\t")
     ground_truth.append(
         pairwise_precision_recall(
-            prediction.set_index("mention-id")["inventor_id"], reference.set_index("mention-id")["inventor_id"]
+            prediction.set_index("mention_id")["inventor_id"], reference.set_index("mention_id")["inventor_id"]
         )
     )
 

### 2022-07-27 scripts/patentsview-inventors-benchmark.py

@@ -18,11 +18,11 @@ data = pd.read_csv("data-raw/patentsview-inventor/gold-labels.txt", sep="\t", he
 
 mention_numbers = data[0].str.split("-").values
 
-data["mention-id"] = list(map(lambda x: "US" + x[0].lstrip("0") + "-" + x[1], mention_numbers))
-data["unique-id"] = data[1]
+data["mention_id"] = list(map(lambda x: "US" + x[0].lstrip("0") + "-" + x[1], mention_numbers))
+data["unique_id"] = data[1]
 
-rawinventor["mention-id"] = "US" + rawinventor.patent_id + "-" + rawinventor.sequence
-data = data.merge(rawinventor[["mention-id", "name_first", "name_last"]], on="mention-id", how="left")
+rawinventor["mention_id"] = "US" + rawinventor.patent_id + "-" + rawinventor.sequence
+data = data.merge(rawinventor[["mention_id", "name_first", "name_last"]], on="mention_id", how="left")
 
-cols = ["mention-id", "unique-id", "name_first", "name_last"]
+cols = ["mention_id", "unique_id", "name_first", "name_last"]
 data[cols].to_csv("pv_evaluation/data/inventor/patentsview-inventors-benchmark.csv", index=False)

### 2022-07-27 analyses/2-simulation/src/1-get-disambiguation.py
change naming conventions (#30)

@@ -12,5 +12,5 @@ if not os.path.isfile("output/rawinventor.tsv"):
     os.remove("rawinventor.tsv.zip")
 
 rawinventor = pd.read_csv("rawinventor.tsv", sep="\t")
-rawinventor["mention-id"] = "US" + rawinventor.patent_id.astype(str) + "-" + rawinventor.sequence.astype(str)
-rawinventor[["mention-id", "inventor_id"]].to_csv("output/disambiguation.tsv", sep="\t", index=False)
+rawinventor["mention_id"] = "US" + rawinventor.patent_id.astype(str) + "-" + rawinventor.sequence.astype(str)
+rawinventor[["mention_id", "inventor_id"]].to_csv("output/disambiguation.tsv", sep="\t", index=False)

### 2022-07-27 analyses/2-simulation/src/3-make-sim-records-precision.py

@@ -12,10 +12,10 @@ from pv_evaluation.estimators import pairwise_precision_estimator
 
 rates = [x.named["rate"] for x in findall("prediction_rate_{rate}.tsv", "".join(os.listdir("output/")))]
 predictions = {
-    rate: pd.read_csv(f"output/prediction_rate_{rate}.tsv", sep="\t").set_index("mention-id")["inventor_id"] for rate in rates
+    rate: pd.read_csv(f"output/prediction_rate_{rate}.tsv", sep="\t").set_index("mention_id")["inventor_id"] for rate in rates
 }
 
-reference = pd.read_csv("output/disambiguation.tsv", sep="\t").set_index("mention-id")["inventor_id"]
+reference = pd.read_csv("output/disambiguation.tsv", sep="\t").set_index("mention_id")["inventor_id"]
 
 estimators = {
     "P_naive": lambda ref, benchmark: pairwise_precision(ref, benchmark),

### 2022-07-27 analyses/2-simulation/src/5-make-sim-records-recall.py

@@ -12,10 +12,10 @@ from pv_evaluation.estimators import pairwise_recall_estimator
 
 rates = [x.named["rate"] for x in findall("prediction_rate_{rate}.tsv", "".join(os.listdir("output/")))]
 predictions = {
-    rate: pd.read_csv(f"output/prediction_rate_{rate}.tsv", sep="\t").set_index("mention-id")["inventor_id"] for rate in rates
+    rate: pd.read_csv(f"output/prediction_rate_{rate}.tsv", sep="\t").set_index("mention_id")["inventor_id"] for rate in rates
 }
 
-reference = pd.read_csv("output/disambiguation.tsv", sep="\t").set_index("mention-id")["inventor_id"]
+reference = pd.read_csv("output/disambiguation.tsv", sep="\t").set_index("mention_id")["inventor_id"]
 
 estimators = {
     "R_naive": lambda ref, benchmark: pairwise_recall(ref, benchmark),

### 2022-07-27 scripts/als-inventors.py

@@ -15,11 +15,11 @@ if not os.path.isfile("rawinventor.tsv"):
 rawinventor = pd.read_csv("rawinventor.tsv", sep="\t", dtype=str)
 
 data = pd.read_csv("data-raw/ALS-dataset/als-inventors.csv", dtype=str)
-data.rename(columns={"inventor-id":"unique-id"}, inplace=True)
-data = data[~data["mention-id"].duplicated(keep='first')]
+data.rename(columns={"inventor-id":"unique_id", "mention-id":"mention_id"}, inplace=True)
+data = data[~data["mention_id"].duplicated(keep='first')]
 
-rawinventor["mention-id"] = "US" + rawinventor.patent_id + "-" + rawinventor.sequence
-data = data.merge(rawinventor[["mention-id", "name_first", "name_last"]], on="mention-id", how="left")
+rawinventor["mention_id"] = "US" + rawinventor.patent_id + "-" + rawinventor.sequence
+data = data.merge(rawinventor[["mention_id", "name_first", "name_last"]], on="mention_id", how="left")
 
-cols = ["mention-id", "unique-id", "name_first", "name_last"]
+cols = ["mention_id", "unique_id", "name_first", "name_last"]
 data[cols].to_csv("pv_evaluation/data/inventor/als-inventors.csv", index=False)

### 2022-07-27 scripts/lai-2011-benchmark.py

@@ -16,11 +16,11 @@ rawinventor = pd.read_csv("rawinventor.tsv", sep="\t", dtype=str)
 
 lai_benchmark = pd.read_csv("data-raw/Lai-2011-data/benchmark_with_sequence.tsv", sep="\t", dtype=str, header=1)
 
-lai_benchmark["mention-id"] = "US" + lai_benchmark.Patent + "-" + lai_benchmark.Sequence
-lai_benchmark["unique-id"] = lai_benchmark.UniqueID
+lai_benchmark["mention_id"] = "US" + lai_benchmark.Patent + "-" + lai_benchmark.Sequence
+lai_benchmark["unique_id"] = lai_benchmark.UniqueID
 
-rawinventor["mention-id"] = "US" + rawinventor.patent_id + "-" + rawinventor.sequence
-lai_benchmark = lai_benchmark.merge(rawinventor[["mention-id", "name_first", "name_last"]], on="mention-id", how="left")
+rawinventor["mention_id"] = "US" + rawinventor.patent_id + "-" + rawinventor.sequence
+lai_benchmark = lai_benchmark.merge(rawinventor[["mention_id", "name_first", "name_last"]], on="mention_id", how="left")
 
-cols = ["mention-id", "unique-id", "name_first", "name_last"]
+cols = ["mention_id", "unique_id", "name_first", "name_last"]
 lai_benchmark[cols].to_csv("pv_evaluation/data/inventor/lai-2011-benchmark.csv", index=False)

### 2022-07-27 pv_evaluation/benchmark/data.py
change naming conventions (#30)

@@ -5,36 +5,36 @@ INVENTOR_DATA_MODULE = "pv_evaluation.data.inventor"
 
 
 def load_full_benchmark(module, filename):
-    """Load benchmark DataFrame from csv file with columns "unique-id", "mention-id", "name_first", and "name_last".
+    """Load benchmark DataFrame from csv file with columns "unique_id", "mention_id", "name_first", and "name_last".
 
     Args:
         module (str): module where file is located.
         filename (str): csv filename.
 
     Returns:
-        DataFrame: pandas Dataframe with columns "unique-id", "mention-id", "name_first", and "name_last".
+        DataFrame: pandas Dataframe with columns "unique_id", "mention_id", "name_first", and "name_last".
     """
     with resources.open_text(module, filename) as f:
         data = pd.read_csv(f)
 
-    cols = ["unique-id", "mention-id", "name_first", "name_last"]
+    cols = ["unique_id", "mention_id", "name_first", "name_last"]
     return data[cols]
 
 def load_unique_id_series(module, filename):
-    """Load disambiguation series from csv file with columns "unique-id" and "mention-id".
+    """Load disambiguation series from csv file with columns "unique_id" and "mention_id".
 
     Args:
         module (str): module where file is located.
         filename (str): csv filename.
 
     Returns:
-        Series: pandas Series named "unique-id" and with "mention-id" as an index.
+        Series: pandas Series named "unique_id" and with "mention_id" as an index.
     """
     with resources.open_text(module, filename) as f:
         data = pd.read_csv(f)
 
-    data.set_index("mention-id", inplace=True)
-    return data["unique-id"]
+    data.set_index("mention_id", inplace=True)
+    return data["unique_id"]
 
 
 def load_lai_2011_inventors_benchmark():

### 2022-07-27 pv_evaluation/benchmark/report.py

@@ -44,7 +44,7 @@ def inventor_benchmark_table(disambiguations, metrics=None, benchmarks=None):
     """Compute performance evaluation metrics on benchmark datasets.
 
     Args:
-        disambiguations (dict): dictionary of disambiguation results (disambiguation results are pandas Series with "mention-id" index and cluster assignment values).
+        disambiguations (dict): dictionary of disambiguation results (disambiguation results are pandas Series with "mention_id" index and cluster assignment values).
         metrics (dict, optional): dictionary of metrics (from the metrics submodule) to compute. Defaults to `DEFAULT_METRICS`.
         benchmarks (dict, optional): benchmark datasets loading functions to use from the benchmark submodule. Defaults to `DEFAULT_BENCHMARK`.
 
@@ -87,7 +87,7 @@ def inventor_benchmark_plot(disambiguations, metrics=None, benchmarks=None, face
     """Bar plot of performance evaluation metrics on benchmark datasets.
 
     Args:
-        disambiguations (dict): dictionary of disambiguation results (disambiguation results are pandas Series with "mention-id" index and cluster assignment values).
+        disambiguations (dict): dictionary of disambiguation results (disambiguation results are pandas Series with "mention_id" index and cluster assignment values).
         metrics (dict, optional): dictionary of metrics (from the metrics submodule) to compute. Defaults to `DEFAULT_METRICS`.
         benchmarks (dict, optional): benchmark datasets loading functions (from the benchmark submodule) to use. Defaults to `DEFAULT_BENCHMARK`.
 
@@ -130,9 +130,9 @@ def inspect_clusters_to_split(disambiguation, benchmark, join_with=None):
     """Get table of cluster assignment errors on the given benchmark.
 
     Args:
-        disambiguation (Series): disambiguation result Series (disambiguation results are pandas Series with "mention-id" index and cluster assignment values).
+        disambiguation (Series): disambiguation result Series (disambiguation results are pandas Series with "mention_id" index and cluster assignment values).
         benchmark (Series): reference disambiguation Series.
-        join_with (DataFrame, optional): DataFrame to join based on "mention-id". Defaults to None.
+        join_with (DataFrame, optional): DataFrame to join based on "mention_id". Defaults to None.
 
     Returns:
         DataFrame: DataFrame containing erroneous cluster assignments according to the given benchmark.
@@ -156,9 +156,9 @@ def inspect_clusters_to_merge(disambiguation, benchmark, join_with=None):
[…]

### 2022-07-27 pv_evaluation/templates/render.py

@@ -11,7 +11,7 @@ def render_inventor_disambiguation_report(outdir, summary_table_files, cache=Tru
 
     Args:
         outdir (str): directory where to output html files.
-        summary_table_files (list): list of paths to disambiguation table files (tables with the five columns "mention-id", "inventor_id", "patent_id", "name_first", and "name_last").
+        summary_table_files (list): list of paths to disambiguation table files (tables with the five columns "mention_id", "inventor_id", "patent_id", "name_first", and "name_last").
             File format can be one of tsv, csv, or parquet.
         cache (bool, optional): whether or not to cache jupyter chunk execution between runs. Defaults to True.
 

### 2022-07-27 scripts/harvard-inventors-benchmark.py

@@ -16,11 +16,11 @@ rawinventor = pd.read_csv("rawinventor.tsv", sep="\t", dtype=str)
 
 data = pd.read_csv("data-raw/harvard-inventors-benchmark/harvard-benchmark-with-reviewed-sequence-number.csv", dtype=str)
 
-data["mention-id"] = "US" + data.patent_number + "-" + data.sequence
-data["unique-id"] = data["inventor_id"]
+data["mention_id"] = "US" + data.patent_number + "-" + data.sequence
+data["unique_id"] = data["inventor_id"]
 
-rawinventor["mention-id"] = "US" + rawinventor.patent_id + "-" + rawinventor.sequence
-data = data.merge(rawinventor[["mention-id", "name_first", "name_last"]], on="mention-id", how="left")
+rawinventor["mention_id"] = "US" + rawinventor.patent_id + "-" + rawinventor.sequence
+data = data.merge(rawinventor[["mention_id", "name_first", "name_last"]], on="mention_id", how="left")
 
-cols = ["mention-id", "unique-id", "name_first", "name_last"]
+cols = ["mention_id", "unique_id", "name_first", "name_last"]
 data[cols].to_csv("pv_evaluation/data/inventor/harvard-inventors-benchmark.csv", index=False)

### 2022-07-27 tests/resources/make.py

@@ -24,10 +24,10 @@ df.sort_values(by="name_last", inplace=True)
 data = df.head(50000)
 
 # Define index and relevant fields
-data["mention-id"] = "US" + data.patent_id.str.cat(data.sequence.astype(str), sep="-")
+data["mention_id"] = "US" + data.patent_id.str.cat(data.sequence.astype(str), sep="-")
 data["name_full"] = data.name_first.str.cat(data.name_last, sep="_")
 
 # Save as raw_inventor_sample.tsv
-data[["mention-id", "name_full", "inventor_id", "patent_id", "name_first", "name_last"]].to_csv(
+data[["mention_id", "name_full", "inventor_id", "patent_id", "name_first", "name_last"]].to_csv(
     "raw_inventor_sample.tsv", sep="\t", index=False
 )

### 2022-07-28 docs/source/conf.py
update docs

@@ -40,7 +40,7 @@ extensions = [
 
 nb_execution_mode = "off"
 
-source_suffix = [".rst", ".md", ".ipynb", ".html"]
+source_suffix = [".rst", ".md", ".ipynb"]
 
 # Add any paths that contain templates here, relative to this directory.
 templates_path = ["_templates"]

### 2022-07-28 pv_evaluation/benchmark/__init__.py
remove harvard dataset

@@ -7,7 +7,6 @@ from pv_evaluation.benchmark.data import (
     load_lai_2011_inventors_benchmark,
     load_als_inventors_benchmark,
     load_ens_inventors_benchmark,
-    load_harvard_inventors_benchmark,
 )
 
 from pv_evaluation.benchmark.report import (

### 2022-07-28 scripts/harvard-inventors-benchmark.py

@@ -1,26 +1,0 @@
-try:
-    import pandas as pd
-    import wget
-    import zipfile
-    import os
-except:
-    raise Exception("Unable to import required dependencies.")
-
-if not os.path.isfile("rawinventor.tsv"):
-    wget.download("https://s3.amazonaws.com/data.patentsview.org/download/rawinventor.tsv.zip")
-    with zipfile.ZipFile("rawinventor.tsv.zip", 'r') as zip_ref:
-        zip_ref.extractall(".")
-    os.remove("rawinventor.tsv.zip")
-
-rawinventor = pd.read_csv("rawinventor.tsv", sep="\t", dtype=str)
-
-data = pd.read_csv("data-raw/harvard-inventors-benchmark/harvard-benchmark-with-reviewed-sequence-number.csv", dtype=str)
-
-data["mention_id"] = "US" + data.patent_number + "-" + data.sequence
-data["unique_id"] = data["inventor_id"]
-
-rawinventor["mention_id"] = "US" + rawinventor.patent_id + "-" + rawinventor.sequence
-data = data.merge(rawinventor[["mention_id", "name_first", "name_last"]], on="mention_id", how="left")
-
-cols = ["mention_id", "unique_id", "name_first", "name_last"]
-data[cols].to_csv("pv_evaluation/data/inventor/harvard-inventors-benchmark.csv", index=False)

### 2022-08-02 paper/main.tex

@@
 
-\renewcommand{\baselinestretch}{2}
+\renewcommand{\baselinestretch}{1.2}
 
@@
 \usepackage{amssymb, amsthm}
-\usepackage{listings}
 \usepackage{booktabs}
@@
 \usepackage{lineno}
-\linenumbers
+\usepackage{url}
+%\linenumbers
+
+\usepackage{listings}
+\usepackage{xcolor}
+
+\definecolor{codegreen}{rgb}{0,0.6,0}
+\definecolor{codegray}{rgb}{0.5,0.5,0.5}
+\definecolor{codepurple}{rgb}{0.58,0,0.82}
+\definecolor{backcolour}{rgb}{0.95,0.95,0.92}
+
+\lstdefinestyle{mystyle}{
+    commentstyle=\color{codegreen},
+    keywordstyle=\bf,
+    stringstyle=\color{magenta},
+    basicstyle=\ttfamily,
+    breakatwhitespace=false,         
+    breaklines=true,                 
+    captionpos=b,                    
+    keepspaces=true,                 
+    numbers=none,                    
+    numbersep=5pt,                  
+    showspaces=false,                
+    showstringspaces=false,
+    showtabs=false,                  
+    tabsize=2
+}
+
+\lstset{style=mystyle}
 
@@
 \usepackage{xcolor}
-\newcommand{\ob}[1]{{\color{purple}#1}}
+\newcommand{\ob}[1]{{#1}}
 
@@
 It is motivated by PatentsView.org, a {U.S.
-Patents and Trademarks Office patent data exploration tool} which disambiguates patent inventors using an entity resolution algorithm.
-We provide a data collection methodology and tailored performance estimators which account for sampling biases.
-Our approach is simple, practical and principled -- key characteristics which allow us to paint the first representative picture of PatentsView's disambiguation performance.
-This is used to inform PatentsView's users of the reliability of the data and to allow the comparison of competing disambiguation algorithms.
+Patents and Trademarks Office patent data exploration tool} that disambiguates patent inventors using an entity resolution algorithm.
+We provide a data collection methodology and tailored performance estimators that account for sampling biases.
+Our approach is simple, practical and principled -- key characteristics that allow us to paint the first representative picture of PatentsView's disambiguation performance.
+This approach is used to inform PatentsView's users of the reliability of the data and to allow the comparison of competing disambiguation algorithms.
 \end{abstract}
@@
 \section{Introduction}
-Entity resolution (also called record linkage, deduplication, or disambiguation) is the task of identifying records in a database which refer to the same entity.
+Entity resolution (also called record linkage, deduplication, or disambiguation) is the task of identifying records in a database that refer to the same entity.
 An entity may be a person, a company, an object or an event.
@@
 For instance, the U.S.
-Patents and Trademarks Office (USPTO) makes available patent data dating back to 1790 \ob{(numerized full-text data is available from 1976)}.
+Patents and Trademarks Office (USPTO) makes available patent data dating back to 1790 \ob{(digitized full-text data is available from 1976)}.
 However, there is no standard for uniquely identifying inventors on patent applications.
-The result is a set of ambiguous mentions to inventors, where a single person's name may be spelled in different ways on two applications, and where two different inventors with the same name may be difficult to distinguish.
+The result is a set of ambiguous mentions of inventors, where a single person's name may be spelled in different ways on two applications and where two different inventors with the same name may be difficult to distinguish.
 \ob{Inventor mobility further complicates the use of contextual information for disambiguation.} Much research has been done within the fields of economics, computer science and statistics to disambiguate inventor mentions \ob{in this situation} \citep{trajtenberg2008identification, ferreira2012brief, ventura2013methods, Li2014, Ventura2015, kim2016random, yang2017mixture, morrison2017disambiguation, muller2017semantic, traylor2017learning, balsmeier2018machine,tam2019optimal, monath2019scalable, doherr2021disambiguation}.
 
-The Office of the Chief Economist at the USPTO and the American Institutes for Research (AIR) currently maintain \textbf{PatentsView.org}, a patents knowledge discovery service which provides disambiguated patents data based on statistical entity resolution \citep{toole2021patentsview}.
+The Office of the Chief Economist at the USPTO and the American Institutes for Research (AIR) currently maintain \textbf{PatentsView.org}, a patents knowledge discovery service that provides disambiguated patents data based on statistical entity resolution \citep{toole2021patentsview}.
 Our paper is motivated by this disambiguation service.
@@
 
-The entity resolution evaluation problem is to extrapolate from observed performance on small samples to real performance in a database with millions of records.
-\cite{Wang2022} refers to this as bridging the ``reality-ideality gap" in entity resolution, where high performance on benchmark datasets often does not translate in the real world.
+The entity resolution evaluation problem is to extrapolate from observed performance in small samples to real performance in a database with millions of records.
+\cite{Wang2022} refer to this as bridging the reality-ideality gap in entity resolution, where high performance on benchmark datasets often does not translate into the real world.
 Here, performance may be defined as any combination of commonly used evaluation metrics for entity resolution, such as precision and recall, cluster homogeneity and completeness, rand index, or generalized merge distance \citep{Maidasani2012}.
 These metrics can be computed on benchmark datasets for which we have a ground truth disambiguation.
-However, the key evaluation problem is to obtain estimates which are representative of performance on the full data for which no ground truth disambiguation is available.
+However, the key evaluation problem is to obtain estimates that are representative of performance on the full data, for which no ground truth disambiguation is available.
 This is challenging for the following reasons.
@@
 While it may be easy to disambiguate a small dataset, the opportunity for errors grows \textit{quadratically} in the number of records.
-As such, we may observe good performance of an algorithm on a small benchmark dataset, while the true performance of on the entire data may be something else entirely.\footnote{This particular effect of dataset size in entity resolution is explored in \cite{Draisbach2013} in the context of choosing similarity thresholds.} This is a problem that PatentsView.org currently faces.
+As such, we may observe good performance of an algorithm on a small benchmark dataset, while the true performance on the entire dataset may be something else entirely.\footnote{This particular effect of dataset size in entity resolution is explored in \cite{Draisbach2013} in the context of choosing similarity thresholds.} This is a problem that PatentsView.org currently faces.
 Despite encouraging performance evaluation metrics on benchmark datasets, with nearly perfect precision and recall reported in the latest methodological report \citep{Monath2021}, the data science team at AIR observes lower real-world accuracy.
@@
 
-Our approach, detailed in sections \ref{sec:approach} and \ref{sec:proposed_estimators}, addresses these challenges by putting forward novel cluster-based expressions for performance metrics which reflect various sampling schemes.
-Each of these representations immediately suggests simple estimators which properly account for the above issues.
+Our approach, detailed in sections \ref{sec:approach} and \ref{sec:proposed_estimators}, addresses these challenges by putting forward novel cluster-based expressions for performance metrics that reflect various sampling schemes.
+Each of these representations immediately suggests simple estimators that properly account for the above issues.
 
 \begin{example}[Bias of precision computed on benchmark datasets]\label{first_example}
-    To exemplify the problem with the trivial use of performance evaluation metrics on benchmark datasets, we have carried out a simple experiment which is described in detail in appendix \ref{appendix:example}.
-In short, we considered evaluating a disambiguation algorithm by sampling ground truth clusters and computing pairwise precision\footnote{Pairwise precision is the probability that a pair of record predicted to be a match is indeed a match.
+    To exemplify the problem with the trivial use of performance evaluation metrics on benchmark datasets, we carried out a simple experiment that is described in detail in appendix \ref{appendix:example}.
+In short, we evaluated a disambiguation algorithm by sampling ground truth clusters and computing pairwise precision\footnote{Pairwise precision is the probability that a pair of record predicted to be a match is indeed a match.
 See section \ref{sec:proposed_estimators} for a formal definition} on this set of sampled clusters.
-This is analogous to the way that many real-world benchmark data sets are obtained and typically used.
+This is analogous to the way that many real-world benchmark datasets are obtained and typically used.
 In this experiment, we know that the disambiguation algorithm has a precision of $52\%$ for the entire dataset.
@@
 Panel \textbf{B} shows our proposed precision estimates which accounts for the sampling mechanism.
-Sample bias and root mean squared error (rmse) are reported on each figure.}
+Sample bias and root mean squared error (rmse) are reported in each figure.}
         \label{fig:precision_problem}
@@
     In panel \textbf{A} of figure \ref{fig:precision_problem}, we see the distribution of precision estimates versus the true precision of $52\%$ shown as a dotted vertical line.
-Precision estimates are most of the time very close to $100\%$ and always higher than $80\%$, despite the truth being a precision of only $52\%$.
+Precision estimates are usually very close to $100\%$ and always higher than $80\%$, despite the truth being a precision of only $52\%$.
 In contrast, panel \textbf{B} shows the distribution of our proposed precision estimator which is nearly unbiased.
 Both precision estimators rely on exactly the same data.
-They only differ in how they account for the underlying sampling process and the extrapolation from small benchmark datasets to full data.
+They only differ in how they account for the underlying sampling process and the extrapolation from small benchmark datasets to the full data.
 
@@
 This requires choosing between alternative methods and evaluating the results of methodological experiments.
-Without sound evaluation methodology, decisions regarding the disambiguation algorithm may be misaligned from real-world use and real-world performance.
+Without sound evaluation methodology, decisions regarding the disambiguation algorithm may not align with real-world use and real-world performance.
 Notably, for a performance metric such as the pairwise f-score, one algorithm may perform better than another on a small benchmark dataset, while the opposite may hold true for performance on the entire data.
-This problem happens on typical benchmark datasets obtained from randomly sampling blocks or randomly sampling clusters (see section \ref{sec:proposed_estimators} for a definition of different sampling mechanisms).
+This problem arises with typical benchmark datasets obtained from randomly sampling blocks or randomly sampling clusters (see section \ref{sec:proposed_estimators} for a definition of different sampling mechanisms).
 
@@
 PatentsView.org's disambiguation results have been used in numerous scientific studies \citep{toole2021patentsview}.
-These studies make assumptions about the reliability of the data which need to be validated and upheld.
+These studies make assumptions about the reliability of the data that need to be validated and upheld.
 In short, users of disambiguated data need to understand its reliability in order to make scientifically appropriate use of it.
@@
 
-Much of past work has focused on defining and using relevant clustering evaluation metrics.
+Much of the past literature has focused on defining and using relevant clustering evaluation metrics.
 The topic of estimating performance from samples has received much less attention, usually focusing on importance sampling estimators based on record pairs.
-We review contributions to these two main topics in the paragraphs below.
+We review the contributions to these two main topics below.
 
@@
 
-Pairwise precision and recall metrics were first reported in \cite{Newcombe1959}, with \cite{Bilenko2003, Christen2007} emphasizing the importance of precision-recall curves for algorithm evaluation.
-Now, there are issues with the use of pairwise precision and recall in entity resolution applications, such as the large relative importance of large clusters.
+Pairwise precision and recall metrics were first reported in \cite{Newcombe1959}, with \cite{Bilenko2003} and \cite{Christen2007} emphasizing the importance of precision-recall curves for algorithm evaluation.
+However, there are issues with the use of pairwise precision and recall in entity resolution applications, such as the large relative importance of large clusters.
 As such, other clustering metrics have been proposed, including cluster precision and recall, cluster homogeneity and completeness, and generalized merge distances \citep{Michelson2009, Menestrina2010, Maidasani2012, Barnes2015}.
@@
 
-{While our work focuses on estimating pairwise precision and recall, the general approach also applies to any cluster based performance evaluation metrics, such as those described in \cite{Michelson2009}.}
+{While our work focuses on estimating pairwise precision and recall, the general approach also applies to any cluster-based performance evaluation metrics, such as those described in \cite{Michelson2009}.}
 
@@
 
-Regarding the reliable estimation of performance metrics, \cite{Belin1995} first proposed a semi-supervised approach to calibrate error rates when using a Fellegi-Sunter model \citep{fellegi_theory_1969}.
+Regarding the reliable estimation of performance metrics, \cite{Belin1995} first proposed a semi-supervised approach to calibrating error rates when using a Fellegi-Sunter model \citep{fellegi_theory_1969}.
 \cite{Marchant2017} proposed an adaptive importance sampling estimator to estimate precision and recall from sampled record pairs.
-Other approaches to the estimation of performance metrics are model-based, where estimated precision and recall can be obtained from predicted match probabilities between record pairs \citep{enamorado2019using}.
+Other approaches to the estimation of performance metrics are model based, where estimated precision and recall can be obtained from predicted match probabilities between record pairs \citep{enamorado2019using}.
 However, these model-based approaches cannot be used when working with black-box machine learning models or ad hoc clustering algorithms.
 
-{In contrast to the above, our approach to estimation is more practical than pairwise sampling and applies to any black-box disambiguation algorithms such as those used at PatentsView.}
+{In contrast, our approach to estimation is more practical than pairwise sampling and applies to any black-box disambiguation algorithms such as those used at PatentsView.}
 
@@
 
-Our approach to estimating performance metrics is based on the use of benchmark datasets which are already existing or which can be collected in a cost-effective way.
-These datasets contain entity clusters corresponding to sampling records and recovering all associated instances, to directly sampling clusters, or to sampling blocks.
-For each of these sampling processes, we propose estimators which correct for the issues discussed in section \ref{sec:challenges}, are nearly unbiased, and easy to use in practice.
+Our approach to estimating performance metrics is based on the use of benchmark datasets that already exist or that can be collected in a cost-effective way.
+These datasets contain entity clusters corresponding to either: (a) sampling records and recovering all associated instances, (b) directly sampling clusters, or (c) sampling blocks.
+For each of these sampling processes, we propose estimators that correct for the issues discussed in section \ref{sec:challenges}, are nearly unbiased, and are easy to use in practice.
 
@@
     \item For evaluation, the review of entity clusters is much more efficient than the review of record pairs.
-We can achieve high accuracy with small samples without relying on any sophisticated sampling scheme.
+We can achieve high accuracy with small samples without relying on sophisticated sampling schemes.
 \end{enumerate}
@@
 To our knowledge, we are the first to propose unbiased performance estimators based on cluster and block samples.
-Past work either ignored biases when computing precision and recall from benchmark datasets \citep{frisoli2018exploring, Monath2021, han2019disambiguating}, did not provide estimates for one of precision or recall \citep{mcveigh2019scaling}, or provided solutions that are tailored to very specific record linkage models \citep{Belin1995}.
-We provide the first general solution to entity resolution evaluation which does not rely on sampling record pairs and which applies to any disambiguation algorithm.}
+Past work either ignored biases when computing precision and recall from benchmark datasets \citep{frisoli2018exploring, Monath2021, han2019disambiguating}, did not provide estimates for precision or recall \citep{mcveigh2019scaling}, or provided solutions tailored to very specific record linkage models \citep{Belin1995}.
+We provide the first general solution to entity resolution evaluation that does not rely on sampling record pairs and that applies to any disambiguation algorithm.}
 
 In short, the proposed approach is simple, principled, and practical.
-It is simple to use, it is statistically principled in its account of sampling processes and in its uncertainty quantification, and it is practical in the way that it can provide cost-effective estimates for any disambiguation algorithm.
+It is simple to use, it is statistically principled in its account of sampling processes and uncertainty, and it is practical in the way that it can provide cost-effective estimates for any disambiguation algorithm.
 
@@
 The rest of the paper is organized as follows.
-In section \ref{sec:data_methods}, {we describe: motivating benchmark datasets, our data collection process for evaluation, the proposed estimators, and our simulation study used to validate the performance of our estimators.} Section \ref{sec:results} then shows the results: our performance estimates and results from the simulation study.
-Finally, section \ref{sec:discussion} summarizes the paper and discusses future research directions.
+In section \ref{sec:data_methods}, {we describe benchmark datasets, our hand-disambiguation methodology for evaluation, the proposed estimators, and our simulation study that we use to validate the performance of our estimators.} Section \ref{sec:results} then presents our performance estimates and results from the simulation study.
+Section \ref{sec:discussion} summarizes the paper and explores future research directions.
 
@@
 
-In this section, {we introduce: motivating datasets used at PatentsView, our hand-disambiguation methodology, our proposed performance metric estimators, and our simulation framework used to compare estimators.} {Note that we focus on \textit{inventor} disambiguation throughout, rather than the related problems of assignee and location disambiguation.}
+In this section, {we introduce the benchmark datasets used at PatentsView, our hand-disambiguation methodology, our proposed performance metric estimators, and the simulation framework that we use to compare estimators.} {Note that we focus on \textit{inventor} disambiguation throughout, rather than on the related problems of assignee and location disambiguation.}
 
@@
 \cite{trajtenberg2008identification} disambiguated the U.S.
-patents of Israeli inventors which were granted between 1963 and 1999.
+patents of Israeli inventors that were granted between 1963 and 1999.
 A total of 6,023 Israeli inventors were identified for this time period with 15,310 associated patents.
@@
 
-\subsection{Hand-Disambiguation Protocol}\label{sec:hand-disambiguation}
+\subsection{Hand-Disambiguation Methodology}\label{sec:hand-disambiguation}
 
-In addition to the above benchmark datasets, {we have carried out a data collection experiment.
+In addition to considering the above benchmark datasets, {we have carried out hand-disambiguation of inventor mentions.
 This was motivated by the evaluation of the current PatentsView inventor disambiguation using the estimators proposed in section \ref{sec:proposed_estimators}.}
@@
 Two AIR staff were tasked with recovering inventors' patents given sampled inventor mentions.
-To do this, they were assisted by tools available on PatentsView.org.
-First, given a sampled inventor, the associated predicted cluster was reviewed \ob{and, if any, wrongly} assigned patents were removed.
+First, given a sampled inventor, the associated predicted cluster was reviewed \ob{and any wrongly} assigned patents were removed.
 Next, PatentsView's search tools were used to find additional mentions of similarly named inventors.
-These were reviewed \ob{and inventor mentions were added} to the predicted cluster if appropriate.
+These inventor mentions were reviewed \ob{and added} to the predicted cluster, if appropriate.
 The two AIR staff had an initial training session, followed by a test run on 10 inventors, before carrying out the rest of the data collection.
-They worked independently so that two resulting datasets were obtained for the same inventor mentions.
+They worked independently, which resulted in two datasets being obtained for the same inventor mentions.
 In section \ref{sec:results}, these are referred to as the \textbf{Staff 1} and \textbf{Staff 2} datasets.
 
-Note that our data collection methodology is biased towards PantentsView's current disambiguation.
-{Indeed, we do not expect the staff to have found all errors or all missing inventor mentions from predicted clusters.
+Note that our data collection methodology is biased toward PantentsView's current disambiguation.
+{Indeed, we did not expect the staff to have found all errors or all missing inventor mentions from the predicted clusters.
 The staff used their best judgment, supported by a thorough search, to resolve inventor mentions.} In cases where no errors were found, the current disambiguation was assumed to be correct.
-Performance estimates based on this data might therefore be slightly optimistic.
-{This should be acknowledged when reporting performance estimates to PatentsView.org users.
+Performance estimates based on this data might therefore be slightly optimistic, which should be acknowledged when reporting performance estimates to PatentsView.org users.
 Otherwise, for the purpose of improving the current disambiguation \ob{algorithm, this data} is still appropriate to use.
-It represents the most visible errors in the current disambiguation rather than the totality of them.}
+It represents the most visible errors in the current disambiguation rather than the totality of them.
 
@@
 Let $\mathcal{D} = \{1, 2, 3, \dots, N\}$ index a set of records let $\mathcal{C}$ be the partition of $\mathcal{D}$ representing ground truth clustering, and let $\widehat{\mathcal{C}}$ be a set of predicted clusters.
-Now let $\mathcal{T}$ be the set of record pairs which appear in the same cluster in $\mathcal{C}$ (matching pairs), and let $\mathcal{P}$ be the set of record pairs which appear in the same predicted cluster in $\widehat{\mathcal{C}}$ (predicted links).
+Now let $\mathcal{T}$ be the set of record pairs that appear in the same cluster in $\mathcal{C}$ (matching pairs), and let $\mathcal{P}$ be the set of record pairs that appear in the same predicted cluster in $\widehat{\mathcal{C}}$ (predicted links).
 Pairwise precision ($P$) and pairwise recall ($R$) are then defined as
@@
 
-We now provide three alternative representations of precision and recall which correspond to the processes of sampling records, sampling true clusters, and sampling blocks.
-These will be used to obtain precision and recall estimators under these sampling processes.
+We now provide three alternative representations of precision and recall that correspond to the processes of sampling records, sampling true clusters, and sampling blocks.
+These representations will be used to obtain precision and recall estimators under these sampling processes.
 
@@
 
-In the cluster sampling case, sampling probabilities are typically known only up to normalizing factors.
-This is due to the fact that the total number of true clusters and other aspects of the ground truth cluster distribution are unknown in practice.
-As such, we provide expressions for precision and recall which only require knowing sampling probabilities up to normalizing factors.
+In the cluster sampling case, sampling probabilities are typically known only up to a normalizing factor.
+This is because the total number of true clusters and other aspects of the ground truth cluster distribution are unknown in practice.
+As such, we provide expressions for precision and recall that only require knowing the sampling probabilities up to a normalizing factor.
 This allows the consideration of sampling uniformly at random and sampling clusters with probability proportional to their size.
@@
 \begin{remark}
-    Lemma \ref{lemma:record_sampling_representation} and lemma \ref{lemma:cluster_sampling_representation} can be generalized to apply to any performance metric which can be expressed as a sum $\sum_{c \in \mathcal{C}} h(c, \widehat{\mathcal{C}})$, for some function $h$, or as a function of such sums.
+    Lemma \ref{lemma:record_sampling_representation} and lemma \ref{lemma:cluster_sampling_representation} can be generalized to apply to any performance metric that can be expressed as a sum $\sum_{c \in \mathcal{C}} h(c, \widehat{\mathcal{C}})$, for some function $h$, or as a function of such sums.
 For instance, the use of the so-called \textit{cluster} precision and \textit{cluster} recall \citep{Barnes2015}, or of cluster homogeneity and completeness \citep{Barnes2015}, can be more appropriate in the presence of large clusters.
@@
 \begin{remark}
-    Lemmas \ref{lemma:record_sampling_representation} -- \ref{lemma:block_sampling_representation} are formulated in terms of sampled ground truth clusters and sampled blocks which do not contain errors.
+    Lemmas \ref{lemma:record_sampling_representation} -- \ref{lemma:block_sampling_representation} are formulated in terms of sampled ground truth clusters and sampled blocks that do not contain errors.
 However, given the duality between precision and recall (interchanging the roles between $\mathcal{C}$ and $\widehat{\mathcal{C}}$  interchanges precision and recall), the results also apply to sampling \textit{predicted} clusters.
@@
 As such, they can be estimated using sample means and ratios of sample means.
-For readability, we present here a generic formula for an approximately unbiased estimator of the ratio of means, and then specify the needed quantities for each representation below.
+For readability, we present here a generic formula for an approximately unbiased estimator of the ratio of means and then specify the needed quantities for each representation below.
 The estimator applies a first order bias correction to the ratio of sample means, based on a Taylor approximation.
-Approximate confidence intervals can be computed based on the variance estimator of the ratio of sample means by Taylor approximation, assuming the corrected estimator has small bias \citep{fuller2011sampling}.
+Approximate confidence intervals can be computed based on the variance estimator of the ratio of sample means by Taylor approximation, assuming the corrected estimator has a small bias \citep{fuller2011sampling}.
 The generic formula for estimating the ratio of $T$-sized ``population'' (of records/clusters/blocks) means of the form
@@
 \end{align}
-We note that an additional symbol $\theta_{n,T}$ is introduced for possible finite population correction when relatively large number of elements are sampled without replacement (see below).
+We note that an additional symbol $\theta_{n,T}$ is introduced for a possible finite population correction when relatively large number of elements are sampled without replacement (see below).
 Classical adjustment is set to $\theta_{n,T} = (1 - \frac{n-1}{T-1})$ \citep{Cochran1977}.
-For practical purposes when $T$ is large, often $\theta_{n,T}=1$ will suffice.
+For practical purposes when $T$ is large, $\theta_{n,T}=1$ will suffice.
 In fact, knowledge of $T$ is not needed at all as long as it is large enough relative to $n$, which is useful because the total number of true clusters/blocks is not known in advance.
-Confidence interval can be computed based on the variance estimate of the above, which is
+Confidence intervals can be computed based on the variance estimate of the above, which is
 \begin{align} \label{eq:estimated_variance}
@@
 \end{align}
-The specific values for $A_s$, $B_s$, and $T$ in each of our representation are described in appendix \ref{sec:appendix}.
+The specific values for $A_s$, $B_s$, and $T$ in each of our representation are described in appendix \ref{sec:appendix_estimators}.
 
@@
     In entity resolution applications, we can typically assume that elements have been sampled with replacement (or closely so).
-Indeed, with a small proportion of sampled elements, non-replacement samples are approximately equivalent to samples with replacement.
-However, if dealing with relatively large non-replacement samples, then the sampling probabilities used in the definition of the estimators should be adjusted to reflect the size-dependent effect of non-replacement \citep{Horvitz1952}.
+Indeed, with a small proportion of sampled elements, nonreplacement samples are approximately equivalent to samples with replacement.
+However, if dealing with relatively large nonreplacement samples, then the sampling probabilities used in the definition of the estimators should be adjusted to reflect the size-dependent effect of nonreplacement \citep{Horvitz1952}.
 \end{remark}
@@
 
-In order to assess the performance of the proposed estimators, we carry out a simulation study based on PatentsView's inventor disambiguation.
-Specifically, in the context of the simulation, we consider PatentsView current inventor disambiguation as the ground truth clustering.
-A simulated set of predicted clusters is obtained by introducing errors (misattribution of inventor mentions) into the current disambiguation.
-We then estimate the precision and recall of this predicted clustering using our estimators based on random cluster samples.
-The process of sampling clusters and estimating precision/recall is repeated $100$ times in order to provide the distribution of the estimators and metrics such as bias and root mean squared error (rmse).
+In order to assess the performance of the proposed estimators, we carried out a simulation study based on PatentsView's inventor disambiguation.
+Specifically, in the context of the simulation, we considered PatentsView current inventor disambiguation as the ground truth clustering.
+A simulated set of predicted clusters was obtained by introducing errors (misattribution of inventor mentions) into the current disambiguation.
+We then estimated the precision and recall of this predicted clustering using our estimators based on random cluster samples.
+The process of sampling clusters and estimating precision/recall was repeated $100$ times in order to provide the distribution of the estimators and metrics such as bias and root mean squared error (rmse).
 
-To introduce errors, we pick records at random and change their cluster assignment to that of other records picked at random.
-This is a simple process which ensures that larger clusters are more likely to contain errors.
-In our simulation, we consider rates of $5\%$, $10\%$, and $25\%$ for the proportion of records that are sampled for cluster misassignment.
-The larger proportions of error are more realistic.
-However, the $5\%$ misattribution rate helps showcase properties of our estimators when only a small portion of sampled clusters are associated with errors.
+To introduce errors, we picked records at random and changed their cluster assignment to that of other records picked at random.
+This is a simple process that ensures that larger clusters are more likely to contain errors.
+In our simulation, we considered rates of $5\%$, $10\%$, and $25\%$ for the proportion of records that are sampled for cluster misassignment.
+Although the larger error rates are more realistic, the $5\%$ misattribution rate helps showcase the properties of our estimators when only a small proportion of the sampled clusters is associated with errors.
 
-For the sampling process, we consider sampling records uniformly at random and recovering their associated clusters.
+For the sampling process, we considered sampling records uniformly at random and recovering their associated clusters.
 This is the same as sampling clusters with probability proportional to their size.
-In the record/cluster sampling cases, we look at the effect of sampling $100$, $200$ and $400$ records/clusters.
+In the record/cluster sampling cases, we looked at the effect of sampling $100$, $200$ and $400$ records/clusters.
 
-Finally, we compare the following three precision and recall estimators:
+Finally, we compared the following three precision and recall estimators:
 \begin{description}
-    \item[\texttt{P\_naive}, \texttt{R\_naive}] This is the ``naive" precision (resp.
-recall) estimator obtained by computing precision (resp.
-recall) when only looking at records which appear in the sampled clusters.
+    \item[\texttt{P\_naive}, \texttt{R\_naive}] This is the ``naive" precision (respectively recall) estimator obtained by computing precision (respectively recall) when only looking at records that appear in the sampled clusters.
     \item[\texttt{P\_record}, \texttt{R\_record}] These are the precision and recall estimators corresponding to uniformly sampling records in lemma \ref{lemma:record_sampling_representation} ($p_i \propto 1$) with the bias adjustment given in \eqref{eq:bias_adjustment}.
 Note that these are the same as the estimators obtained from lemma \ref{lemma:cluster_sampling_representation} when sampling clusters with probability proportional to their size ($p_c \propto \lvert c \rvert$).
-    \item[\texttt{P\_cluster\_block}] This is the precision estimator obtained by considering each sampled cluster as its own block in lemma \ref{lemma:block_sampling_representation}, where clusters have been sampled with probability proportional to their size ($p_b \propto \lvert b \rvert$), and with bias adjustment given in \eqref{eq:bias_adjustment}.
+    \item[\texttt{P\_cluster\_block}] This is the precision estimator obtained by considering each sampled cluster as its own block in lemma \ref{lemma:block_sampling_representation}, where clusters have been sampled with probability proportional to their size ($p_b \propto \lvert b \rvert$) and with the bias adjustment given in \eqref{eq:bias_adjustment}.
 Note that in the case of recall with cluster blocks, the estimator corresponding to lemma \ref{lemma:block_sampling_representation} is the same as the one corresponding to lemma \ref{lemma:cluster_sampling_representation} and lemma \ref{lemma:record_sampling_representation}.
@@
 
-The reason why \texttt{P\_cluster\_block} performs better than \texttt{P\_record} is due to the fact that \texttt{P\_record} has been derived in a generic way which applies to any performance metric which can be expressed in cluster form similar to \eqref{eq:lemma_1}.
+\texttt{P\_cluster\_block} performs better than \texttt{P\_record} because \texttt{P\_record} has been derived in a generic way that applies to any performance metric that can be expressed in cluster form similar to \eqref{eq:lemma_1}.
 On the other hand, \texttt{P\_cluster\_block} relies on specific properties of precision.
@@
 In practice, \texttt{P\_cluster\_block} should be preferred as a pairwise precision estimator.
+The bias and rmse of the precision estimators are reported in table \ref{tab:precision_results}.
 
@@
 \end{figure}
-
-Bias and root mean squared error are reported in table \ref{tab:precision_results}.
 
@@
 However, the recall estimator accounting for the sampling mechanism is more accurate.
-Bias and root mean squared error (rmse) are reported in table \ref{tab:recall_results}.
+The bias and rmse of the recall estimators are reported in table \ref{tab:recall_results}.
 
@@
 Note that no variance estimates can be given for single samples.
-For \cite{Li2014}'s inventors benchmark, given that inventor clusters were originally obtained from a set of inventor curriculum vitae, we assumed that inventor clusters were sampled uniformly at random.
+For \cite{Li2014}'s inventors benchmark, given that the inventor clusters were originally obtained from a set of inventor curriculum vitae, we assumed that the clusters were sampled uniformly at random.
 As such, we used cluster block estimators with constant probability weights.
 
-\begin{table}
+\begin{table}[!h]
     \centering
@@
     \midrule
-    Staff 1 & 86\% (5.6\%) & 94\% (2.1\%)  & 1976 -- Dec. 31, 2022 (U.S. granted)\\
-    Staff 2 & 88\% (5.6\%) & 95\% (2.0\%) & 1976 -- Dec. 31, 2022 (U.S. granted)\\
+    Staff 1 & 88\% (3.4\%) & 95\% (1.1\%)  & 1976 -- Dec. 31, 2022 (U.S. granted)\\
+    Staff 2 & 87\% (3.6\%) & 96\% (1.0\%) & 1976 -- Dec. 31, 2022 (U.S. granted)\\
     Israeli Benchmark & 79\% (NA) & 94\% (NA) & 1976 -- 1999 (U.S. granted)\\
@@
 \end{table}
-
-It is interesting to note that there is a small but notable difference in the estimates from the ``Staff 1" and ``Staff 2" datasets.
-Since these datasets were obtained by two different people from the same sample of inventor mentions, the difference in estimates is due to differences in the hand-disambiguation provided by the two staff.
-Staff 2 was slightly more conservative than Staff 1 in flagging errors.
 
@@
 Motivated by PatentsView's disambiguation, this paper introduced a novel evaluation methodology for entity resolution algorithms.
-The methodology relies on benchmark datasets containing ground truth clusters and estimators which account for biases inherent to these datasets.
-For PatentsView, this provided the first representative estimates of disambiguation performance.
+The methodology relies on benchmark datasets containing ground truth clusters and estimators that account for biases inherent to these datasets.
+For PatentsView, this provided the first representative estimates of its disambiguation performance.
 Furthermore, all data and code used in this paper, as well as other tools developed to facilitate evaluation at PatentsView, are freely available at \hyperref[https://github.com/PatentsView/PatentsView-Evaluation/]{https://github.com/PatentsView/PatentsView-Evaluation/}.
 
-There are two main resulting products for this work.
-The first is to provide PatentsView data users with an appropriate understanding of PatentsView data quality.
+There are two main products resulting from this work.
+The first is the appropriate understanding of the quality of the data provided to PatentsView's users.
 Our performance estimates indicate that, despite an overall accurate disambiguation, there is significant room for \ob{improvement.
 Notably, the current disambiguation over-estimates the number of matching inventor mention pairs.} The second product is the set of tools needed for methodological research and model comparison.
-Given our evaluation methodology, we can now reliably compare algorithms and decide with confidence on changes which will affect users.
+Given our evaluation methodology, we can now reliably compare algorithms and decide with confidence on changes that will affect users.
 
@@
 This is challenging problem given the lack of validation information available.
-Surveying inventors to validate the hand-disambiguation process would be one approach to explore for this.
+Surveying inventors to validate the hand-disambiguation process would be one way to explore this issue.
 Sensitivity analyses involving potential errors in the hand-disambiguation process could also be informative.
-We refer the reader to \citep{bailey2017well} for a state-of-the-art hand-labeling study which evaluated human review accuracy.}
+We refer the reader to \cite{bailey2017well} for a state-of-the-art hand-labeling study that evaluated human review accuracy.}
 
 {Another important topic for future work is the development of estimators for additional performance metrics.
-As we have seen in the simulation study, the generically-derived estimators (e.g., from lemma \ref{lemma:cluster_sampling_representation}) do not perform as well as estimators derived using specific properties of pairwise precision and recall (lemma \ref{lemma:block_sampling_representation}).
+As we have seen in the simulation study, the generically derived estimators (e.g., from lemma \ref{lemma:cluster_sampling_representation}) do not perform as well as estimators derived using specific properties of pairwise precision and recall (lemma \ref{lemma:block_sampling_representation}).
 As such, care should be taken to obtain efficient estimators for every metric of interest.}
@@
 \ob{Finally, we note that the performance of estimators can degrade when dealing with heavy-tailed cluster size distributions.
-Bias of ratio estimators can be high in this case, especially when using small samples and when sampling clusters uniformly at random rather than with probability proportional to their size.
-Model-based estimators which exploit known properties of the cluster size distribution could be developed to improve estimation accuracy in this situation.}
+The bias of ratio estimators can be high in this case, especially when using small samples and when sampling clusters uniformly at random rather than with probability proportional to size.
+Model-based estimators that exploit known properties of the cluster size distribution could be developed to improve estimation accuracy in such cases.}
 
@@
 
-Olivier Binette led the project and wrote most of the manuscript.
-Sokhna A York and Emma Hickerson carried out data collection by manually reviewing inventor clusters.
+Olivier Binette led the evaluation project and wrote most of this manuscript.
+Sokhna A York and Emma Hickerson carried out the data collection by manually reviewing inventor clusters.
 Youngsoo Baek provided bias adjustment and uncertainty quantification for ratio estimators.
@@
 
-\subsection{Bias of precision computed on benchmark datasets}\label{appendix:example}
+\subsection{Bias of Precision Computed on Benchmark Datasets}\label{appendix:example}
 
-This section provides more information regarding example \ref{first_example}.
+This section provides more information on example \ref{first_example}.
 
-For this example, we considered the RLdata10000 dataset from \citep{RecordLinkage}.
+For this example, we considered the RLdata10000 dataset from \cite{RecordLinkage}.
 This is a synthetic dataset containing 10,000 records with first name, last name, and date of birth attributes.
@@
 
-The disambiguation algorithm we consider matches records together if any of the following conditions is met:
+The disambiguation algorithm we consider matches records if any of the following conditions are met:
 \begin{itemize}
@@
 It has $52\%$ precision and $83\%$ recall.
-However, it allows to to showcase the issue with non-adjusted precision computed on cluster samples.
+However, it allows us to to showcase the issue with nonadjusted precision computed on cluster samples.
 
-In our experiment, we have repeated 5,000 times the following 3-steps process:
+In our experiment, we have repeated 5,000 times the following three-steps process 5,000 times:
 \begin{enumerate}
-    \item First, 200 records were sampled and the ground truth clusters associated to them were recovered. This provided a ``benchmark" dataset which was used for evaluation.
+    \item First, 200 records were sampled and the ground truth clusters associated with them were recovered. This step provided a ``benchmark" dataset that was used for evaluation.
     \item Second, a trivial precision estimate was obtained by computing precision over the benchmark dataset.
-That is, predicted cluster assignments were restricted to records which appear in the benchmark data and precision was compared for this.
-Most often than not, the result was an observation of $100\%$ precision.
-    \item Third, we computed our proposed precision estimator which corresponds to lemma \ref{lemma:record_sampling_representation} and the estimator $\widehat P_{\text{block}}$ defined in equation \eqref{eq:P_block}, with blocks corresponding to clusters and with sampling probabilities $p_b \propto \lvert b \rvert$.
+That is, predicted cluster assignments were restricted to records that appear in the benchmark data and precision was compared for these records.
+More often than not, the result was an observation of $100\%$ precision.
+    \item Third, we computed our proposed precision estimator which corresponds to lemma \ref{lemma:record_sampling_representation} and the estimator $\widehat P_{\text{block}}$ defined in \eqref{eq:P_block}, with blocks corresponding to clusters and with sampling probabilities $p_b \propto \lvert b \rvert$.
 \end{enumerate}
-The distributions of the these two precision estimates over the 5,000 repetitions are shown in figure \ref{fig:precision_problem}.
+The distributions of the two precision estimates over the 5,000 repetitions are shown in figure \ref{fig:precision_problem}.
 Our proposed estimator is accurate and nearly unbiased, whereas the trivial precision estimates have almost nothing to do with actual algorithmic performance.
 
-\subsection{Precision and Recall Estimator Formulas}
+\subsection{Precision and Recall Estimator Formulas} \label{sec:appendix_estimators}
 
 This section describes specific values for $A_s$, $B_s$, and $T$ in \eqref{eq:bias_adjustment} in order to obtained nearly unbiased precision and recall estimators based on each of the representation in section \ref{sec:proposed_estimators}.
-We use the symbols $\widehat P$ and $\widehat R$, indexed by one of ``$\text{rec}$", ``$\text{clust}$", and ``$\text{block}$", in order to refer to precision and recall estimators corresponding to record, cluster, and block sampling representations.
+We use the symbols $\widehat P$ and $\widehat R$, indexed by either ``$\text{rec}$", ``$\text{clust}$", or ``$\text{block}$", in order to refer to precision and recall estimators corresponding to record, cluster, and block sampling representations, respectively.
 
@@
 
+\subsection{Estimators Implementation}\label{sec:implementation}
+
+\ob{The proposed estimators have been implemented as part of the \textbf{pv\_evaluation} Python package available on GitHub at \url{https://github.com/PatentsView/PatentsView-Evaluation}.
+Given a predicted clustering \texttt{prediction} and given a set of sampled clusters \texttt{sample}, each represented as a membership vector (pandas Series objects with mention identifiers as an index and cluster assignment identifiers as values), estimates can be obtained as follows.
+First, the sampling mechanism has to be chosen.
+This can be one of ``\texttt{record}" for record sampling as in lemma \ref{lemma:record_sampling_representation}, ``\texttt{cluster}" for the estimator corresponding to cluster sampling as in lemma \ref{lemma:cluster_sampling_representation}, ``\texttt{cluster\_block}" for cluster sampling with the estimator corresponding to lemma \ref{lemma:block_sampling_representation}, and ``\texttt{single\_block}" for the sampling of a single block with the estimator corresponding to lemma \ref{lemma:block_sampling_representation}.
+Then, probability weights can be set to either ``\texttt{uniform}" for uniform sampling, or ``\texttt{cluster\_size}" for sampling with probability proportional to size.}
+
+\ob{For example, when sampling clusters with probability proportional to their sizes and using the estimator corresponding to lemma \ref{lemma:block_sampling_representation}, precision estimates can be obtained as follows:}
+\begin{lstlisting}[language=Python]
+from pv_evaluation.estimators import pairwise_precision_estimator
+pairwise_precision_estimator(
+    prediction, 
+    sample, 
+    sampling_type="cluster_block", 
+    weights="cluster_size"
+)
+\end{lstlisting}
+\ob{Standard deviation estimates are obtained similarly using the \texttt{pairwise\_precision\_std()} function from the \texttt{pv\_evaluation.estimators} module.
+The complete API documentation can be consulted at \url{https://patentsview.github.io/PatentsView-Evaluation}.}
+
 \subsection{Proofs}\label{appendix:proofs}
@@
 \end{equation}
-Through a similar argument as above, we may express the nominator as 
+Through a similar argument as above, we may express the numerator as 
 \begin{equation}\label{eq:nominator}
@@
 \end{equation}
-Simplifying $\pi \lvert \mathcal{C} \rvert$ from the nominator and denominator then yields the expression for precision.
+Simplifying $\pi \lvert \mathcal{C} \rvert$ from the numerator and denominator then yields the expression for precision.
 
-The expression for recall follows in a straightforward way from equation \eqref{eq:recall_cluster_form}.
+The expression for recall follows in a straightforward way from \eqref{eq:recall_cluster_form}.
 \end{proof}
@@
 It follows that $\lvert T \rvert = \sum_{b \in \mathcal{B}} \lvert \mathcal{T}_b \rvert$ and  $\lvert \mathcal{T} \cap \mathcal{P} \rvert = \sum_{b \in \mathcal{B}} \lvert \mathcal{T}_b \cap \mathcal{P}_b \rvert$.
-The expression for recall in in \eqref{eq:lemma_3} follows directly.
+The expression for recall in \eqref{eq:lemma_3} follows directly.
 For precision, we can express $\lvert \mathcal{P} \rvert$ as the number of links within blocks plus the number of links across blocks.
-Since the number of links across blocks are counted twice when considering for each block, we obtain $\lvert \mathcal{P} \rvert = \sum_{b \in \mathcal{B}} \left( \lvert \mathcal{P}_b \rvert + \tfrac{1}{2} \lvert \mathcal{P}_b^{-} \rvert \right)$.
+Since the number of links across blocks is counted twice when each block is considered, we obtain $\lvert \mathcal{P} \rvert = \sum_{b \in \mathcal{B}} \left( \lvert \mathcal{P}_b \rvert + \tfrac{1}{2} \lvert \mathcal{P}_b^{-} \rvert \right)$.
 \end{proof}

### 2022-08-12 pv_evaluation/benchmark/report.py
Tooltips (#33)
* update

* update docs

* update changelog

@@ -223,7 +223,23 @@ def style_cluster_inspection(table, by="prediction"):
     return table.style.apply(format_color_groups, axis=None)
 
 
-def inspect_clusters_to_split(disambiguation, benchmark, join_with=None):
+def add_links(table, type="patentsview"):
+    """Add Google Patents links to table with mention IDs as index. 
+
+    Args:
+        table (DataFrame): pandas DataFrame with mention IDs as an index.
+
+    Returns:
+        DataFrame: table with added Google Patents links.
+    """
+
+    if len(table) > 0:
+        patent_codes = table.index.str.split("-", expand=True).droplevel(1).str.lstrip("US").values
+        table["link"] = [f"<a class='previewbox-anchor' href='https://datatool.patentsview.org/#detail/patent/{x}'>🔗</a>" for x in patent_codes]
+    return table
+
+
+def inspect_clusters_to_split(disambiguation, benchmark, join_with=None, links=False):
     """Get table of cluster assignment errors on the given benchmark.
 
     Args:
@@ -244,12 +260,17 @@ def inspect_clusters_to_split(disambiguation, benchmark, join_with=None):
     )
 
     if join_with is not None:
-        return clusters_to_split.join(join_with, rsuffix="_joined")
+        table = clusters_to_split.join(join_with, rsuffix="_joined")
     else:
-        return clusters_to_split
+        table = clusters_to_split
+
+    if links:
+        table = add_links(table)
+
+    return table
 
 
-def inspect_clusters_to_merge(disambiguation, benchmark, join_with=None):
+def inspect_clusters_to_merge(disambiguation, benchmark, join_with=None, links=False):
     """Get table to inspect missing cluster links given a benchmark dataset.
 
     Args:
@@ -264,6 +285,11 @@ def inspect_clusters_to_merge(disambiguation, benchmark, join_with=None):
     clusters_to_merge.rename(columns={"prediction": "reference", "reference": "prediction"}, inplace=True)
 
     if join_with is not None:
-        return clusters_to_merge.join(join_with, rsuffix="_joined")
+        table = clusters_to_merge.join(join_with, rsuffix="_joined")
     else:
-        return clusters_to_merge
+        table = clusters_to_merge
+
+    if links:
+        table = add_links(table)
+
+    return table

### 2022-08-23 paper/main.tex
Updates from Overleaf

@@
 
-\title{Practical Performance Evaluation of Entity Resolution Algorithms: Lessons Learned at PatentsView.org}
+\title{Estimating the Performance of Entity Resolution Algorithms: New Approach and a Case Study at PatentsView.org}
 
@@
 However, there are issues with the use of pairwise precision and recall in entity resolution applications, such as the large relative importance of large clusters.
-As such, other clustering metrics have been proposed, including cluster precision and recall, cluster homogeneity and completeness, and generalized merge distances \citep{Michelson2009, Menestrina2010, Maidasani2012, Barnes2015}.
+As such, other clustering metrics have been proposed, including cluster precision and recall, cluster homogeneity and completeness, the B$^3$ metric \citep{bagga1998algorithms}, and generalized merge distances \citep{Michelson2009, Menestrina2010, Maidasani2012, Barnes2015}.
 Important practical issues regarding the use of aggregate metrics are discussed in \cite{Hand2018}.
@@
 
+\nocite{Subramanian2021}
 \bibliographystyle{chicago}

### 2022-09-21 paper/main.tex
update paper

@@
 
-\title{Estimating the Performance of Entity Resolution Algorithms: New Approach and a Case Study at PatentsView.org}
+\title{Estimating the Performance of Entity Resolution Algorithms: Lessons Learned Through PatentsView.org}
+%\title{Estimating the Performance of Entity Resolution Algorithms: New Approach and a Case Study for PatentsView.org}
 
@@
 
-\begin{table}\label{tab:precision_results}
+\begin{table}
     \centering
-    \caption{\centering Bias and root mean squared error (rmse) of precision estimators for the simulation study described in section \ref{sec:simulation_study}.
+    \caption{\label{tab:precision_results}\centering Bias and root mean squared error (rmse) of precision estimators for the simulation study described in section \ref{sec:simulation_study}.
 The \texttt{rate} variable represents the percentage misattribution rate.}
@@
 
-\begin{table}\label{tab:recall_results}
+\begin{table}
     \centering
-    \caption{\centering Bias and root mean squared error of recall estimators for the simulation study described in section \ref{sec:simulation_study}.
+    \caption{\label{tab:recall_results}\centering Bias and root mean squared error of recall estimators for the simulation study described in section \ref{sec:simulation_study}.
 The \texttt{rate} variable represents the percentage misattribution rate.}
@@
 \begin{equation}
-    P = \sum_{i=1}^N p_i \frac{g(c(i)), \widehat{\mathcal{C}})}{p_i \lvert c(i) \rvert} = \mathbb{E}\left[ \frac{g(c(i)), \widehat{\mathcal{C}}}{p_i \lvert c(i) \rvert} \right].
+    P = \sum_{i=1}^N p_i \frac{g(c(i)), \widehat{\mathcal{C}})}{p_i \lvert c(i) \rvert} = \mathbb{E}\left[ \frac{g(c(i), \widehat{\mathcal{C}})}{p_i \lvert c(i) \rvert} \right].
 \end{equation}

### 2022-11-04 setup.py
version 1.0.0 draft

@@ -4,7 +4,8 @@ from setuptools import setup, find_packages
 if __name__ == "__main__":
     setup(
         name="pv_evaluation",
-        version="0.0.1",
+        version="1.0.0",
+        license_files = ('LICENSE.txt',),
         author="Olivier Binette, Sarvo Madhavan",
         author_email="olivier.binette@gmail.com",
         description="Tools to evaluate disambiguation algorithms",
@@ -23,6 +24,7 @@ if __name__ == "__main__":
             "quarto",
             "jinja2",
             "kaleido",
+            "openpyxl",
         ],
         scripts=["scripts/hand-disambiguation/process-inventors-hand-disambiguation.py"],
     )

### 2022-11-04 pv_evaluation/templates/inventor/callouts/entropy-tips.qmd
version 1.0.0 draft

@@
 
-For $q=2$, the Hill number is the probability that two randomly sampled inventors have the same number of authored patents:
+For $q=2$, the Hill number is the inverse of the probability that two randomly sampled inventors have the same number of authored patents:
 $$

### 2022-11-14 paper/main.tex

@@
 
-\renewcommand{\baselinestretch}{1.2}
+\renewcommand{\baselinestretch}{2}
 
@@
 This paper introduces a novel evaluation methodology for entity resolution algorithms.
-It is motivated by PatentsView.org, a {U.S.
-Patents and Trademarks Office patent data exploration tool} that disambiguates patent inventors using an entity resolution algorithm.
+It is motivated by PatentsView.org, a U.S.
+Patents and Trademarks Office patent data exploration tool that disambiguates patent inventors using an entity resolution algorithm.
 We provide a data collection methodology and tailored performance estimators that account for sampling biases.

### 2022-11-29 scripts/hand-disambiguation/process-inventors-hand-disambiguation.py
update

@@ -145,8 +145,8 @@ if args.debug:
 else:
     true_clusters = benchmark.apply(lambd, axis=1)
     reference = (
-        pd.concat({"inventor_id": benchmark.inventor_id, "mention_id": true_clusters}, axis=1)
+        pd.concat({"unique_id": benchmark.inventor_id, "mention_id": true_clusters}, axis=1)
         .explode("mention_id")
-        .set_index("mention_id")["inventor_id"]
+        .set_index("mention_id")["unique_id"]
     )
     reference.to_csv(args.output)

### 2022-11-29 pv_evaluation/templates/inventor/2-summary.qmd
update

--- 2022-05-25 pv_evaluation/templates/inventor/2-summary.qmd
@@
 ```{python}
+import os
 import pandas as pd
@@
 
-from pv_evaluation.utils import compare_plots
-from pv_evaluation.summary import InventorDisambiguationSummary
+from er_evaluation.plots import compare_plots, plot_cluster_sizes_distribution
 from pv_evaluation.benchmark import inventor_benchmark_plot
@@
 ```{python}
-summarizers = {filename: InventorDisambiguationSummary(filename, processed_data_dir=".") for filename in {{ summary_table_files }} }
+def read_auto(datapath, dtype):
+    _, ext = os.path.splitext(datapath)
+
+    if ext == ".csv":
+        return pd.read_csv(datapath, dtype=dtype)
+    elif ext == ".tsv":
+        return pd.read_csv(datapath, sep="\t", dtype=dtype)
+    elif ext in [".parquet", ".pq", ".parq"]:
+        return pd.read_parquet(datapath, dtype=dtype)
+    elif ext in [".xlsx", ".xls"]:
+        return pd.read_excel(datapath, dtype=dtype)
+    else:
+        raise Exception("Unsupported file type. Should be one of csv, tsv, parquet, or xlsx.")
+
+def load_disambiguation(filename):
+    data = read_auto(filename, dtype=str)
+    data.set_index("mention_id", inplace=True)
+    disambiguation = data.iloc[:, 0]
+    disambiguation.rename(data.columns.values[0], inplace=True)
+    return disambiguation
+
+disambiguations = {filename: load_disambiguation(filename) for filename in {{ disambiguation_files }}}
+
+inventor_not_disambiguated = read_auto("{{ inventor_not_disambiguated_file }}", dtype=str)
+inventor_not_disambiguated["mention_id"] = "US" + inventor_not_disambiguated.patent_id + "-" + inventor_not_disambiguated.inventor_sequence
+inventor_not_disambiguated.set_index("mention_id", inplace=True)
 ```
@@
 
+:::{.column-body-outset}
 ```{python}
-compare_plots(*[s.plot_cluster_size_distribution() for s in summarizers.values()])
+fig = compare_plots(*[plot_cluster_sizes_distribution(d, name=k, normalize=True) for k, d in disambiguations.items()])
+fig.update_layout(autosize=False, width=800)
+fig.update_xaxes(range=(0, 20))
+fig.update_yaxes(autorange=True)
+fig.show()
 ```
+:::
 
@@
 ```{python}
-summarizers["{{ filename }}"].get_top_inventors(n=20)
+# Top inventors dataframe
 ```
@@
 
+:::{.column-body-outset}
 ```{python}
-compare_plots(*[s.plot_entropy_curve() for s in summarizers.values()])
+#fig = compare_plots(*[plot_cluster_sizes_distribution(d, name=k, normalize=True) for k, d in disambiguations.items()])
+#fig.update_layout(autosize=False, width=800)
+#fig.update_xaxes(range=(0, 20))
+#fig.update_yaxes(autorange=True)
+#fig.show()
 ```
+:::
 
@@
 
+:::{.column-body-outset}
 ```{python}
-compare_plots(*[s.plot_cluster_unique_name_distribution() for s in summarizers.values()])
+#fig = # Plot unique cluster size distribution
+#fig.update_layout(autosize=False, width=800)
+#fig.show()
 ```
+:::
 
@@
 
+:::{.column-body-outset}
 ```{python}
-compare_plots(*[s.plot_homonymy_rate_distribution() for s in summarizers.values()])
+#fig = compare_plots(*[s.plot_homonymy_rate_distribution() for s in summarizers.values()])
+#fig.update_layout(autosize=False, width=800)
+#fig.show()
 ```
+:::
 

### 2022-11-29 pv_evaluation/benchmark/__init__.py

@@ -7,14 +7,13 @@ from pv_evaluation.benchmark.data import (
     load_lai_2011_inventors_benchmark,
     load_als_inventors_benchmark,
     load_ens_inventors_benchmark,
+    load_binette_2022_inventors_benchmark,
     load_air_umass_assignees_benchmark,
     load_nber_subset_assignees_benchmark,
 )
 
 from pv_evaluation.benchmark.report import (
-    inventor_estimates_table,
     inventor_estimates_plot,
-    inventor_benchmark_table,
     inventor_benchmark_plot,
     inspect_clusters_to_split,
     inspect_clusters_to_merge,
@@ -30,9 +29,7 @@ __all__ = [
     "load_harvard_inventors_benchmark",
     "load_air_umass_assignees_benchmark",
     "load_nber_subset_assignees_benchmark",
-    "inventor_estimates_table",
     "inventor_estimates_plot",
-    "inventor_benchmark_table",
     "inventor_benchmark_plot",
     "inspect_clusters_to_split",
     "inspect_clusters_to_merge",

### 2022-11-29 pv_evaluation/benchmark/report.py

@@ -159,7 +159,7 @@ def inspect_clusters_to_split(disambiguation, benchmark, join_with=None, links=F
     Args:
         disambiguation (Series): disambiguation result Series (disambiguation results are pandas Series with "mention_id" index and cluster assignment values).
         benchmark (Series): reference disambiguation Series.
-        join_with (DataFrame, optional): DataFrame to join based on "mention_id". Defaults to None.
+        join_with (DataFrame, optional): DataFrame indexed by "mention_id". Defaults to None.
 
     Returns:
         DataFrame: DataFrame containing erroneous cluster assignments according to the given benchmark.
@@ -190,7 +190,7 @@ def inspect_clusters_to_merge(disambiguation, benchmark, join_with=None, links=F
     Args:
         disambiguation (Series): disambiguation result Series (disambiguation results are pandas Series with "mention_id" index and cluster assignment values).
         benchmark (Series): reference disambiguation Series.
-        join_with (DataFrame, optional): DataFrame to join based on "mention_id". Defaults to None.
+        join_with (DataFrame, optional): DataFrame indexed by "mention_id". Defaults to None.
 
     Returns:
         DataFrame: DataFrame containing missing cluster links according to the given benchmark.

### 2022-11-29 pv_evaluation/templates/render.py

@@ -6,13 +6,13 @@ from pkg_resources import resource_filename
 from datetime import datetime
 
 
-def render_inventor_disambiguation_report(outdir, disambiguation_files, inventor_not_disambiguated, cache=True, **kwargs):
+def render_inventor_disambiguation_report(outdir, disambiguation_files, inventor_not_disambiguated_file, cache=True, **kwargs):
     """Create html report based on disambiguation results.
 
     Args:
         outdir (str): directory where to output html files.
         disambiguation_files (list): list of string paths to disambiguation files (tables with the two columns "mention_id" and "inventor_id"). Files format can be one of tsv, csv, or parquet.
-        inventor_not_disambiguated (str): string path to a file containing the columns "patent_id", "inventor_sequence", "raw_inventor_name_first", and "raw_inventor_name_last".
+        inventor_not_disambiguated (str): string path to a file containing the columns "patent_id", "inventor_sequence", "raw_inventor_name_first", and "raw_inventor_name_last". For granted patents, this should be the file "g_inventor_not_disambiguated.tsv" from PatentsView's bulk data downloads.
         cache (bool, optional): whether or not to cache jupyter chunk execution between runs. Defaults to True.
 
     Notes:
@@ -21,18 +21,18 @@ def render_inventor_disambiguation_report(outdir, disambiguation_files, inventor
     env = Environment(loader=PackageLoader("pv_evaluation", package_path="templates"))
     template = env.get_template("inventor/0-report.qmd")
 
-    qmdpath = os.path.join(outdir, "index.qmd")
-    htmlpath = os.path.join(outdir, "index.html")
+    qmdpath = os.path.join(os.path.abspath(outdir), "index.qmd")
 
     shutil.copyfile(resource_filename("pv_evaluation", "templates/inventor/header.html"), os.path.join(outdir, "header.html"))
     shutil.copyfile(resource_filename("pv_evaluation", "templates/inventor/footer.html"), os.path.join(outdir, "footer.html"))
 
     with open(qmdpath, "w+") as file:
         file.write(
-            template.render(summary_table_files=summary_table_files, datetime=datetime.now().strftime("%I:%M%p on %B %d, %Y"))
+            template.render(disambiguation_files=disambiguation_files, 
+            inventor_not_disambiguated_file=inventor_not_disambiguated_file, datetime=datetime.now().strftime("%I:%M%p on %B %d, %Y"))
         )
 
     if quarto.path() is None:
[…]

### 2022-11-30 pv_evaluation/benchmark/__init__.py
update

@@ -18,6 +18,11 @@ from pv_evaluation.benchmark.report import (
     inspect_clusters_to_split,
     inspect_clusters_to_merge,
     style_cluster_inspection,
+    top_inventors,
+    plot_entropy_curves,
+    plot_cluster_sizes,
+    plot_name_variation_rates,
+    plot_homonimy_rates,
 )
 
 __all__ = [
@@ -26,6 +31,7 @@ __all__ = [
     "load_lai_2011_inventors_benchmark",
     "load_als_inventors_benchmark",
     "load_ens_inventors_benchmark",
+    "load_binette_2022_inventors_benchmark",
     "load_harvard_inventors_benchmark",
     "load_air_umass_assignees_benchmark",
     "load_nber_subset_assignees_benchmark",
@@ -34,4 +40,9 @@ __all__ = [
     "inspect_clusters_to_split",
     "inspect_clusters_to_merge",
     "style_cluster_inspection",
+    "top_inventors",
+    "plot_entropy_curves",
+    "plot_cluster_sizes",
+    "plot_name_variation_rates",
+    "plot_homonimy_rates",
 ]

### 2022-11-30 pv_evaluation/benchmark/report.py

@@ -1,6 +1,7 @@
 import itertools
 import pandas as pd
 import plotly.express as px
+import numpy as np
 
 from er_evaluation.utils import expand_grid
 from er_evaluation.estimators import (
@@ -9,12 +10,19 @@ from er_evaluation.estimators import (
     pairwise_recall_design_estimate
 )
 from er_evaluation.summary import (
-    cluster_sizes
+    cluster_sizes,
+    name_variation_rate,
+    homonimy_rate,
 )
 from er_evaluation.metrics import (
     metrics_table,
     pairwise_precision,
     pairwise_recall,
+)
+from er_evaluation.plots import (
+    compare_plots,
+    plot_entropy_curve,
+    plot_cluster_sizes_distribution,
 )
 
 from pv_evaluation.benchmark import (
@@ -33,7 +41,7 @@ DEFAULT_ESTIMATORS = {
 }
 DEFAULT_INVENTORS_SAMPLES_WEIGHTS = {
     # Dataset and parameters to pass to the estimator.
-    "lai-sample": {"sample":load_lai_2011_inventors_benchmark(), "weights":1/cluster_sizes(load_lai_2011_inventors_benchmark())},
+    "lai-sample": {"sample":load_lai_2011_inventors_benchmark(), "weights": 1 + 0*cluster_sizes(load_lai_2011_inventors_benchmark())},
     "binette-sample": {"sample":load_binette_2022_inventors_benchmark(), "weights":1/cluster_sizes(load_binette_2022_inventors_benchmark())},
 }
 # Default benchmarks to run.
@@ -50,7 +58,7 @@ DEFAULT_METRICS = {
     "pairwise recall": pairwise_recall,
 }
 
-def inventor_estimates_plot(disambiguations, samples_weights, estimators=None, facet_col_wrap=2, **kwargs):
+def inventor_estimates_plot(disambiguations, samples_weights=None, estimators=None, facet_col_wrap=2, **kwargs):
     """Plot performance estimates for given cluster samples.
 
     Args:
@@ -74,8 +82,8 @@ def inventor_estimates_plot(disambiguations, samples_weights, estimators=None, f
         y="value",
         x="estimator",
         error_y="std",
-        color="algorithm",
-        facet_col="sample",
+        color="prediction",
+        facet_col="sample_weights",
         barmode="group",
         facet_col_wrap=facet_col_wrap,
         **kwargs,
[…]

### 2022-11-30 pv_evaluation/templates/inventor/2-summary.qmd
update

--- 2022-05-25 pv_evaluation/templates/inventor/2-summary.qmd
@@
 
-from pv_evaluation.utils import compare_plots
-from pv_evaluation.summary import InventorDisambiguationSummary
-from pv_evaluation.benchmark import inventor_benchmark_plot
+from er_evaluation.summary import (
+    homonimy_rate,
+    name_variation_rate,
+)
+from er_evaluation.plots import (
+    compare_plots, 
+    plot_cluster_sizes_distribution,
+    plot_entropy_curve,
+)
+from pv_evaluation.benchmark import (
+    inventor_benchmark_plot,
+    inventor_estimates_plot,
+    plot_entropy_curves,
+    top_inventors,
+    plot_cluster_sizes,
+    plot_homonimy_rates,
+    plot_name_variation_rates,
+)
 ```
@@
 ```{python}
-summarizers = {filename: InventorDisambiguationSummary(filename, processed_data_dir=".") for filename in {{ summary_table_files }} }
+def read_auto(datapath, dtype):
+    _, ext = os.path.splitext(datapath)
+
+    if ext == ".csv":
+        return pd.read_csv(datapath, dtype=dtype)
+    elif ext == ".tsv":
+        return pd.read_csv(datapath, sep="\t", dtype=dtype)
+    elif ext in [".parquet", ".pq", ".parq"]:
+        return pd.read_parquet(datapath, dtype=dtype)
+    elif ext in [".xlsx", ".xls"]:
+        return pd.read_excel(datapath, dtype=dtype)
+    else:
+        raise Exception("Unsupported file type. Should be one of csv, tsv, parquet, or xlsx.")
+
+def load_disambiguation(filename):
+    data = read_auto(filename, dtype=str)
+    data.set_index("mention_id", inplace=True)
+    disambiguation = data.iloc[:, 0]
+    disambiguation.rename(filename, inplace=True)
+
+    return disambiguation
+
+disambiguations = {filename: load_disambiguation(filename) for filename in {{ disambiguation_files }}}
+
+inventor_not_disambiguated = read_auto("{{ inventor_not_disambiguated_file }}", dtype=str)
+inventor_not_disambiguated["mention_id"] = "US" + inventor_not_disambiguated.patent_id + "-" + inventor_not_disambiguated.inventor_sequence
+inventor_not_disambiguated.set_index("mention_id", inplace=True)
+
+full_names = inventor_not_disambiguated.raw_inventor_name_first + " " + inventor_not_disambiguated.raw_inventor_name_last
+full_names = full_names.rename("full_name")
 ```
@@
 
+:::{.column-body-outset}
 ```{python}
-compare_plots(*[s.plot_cluster_size_distribution() for s in summarizers.values()])
+plot_cluster_sizes(disambiguations)
 ```
+:::
 
@@
 
-{% for filename in  summary_table_files%}
+{% for filename in  disambiguation_files%}
 
@@
 ```{python}
-summarizers["{{ filename }}"].get_top_inventors(n=20)
+from IPython.core.display import display, HTML
+
+display(HTML(top_inventors(disambiguations["{{ filename }}"], full_names)))
 ```
@@
 
+:::{.column-body-outset}
 ```{python}
-compare_plots(*[s.plot_entropy_curve() for s in summarizers.values()])
+plot_entropy_curves(disambiguations)
 ```
+:::
 
@@
 
+:::{.column-body-outset}
 ```{python}
-compare_plots(*[s.plot_cluster_unique_name_distribution() for s in summarizers.values()])
+plot_name_variation_rates(disambiguations, full_names)
 ```
+:::
 
@@
 
+:::{.column-body-outset}
 ```{python}
-compare_plots(*[s.plot_homonymy_rate_distribution() for s in summarizers.values()])
+plot_homonimy_rates(disambiguations, full_names)
 ```
+:::
 

### 2022-11-30 pv_evaluation/benchmark/report.py
update

@@ -41,7 +41,6 @@ DEFAULT_ESTIMATORS = {
 }
 DEFAULT_INVENTORS_SAMPLES_WEIGHTS = {
     # Dataset and parameters to pass to the estimator.
-    "lai-sample": {"sample":load_lai_2011_inventors_benchmark(), "weights": 1 + 0*cluster_sizes(load_lai_2011_inventors_benchmark())},
     "binette-sample": {"sample":load_binette_2022_inventors_benchmark(), "weights":1/cluster_sizes(load_binette_2022_inventors_benchmark())},
 }
 # Default benchmarks to run.
@@ -60,6 +59,9 @@ DEFAULT_METRICS = {
 
 def inventor_estimates_plot(disambiguations, samples_weights=None, estimators=None, facet_col_wrap=2, **kwargs):
     """Plot performance estimates for given cluster samples.
+
+    Note:
+        The timeframe for the disambiguation should match the timeframe considered by the reference sample.
 
     Args:
         disambiguations (dict): dictionary of disambiguation results (disambiguation results are pandas Series with "mention_id" index and cluster assignment values).

### 2022-11-30 pv_evaluation/benchmark/report.py
update tests

@@ -4,11 +4,7 @@ import plotly.express as px
 import numpy as np
 
 from er_evaluation.utils import expand_grid
-from er_evaluation.estimators import (
-    estimates_table,
-    pairwise_precision_design_estimate,
-    pairwise_recall_design_estimate
-)
+from er_evaluation.estimators import estimates_table, pairwise_precision_design_estimate, pairwise_recall_design_estimate
 from er_evaluation.summary import (
     cluster_sizes,
     name_variation_rate,
@@ -41,7 +37,10 @@ DEFAULT_ESTIMATORS = {
 }
 DEFAULT_INVENTORS_SAMPLES_WEIGHTS = {
     # Dataset and parameters to pass to the estimator.
-    "binette-sample": {"sample":load_binette_2022_inventors_benchmark(), "weights":1/cluster_sizes(load_binette_2022_inventors_benchmark())},
+    "binette-sample": {
+        "sample": load_binette_2022_inventors_benchmark(),
+        "weights": 1 / cluster_sizes(load_binette_2022_inventors_benchmark()),
+    },
 }
 # Default benchmarks to run.
 DEFAULT_INVENTORS_BENCHMARKS = {
@@ -56,6 +55,7 @@ DEFAULT_METRICS = {
     "pairwise precision": pairwise_precision,
     "pairwise recall": pairwise_recall,
 }
+
 
 def inventor_estimates_plot(disambiguations, samples_weights=None, estimators=None, facet_col_wrap=2, **kwargs):
     """Plot performance estimates for given cluster samples.
@@ -250,13 +250,11 @@ def plot_entropy_curves(disambiguations):
     """
     fig = compare_plots(*[plot_entropy_curve(d, name=k) for k, d in disambiguations.items()])
     fig.update_layout(
-        autosize=False, width=800, 
-        title="Hill numbers Curve", 
-        xaxis_title="q",
-        yaxis_title="Hill number of order q"
+        autosize=False, width=800, title="Hill numbers Curve", xaxis_title="q", yaxis_title="Hill number of order q"
     )
     fig.update_yaxes(autorange=True)
     return fig
+
 
 def plot_cluster_sizes(disambiguations):
     """
@@ -264,20 +262,18 @@ def plot_cluster_sizes(disambiguations):
 
     Args:
         disambiguations (Dict): Dictionary of membership vectors representing given disambiguations.
-    
+
     Returns:
         Plotly figure.
     """
[…]

### 2022-11-30 pv_evaluation/templates/render.py
update tests

@@ -28,8 +28,11 @@ def render_inventor_disambiguation_report(outdir, disambiguation_files, inventor
 
     with open(qmdpath, "w+") as file:
         file.write(
-            template.render(disambiguation_files=disambiguation_files, 
-            inventor_not_disambiguated_file=inventor_not_disambiguated_file, datetime=datetime.now().strftime("%I:%M%p on %B %d, %Y"))
+            template.render(
+                disambiguation_files=disambiguation_files,
+                inventor_not_disambiguated_file=inventor_not_disambiguated_file,
+                datetime=datetime.now().strftime("%I:%M%p on %B %d, %Y"),
+            )
         )
 
     if quarto.path() is None:

### 2022-11-30 tests/test_metrics.py

@@ -1,11 +1,0 @@
-import pandas as pd
-
-
-def test_case_one():
-    from pv_evaluation.metrics import cluster_precision_recall, pairwise_precision_recall
-
-    reference = pd.Series([1, 1, 1, 2, 2, 3, 3, 4, 4])
-    prediction = pd.Series([1, 1, 1, 2, 3, 2, 3, 4, 4])
-
-    assert cluster_precision_recall(prediction, reference) == (0.5, 0.5)
-    assert pairwise_precision_recall(prediction, reference) == (2 / 3, 2 / 3)

### 2022-11-30 tests/test_notebooks.py

@@ -1,31 +1,6 @@
 from testbook import testbook
 
 
-@testbook("tests/notebooks/templates/inventor-report.ipynb", execute=True)
-def test_inventor_report_notebook(tb):
-    pass
-
-
-@testbook("tests/notebooks/metrics/test_pairwise.ipynb", execute=True)
-def test_pairwise_notebook(tb):
-    pass
-
-
-@testbook("tests/notebooks/metrics/test_cluster.ipynb", execute=True)
-def test_cluster_notebook(tb):
-    pass
-
-
 @testbook("tests/notebooks/benchmark/benchmark-datasets.ipynb", execute=True)
 def test_benchmark_datasets_notebook(tb):
-    pass
-
-
-@testbook("tests/notebooks/summary/inventor.ipynb", execute=True)
-def test_summary_inventor_notebook(tb):
-    pass
-
-
-@testbook("tests/notebooks/estimators/test_estimators.ipynb", execute=True)
-def test_estimators_notebook(tb):
     pass

### 2023-03-27 pv_evaluation/benchmark/data.py
Prepare release

@@ -179,4 +179,6 @@ def load_nber_subset_assignees_benchmark():
     References:
         [1] Monath, N., Jones, C., & Madhavan, S. Disambiguating Patent Inventors, Assignees, and their Locations in PatentsView. https://s3.amazonaws.com/data.patentsview.org/documents/PatentsView_Disambiguation_Methods_Documentation.pdf
     """
-    return load_unique_id_series(ASSIGNEE_DATA_MODULE, "air-umass-assignees-benchmark.csv")
+    data = load_unique_id_series(ASSIGNEE_DATA_MODULE, "nber-subset-assignees-benchmark.csv")
+
+    return data[~data.index.duplicated()]

### 2023-03-27 pv_evaluation/benchmark/report.py

@@ -5,11 +5,15 @@ from datetime import datetime
 
 
 from er_evaluation.utils import expand_grid
-from er_evaluation.estimators import estimates_table, pairwise_precision_design_estimate, pairwise_recall_design_estimate
+from er_evaluation.estimators import (
+    estimates_table, 
+    pairwise_precision_estimator, 
+    pairwise_recall_estimator
+)
 from er_evaluation.summary import (
     cluster_sizes,
     name_variation_rate,
-    homonimy_rate,
+    homonymy_rate,
     matching_rate
 )
 from er_evaluation.metrics import (
@@ -34,8 +38,8 @@ from pv_evaluation.benchmark import (
 
 DEFAULT_ESTIMATORS = {
     # Point estimates and standard deviation estimates.
-    "pairwise precision": pairwise_precision_design_estimate,
-    "pairwise recall": pairwise_recall_design_estimate,
+    "pairwise precision": pairwise_precision_estimator,
+    "pairwise recall": pairwise_recall_estimator,
 }
 DEFAULT_INVENTORS_SAMPLES_WEIGHTS = {
     # Dataset and parameters to pass to the estimator.
@@ -77,7 +81,7 @@ def inventor_summary_trend_plot(persistent_inventor, names):
 
     metrics = {
         "Matching rate": lambda x: matching_rate(x),
-        "Homonimy rate": lambda x: homonimy_rate(x, names),
+        "Homonimy rate": lambda x: homonymy_rate(x, names),
         "Name variation rate": lambda x: name_variation_rate(x, names),
     }
 
@@ -377,7 +381,7 @@ def plot_name_variation_rates(disambiguations, names):
     return fig
 
 
-def plot_homonimy_rates(disambiguations, names):
+def plot_homonymy_rates(disambiguations, names):
     """
     Plot homonimy rates for a set of given disambiguations
 
@@ -389,7 +393,7 @@ def plot_homonimy_rates(disambiguations, names):
         Plotly figure.
     """
 
-    rates = [homonimy_rate(disambiguations[f], names=names) for f in disambiguations.keys()]
+    rates = [homonymy_rate(disambiguations[f], names=names) for f in disambiguations.keys()]
     data = pd.DataFrame({"Homonimy rate": rates, "Disambiguation": disambiguations.keys(), "none": ""})
 
     fig = px.bar(data, x="none", y="Homonimy rate", color="Disambiguation", barmode="group")

### 2023-03-27 setup.py

@@ -7,7 +7,7 @@ long_description = (this_directory / "README.md").read_text()
 if __name__ == "__main__":
     setup(
         name="pv_evaluation",
-        version="2.0.2",
+        version="2.1.0",
         license_files=("LICENSE.txt",),
         author="Olivier Binette, Sarvo Madhavan",
         author_email="olivier.binette@gmail.com",
@@ -31,7 +31,7 @@ if __name__ == "__main__":
             "jinja2",
             "kaleido",
             "openpyxl",
-            "er-evaluation",
+            "er-evaluation>=2.0.0",
         ],
         scripts=["scripts/hand-disambiguation/process-inventors-hand-disambiguation.py"],
     )

### 2023-03-27 pv_evaluation/templates/inventor/2-summary.qmd
update
Prepare release

@@
 from er_evaluation.summary import (
-    homonimy_rate,
+    homonymy_rate,
     name_variation_rate,
@@
     plot_cluster_sizes,
-    plot_homonimy_rates,
+    plot_homonymy_rates,
     plot_name_variation_rates,
@@
 
-display(HTML(top_inventors(disambiguations["{{ filename }}"], full_names)))
+display(HTML(top_inventors(disambiguations["{{ filename }}"], full_names).to_html()))
 ```
@@
 ```{python}
-plot_homonimy_rates(disambiguations, full_names)
+plot_homonymy_rates(disambiguations, full_names)
 ```

### 2023-03-27 pv_evaluation/benchmark/__init__.py

@@ -24,7 +24,7 @@ from pv_evaluation.benchmark.report import (
     plot_entropy_curves,
     plot_cluster_sizes,
     plot_name_variation_rates,
-    plot_homonimy_rates,
+    plot_homonymy_rates,
 )
 
 __all__ = [
@@ -48,5 +48,5 @@ __all__ = [
     "plot_entropy_curves",
     "plot_cluster_sizes",
     "plot_name_variation_rates",
-    "plot_homonimy_rates",
+    "plot_homonymy_rates",
 ]

### 2023-03-27 pv_evaluation/benchmark/report.py
fix benchmark report import

@@ -3,16 +3,6 @@ from datetime import datetime
 import numpy as np
 import pandas as pd
 import plotly.express as px
-from er_evaluation.estimators import (estimates_table,
-                                      pairwise_precision_design_estimate,
-                                      pairwise_recall_design_estimate)
-from er_evaluation.metrics import (metrics_table, pairwise_precision,
-                                   pairwise_recall)
-from er_evaluation.plots import (compare_plots,
-                                 plot_cluster_sizes_distribution,
-                                 plot_entropy_curve)
-from er_evaluation.summary import (cluster_sizes, homonimy_rate, matching_rate,
-                                   name_variation_rate)
 from er_evaluation.utils import expand_grid
 from er_evaluation.estimators import (
     estimates_table, 
